---
title: "Multi-Variant Headline Study — Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(broom)
library(broom.mixed)
library(knitr)
library(here)
source(here("August headlines", "templates", "config.R"))
```

Reads the cleaned data from `00_clean.Rmd` and answers the two study questions
for each headline: **(a)** does each self-relevance variant beat control, and
**(b)** which variant is best. Generalises to any number of variants; the July
example has one variant (`relevance`) so (b) reduces to a single comparison.

## Load + reshape

```{r load}
d <- readRDS(CFG$cleaned_rds)
dl <- reshape_long(d, CFG)
cat("Analytic N:", n_distinct(dl$PROLIFIC_PID),
    "| headlines:", nlevels(dl$headline),
    "| arms:", paste(levels(dl$arm), collapse = ", "), "\n")
dl |> count(headline, arm) |> pivot_wider(names_from = arm, values_from = n) |> kable()
```

```{r primary}
PM <- CFG$primary_measure   # primary outcome column in long data
variants <- setdiff(levels(dl$arm), CFG$control_label)
```

Primary outcome: **`r PM`**. Variants tested against control: **`r paste(variants, collapse=", ")`**.

## Pooled: variants vs control (all headlines)

`` `r PM` ~ arm + (1 | participant) + (1 | headline) ``. Fixed effects give the
average lift of each variant over control across headlines.

```{r pooled}
f <- reformulate(c("arm", "(1|PROLIFIC_PID)", "(1|headline)"), response = PM)
m_pool <- lmer(f, data = dl, REML = TRUE)
tidy(m_pool, effects = "fixed", conf.int = TRUE) |>
  mutate(across(where(is.numeric), ~round(., 2))) |>
  kable(caption = "Fixed effects (reference = control).")
```

## Per-headline: variant vs control + which variant wins

For each headline: arm means, every variant vs control (OLS), an omnibus test
that arms differ, the best-performing variant, and — if there are 2+ variants —
the best variant vs the runner-up.

```{r perhead-fns}
analyze_headline <- function(sub) {
  sub <- sub |> filter(!is.na(.data[[PM]])) |> mutate(arm = droplevels(arm))
  arms <- levels(sub$arm)
  vars <- setdiff(arms, CFG$control_label)

  # arm means
  means <- sub |> group_by(arm) |>
    summarise(M = mean(.data[[PM]]), SE = sd(.data[[PM]])/sqrt(n()), n = n(), .groups = "drop")

  # variant vs control (OLS, control ref)
  m <- lm(reformulate("arm", PM), data = sub)
  vs_ctrl <- tidy(m, conf.int = TRUE) |>
    filter(term != "(Intercept)") |>
    mutate(variant = sub("^arm", "", term)) |>
    select(variant, B = estimate, SE = std.error, t = statistic,
           p = p.value, conf.low, conf.high)

  # omnibus (does any arm differ)
  omni <- if (length(arms) >= 2) anova(m)$`Pr(>F)`[1] else NA_real_

  # best variant + runner-up test
  vmeans <- means |> filter(arm %in% vars) |> arrange(desc(M))
  best <- as.character(vmeans$arm[1])
  runner_p <- NA_real_; runner <- NA_character_
  if (nrow(vmeans) >= 2) {
    runner <- as.character(vmeans$arm[2])
    tt <- t.test(sub[[PM]][sub$arm == best], sub[[PM]][sub$arm == runner])
    runner_p <- tt$p.value
  }
  list(means = means, vs_ctrl = vs_ctrl, omni = omni,
       best = best, runner = runner, runner_p = runner_p)
}
```

```{r perhead, results='asis'}
for (h in levels(dl$headline)) {
  sub <- filter(dl, headline == h)
  r <- analyze_headline(sub)
  cat("\n\n### ", gsub("_", " ", h), "\n\n")

  print(kable(r$means |> mutate(across(c(M, SE), ~round(., 1))),
              caption = "Arm means"))
  cat("\n")
  print(kable(r$vs_ctrl |> mutate(across(where(is.numeric), ~round(., 2))),
              caption = "Each variant vs control"))

  cat("\n\n**Omnibus (arms differ):** p =",
      ifelse(is.na(r$omni), "NA", round(r$omni, 3)), "  \n")
  cat("**Best variant:** ", r$best,
      if (!is.na(r$runner))
        sprintf("  |  vs runner-up (%s): p = %.3f", r$runner, r$runner_p) else "",
      "\n\n---\n", sep = "")
}
```

## Per-headline means (plot)

```{r plot, fig.width=9, fig.height=3.5}
plot_df <- dl |>
  filter(!is.na(.data[[PM]])) |>
  group_by(headline, arm) |>
  summarise(M = mean(.data[[PM]]), SE = sd(.data[[PM]])/sqrt(n()), .groups = "drop")

ggplot(plot_df, aes(arm, M, ymin = M - SE, ymax = M + SE, color = arm)) +
  geom_pointrange(size = 0.5) +
  facet_wrap(~headline, nrow = 1,
             labeller = as_labeller(function(x) gsub("_", " ", x))) +
  labs(x = NULL, y = paste0(PM, " (0-100)"),
       title = paste("Mean", PM, "by arm and headline"),
       caption = "Points = mean, bars = +/-1 SE") +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1))
```

## Secondary outcomes (pooled)

Same pooled model for the other measures.

```{r secondary}
sec <- setdiff(CFG$measures, PM)
map_dfr(sec, function(mm) {
  f2 <- reformulate(c("arm", "(1|PROLIFIC_PID)", "(1|headline)"), response = mm)
  m2 <- suppressMessages(lmer(f2, data = dl, REML = TRUE))
  tidy(m2, effects = "fixed", conf.int = TRUE) |>
    filter(term != "(Intercept)") |>
    mutate(measure = mm, .before = 1)
}) |>
  mutate(across(where(is.numeric), ~round(., 2))) |>
  select(measure, term, estimate, std.error, statistic, conf.low, conf.high) |>
  kable(caption = "Variant vs control, secondary outcomes (pooled).")
```
