---
title: "Prolific Rejections — Participants to Reject / Not Pay"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(here)
source(here("August headlines", "templates", "config.R"))
```

> **Purpose.** This report is deliberately separate from the analysis. It lists
> every Prolific submission that meets the pre-registered rejection criteria,
> with a reason for each, so a human can review before actioning rejections on
> Prolific. **Rejection is hard to reverse and Prolific scrutinises it — review
> this table manually; do not auto-submit.**

Rejection rule (from `config.R`): reject if any standalone-reject flag fires
(default: off-task > `r CFG$offtask_threshold_min` min) **or** a submission
accumulates `r CFG$reject_nflags`+ quality flags.

## Load + merge

```{r load}
q <- read_qualtrics(CFG$qualtrics_path)
p <- read_prolific(CFG$prolific_path)

# Rejection applies to genuine submissions only: finished, valid PID, and not
# already unpaid on Prolific (RETURNED / TIMED-OUT are never "rejected").
d <- q |>
  filter(DistributionChannel == "anonymous", Finished == TRUE,
         PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID)) |>
  left_join(p, by = "PROLIFIC_PID") |>
  filter(!prolific_status %in% c("RETURNED", "TIMED-OUT"))

d <- compute_flags(d, CFG)
```

Submissions evaluated: **`r nrow(d)`**.

## Summary

```{r summary}
tibble(
  Metric = c("Submissions evaluated", "Flagged (>=1)", "TO REJECT",
             "  via off-task (standalone)", "  via 2+ flags"),
  N = c(nrow(d), sum(d$n_flags >= 1), sum(d$reject),
        sum(d$flag_offtask), sum(d$n_flags >= CFG$reject_nflags))
) |> kable()
```

## ▶ Participants to reject / not pay

The table below is the actionable output: **Prolific ID, submission ID, and the
reason for each rejection.** Empty means no submission met the criteria.

```{r reject-table}
rejects <- d |>
  filter(reject) |>
  transmute(
    PROLIFIC_PID,
    submission_id,
    reason        = reject_reason,
    n_flags,
    attn          = sprintf("%d/%d wrong", n_attn_wrong, n_attn_shown),
    off_task_min,
    completion_code
  ) |>
  arrange(desc(n_flags), desc(off_task_min))

if (nrow(rejects) == 0) {
  cat("No submissions met the rejection criteria.\n")
} else {
  kable(rejects, caption = sprintf("%d submission(s) to reject.", nrow(rejects)))
}
```

## Write rejection CSV

A CSV of the IDs + reasons is written for your records and for pasting IDs into
Prolific's bulk-reject flow. (Prolific rejections still require a manual reason;
use the `reason` column.)

```{r write}
dir.create(dirname(CFG$reject_csv), showWarnings = FALSE, recursive = TRUE)
write_excel_csv(rejects, CFG$reject_csv, na = "")
cat("Wrote", nrow(rejects), "row(s) to", CFG$reject_csv, "\n")
```

## For contrast: flagged but NOT rejected

Submissions with exactly one flag (below the 2+ threshold and no standalone
trigger). These are **kept and paid** under the current rule — review in case you
want to tighten `config.R` (e.g., add `flag_attention` to standalone rejects).

```{r not-rejected}
d |>
  filter(!reject, n_flags >= 1) |>
  transmute(PROLIFIC_PID, n_flags,
            which_flag = case_when(
              flag_attention ~ sprintf("attention (%d/%d wrong)", n_attn_wrong, n_attn_shown),
              flag_straightline ~ sprintf("straightlined (%d sliders)", n_sliders_same),
              flag_bot_combined ~ "bot",
              flag_duplicate ~ "duplicate",
              flag_auth_q ~ "auth-question",
              flag_offtask ~ "off-task",
              TRUE ~ "other")) |>
  arrange(desc(n_flags)) |>
  kable(caption = "Flagged once — paid under current rule.")
```
