---
title: "Step 1 Pilot: Descriptive Analysis"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, reactable, scales, RColorBrewer)
```

```{r aesthetics}
plot_aes <- theme_minimal() +
  theme(
    legend.position    = "bottom",
    legend.text        = element_text(size = 9),
    text               = element_text(size = 12),
    axis.text          = element_text(color = "black"),
    axis.ticks.y       = element_blank(),
    panel.grid.major.y = element_blank()
  )

palette_main <- "#197278"
```

```{r scale-levels}
# ── Amount / knowledge (None at all → A great deal) ─────────────────────────
lvl_know    <- c("None at all", "A little", "A moderate amount", "A lot", "A great deal")
lvl_know_ns <- c(lvl_know, "Not sure")

# ── Agree / disagree (5-point, Somewhat variant) ────────────────────────────
lvl_agree5 <- c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                "Somewhat agree", "Strongly agree")

# ── Positive / negative effect ───────────────────────────────────────────────
lvl_pos_neg <- c("Extremely negative", "Somewhat negative", "Neither positive nor negative",
                 "Somewhat positive", "Extremely positive")

# ── Importance ───────────────────────────────────────────────────────────────
lvl_importance <- c("Not at all important", "Slightly important", "Moderately important",
                    "Very important", "Extremely important")

# ── Likelihood: research_5#2 and research_6#2 (Very unlikely → Very likely) ─
lvl_likelihood_res <- c("Very unlikely", "Somewhat unlikely", "Neutral",
                        "Somewhat likely", "Very likely")

# ── Likelihood: govtfund_5 (Extremely unlikely → Extremely likely) ───────────
lvl_likelihood_gov <- c("Extremely unlikely", "Somewhat unlikely", "Neither likely nor unlikely",
                        "Somewhat likely", "Extremely likely")

# ── Problematic ──────────────────────────────────────────────────────────────
lvl_problematic <- c("Not at all problematic", "Slightly problematic", "Moderately problematic",
                     "Very problematic", "Extremely problematic")

# ── Approve / disapprove (4-point, no midpoint) ─────────────────────────────
lvl_approve4 <- c("Strongly disapprove", "Somewhat disapprove",
                  "Somewhat approve", "Strongly approve")

# ── Approve / disapprove (5-point, "Neither approve nor disapprove") ─────────
# Used for govtfund_4, govtfund_9
lvl_approve5 <- c("Strongly disapprove", "Somewhat disapprove",
                  "Neither approve nor disapprove",
                  "Somewhat approve", "Strongly approve")

# ── Approve / disapprove (5-point, "Neutral / neither…" wording) ─────────────
# Used for highered_1
lvl_approve5_he <- c("Strongly disapprove", "Somewhat disapprove",
                     "Neutral / neither approve nor disapprove",
                     "Somewhat approve", "Strongly approve")

# ── Priority ─────────────────────────────────────────────────────────────────
lvl_priority <- c("Not a priority", "Low priority", "Somewhat priority",
                  "Moderate priority", "High priority")

# ── Frequency (past engagement) ──────────────────────────────────────────────
lvl_freq <- c("Never", "Once or twice a year", "Once or twice a month",
              "Once or twice a week", "Almost every day", "Once or more per day")

# ── Behavioral intention (7-point, includes "Unsure") ────────────────────────
lvl_intent <- c("Definitely will not", "Probably will not", "Maybe will not",
                "Unsure", "Maybe will", "Probably will", "Definitely will")

# ── Local impact of cuts ─────────────────────────────────────────────────────
lvl_impact <- c("Strong negative impact", "Somewhat negative impact",
                "Neither positive nor negative impact",
                "Somewhat positive impact", "Strong positive impact")

# ── Climate scientist trust ──────────────────────────────────────────────────
lvl_climate_trust <- c("Not at all", "Slightly", "Moderately", "Very strongly")

# ── Proportion nonprofit ─────────────────────────────────────────────────────
lvl_proportion <- c("None", "Less than half", "About half", "Most", "All", "Not sure")

# ── Education ────────────────────────────────────────────────────────────────
lvl_degree <- c("No formal education", "Did not complete high school",
                "High school graduate (diploma)", "High school graduate (GED)",
                "Some college (1-4 years, no degree)",
                "Associate's degree (including occupational or academic degrees)",
                "Bachelor's degree (BA, BS, etc.)",
                "Master's degree (MA, MS, MEng, MSW, etc.)",
                "Professional school degree (MD, JD, etc.)", "Doctoral degree (PhD, EdD, etc.)")

# ── Income ───────────────────────────────────────────────────────────────────
lvl_income <- c("Less than $5,000", "$5,000 through $11,999", "$12,000 through $15,999",
                "$16,000 through $24,999", "$25,000 through $34,999", "$35,000 through $49,999",
                "$50,000 through $74,999", "$75,000 through $99,999",
                "$100,000 through $149,999", "$150,000 or greater",
                "Prefer not to say / I don't know")

# ── Political ideology ───────────────────────────────────────────────────────
lvl_ideology <- c("Extremely liberal", "Liberal", "Slightly liberal",
                  "Moderate / middle of the road",
                  "Slightly conservative", "Conservative", "Extremely conservative")
```

```{r helpers}
# Frequency table for a single column
freq_tab <- function(data, col, levels = NULL) {
  df <- data %>%
    filter(!is.na(.data[[col]]), .data[[col]] != "") %>%
    count(Response = .data[[col]], name = "n") %>%
    mutate(Pct = round(100 * n / sum(n), 1))
  if (!is.null(levels)) {
    present <- intersect(levels, df$Response)
    df <- df %>% mutate(Response = factor(Response, levels = present)) %>% arrange(Response)
  } else {
    df <- df %>% arrange(desc(n))
  }
  df %>% reactable(striped = TRUE, compact = TRUE, defaultPageSize = 15)
}

# Bar chart for a single item
bar_single <- function(data, col, title = "", levels = NULL, fill = palette_main) {
  df <- data %>%
    filter(!is.na(.data[[col]]), .data[[col]] != "") %>%
    count(response = .data[[col]])
  if (!is.null(levels)) {
    present <- intersect(levels, df$response)
    df <- df %>% mutate(response = factor(response, levels = present))
  } else {
    df <- df %>% mutate(response = fct_reorder(response, n))
  }
  ggplot(df, aes(x = response, y = n)) +
    geom_col(fill = fill) +
    geom_text(aes(label = n), hjust = -0.2, size = 3.5) +
    coord_flip() +
    expand_limits(y = max(df$n) * 1.15) +
    labs(x = "", y = "Count", title = title) +
    plot_aes
}

# Stacked proportional bar chart for a matrix question
bar_matrix <- function(data, cols, item_labels, title = "", scale_levels = NULL,
                       pal = "RdYlGn", pal_dir = 1, legend_rows = 2, fig_height = NULL) {
  df <- data %>%
    select(all_of(cols)) %>%
    rename_with(~ item_labels) %>%
    pivot_longer(everything(), names_to = "item", values_to = "response") %>%
    filter(!is.na(response), response != "")
  if (!is.null(scale_levels)) {
    present <- intersect(scale_levels, unique(df$response))
    df <- df %>% mutate(response = factor(response, levels = present))
  }
  df %>%
    count(item, response) %>%
    group_by(item) %>%
    mutate(pct = n / sum(n),
           item = factor(item, levels = rev(item_labels))) %>%
    ggplot(aes(x = item, y = pct, fill = response)) +
    geom_col(position = "fill", width = 0.7) +
    coord_flip() +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    scale_fill_brewer(palette = pal, direction = pal_dir) +
    labs(x = "", y = "Proportion", fill = "", title = title) +
    plot_aes +
    guides(fill = guide_legend(reverse = TRUE, nrow = legend_rows))
}

# Frequency table for a matrix question
freq_matrix <- function(data, cols, item_labels, scale_levels = NULL) {
  df <- data %>%
    select(all_of(cols)) %>%
    rename_with(~ item_labels) %>%
    pivot_longer(everything(), names_to = "Item", values_to = "Response") %>%
    filter(!is.na(Response), Response != "") %>%
    count(Item, Response) %>%
    group_by(Item) %>%
    mutate(Pct = round(100 * n / sum(n), 1))
  if (!is.null(scale_levels)) {
    present <- intersect(scale_levels, unique(df$Response))
    df <- df %>% mutate(Response = factor(Response, levels = present)) %>% arrange(Item, Response)
  }
  df %>%
    reactable(groupBy = "Item", striped = TRUE, compact = TRUE, filterable = TRUE,
              defaultPageSize = 20,
              columns = list(Item = colDef(minWidth = 250)))
}
```

```{r load-data}
path <- "~/Documents/GitHub/UniversityNews"

data <- readRDS(sprintf("%s/Data/Cleaned/UnivNews_Step1_combined.rds", path)) %>%
  arrange(StartDate)

N <- nrow(data)
```

**N = `r N`** (Cohorts 1 + 2 combined; all responses retained, no exclusions applied).

Sections follow the order questions appeared in the survey.

---

# 1. University Research Beliefs {.tabset}

## Knowledge & Science Attitude {.unnumbered}

**research_1**: How much do you, personally, know about research at colleges and universities?

```{r r1}
bar_single(data, "research_1", title = "Self-rated knowledge of university research", levels = lvl_know)
freq_tab(data, "research_1", levels = lvl_know)
```

**research_2**: "Scientific research methods are the best way to find out if something is true or false."

```{r r2}
bar_single(data, "research_2", title = "Scientific methods are the best way to find truth",
           levels = lvl_agree5)
freq_tab(data, "research_2", levels = lvl_agree5)
```

## Effects of Research on Groups (research_3) {.unnumbered}

To what extent has research at colleges and universities had a positive or negative effect on each of the following?

```{r r3, fig.height=7}
r3_cols   <- paste0("research_3_", 1:13)
r3_labels <- c("You personally", "People you care about", "People in your local community",
               "People in the United States", "Students at universities",
               "Scientists at universities", "Universities themselves",
               "Pharmaceutical companies", "Technology companies",
               "The military", "The US government",
               "Wealthy individuals", "Disadvantaged individuals")

bar_matrix(data, r3_cols, r3_labels,
           title        = "Effects of university research on groups",
           scale_levels = lvl_pos_neg,
           pal = "RdYlGn", pal_dir = 1, legend_rows = 2, fig_height = 7)
freq_matrix(data, r3_cols, r3_labels, scale_levels = lvl_pos_neg)
```

## Research Literacy & Attitudes (research_4) {.unnumbered}

Rate your agreement with the following statements:

```{r r4, fig.height=6}
r4_cols   <- paste0("research_4_", 1:8)
r4_labels <- c("I usually understand research findings discussed in the news",
               "I know where to look up info about academic research",
               "It's clear how to apply research findings in my own life",
               "I often think about the impact of science on my everyday life",
               "The benefits of scientific research outweigh harmful results",
               "Science makes our way of life change too fast",
               "Because of scientific research, there will be more opportunities for the next generation",
               "Research advancing knowledge is necessary, even w/o immediate benefits")

bar_matrix(data, r4_cols, r4_labels,
           title        = "Research literacy and attitudes",
           scale_levels = lvl_agree5,
           pal = "RdYlBu", pal_dir = 1, legend_rows = 2, fig_height = 6)
freq_matrix(data, r4_cols, r4_labels, scale_levels = lvl_agree5)
```

## Research Importance (research_5) {.unnumbered}

For each research area/outcome, how important is it for the public good?

```{r r5-imp, fig.height=8}
r5_imp_cols <- paste0("research_5.1_", 1:13)
r5_labels <- c("Advancing social science (behavior, mental health, poverty, misinformation)",
               "Developing new medicines (cancer, heart disease, dementia)",
               "Protecting the environment and ensuring clean air and water",
               "Developing new energy technologies",
               "Developing advanced technologies to drive economic growth",
               "Developing innovative manufacturing processes",
               "Developing new defense and national security technologies",
               "Advancing AI and machine learning",
               "Exploring space",
               "Improving education systems",
               "Developing better public policies",
               "Helping individuals understand how to improve their lives",
               "Increasing awareness of others' experiences and perspectives")

bar_matrix(data, r5_imp_cols, r5_labels,
           title        = "Importance of research areas for the public good",
           scale_levels = lvl_importance,
           pal = "Blues", pal_dir = 1, legend_rows = 2, fig_height = 8)
freq_matrix(data, r5_imp_cols, r5_labels, scale_levels = lvl_importance)
```

## Research Likelihood (research_5) {.unnumbered}

For each research area/outcome, how likely is academic research to produce it?

```{r r5-lik, fig.height=8}
r5_lik_cols <- paste0("research_5.2_", 1:13)

bar_matrix(data, r5_lik_cols, r5_labels,
           title        = "Likelihood that academic research produces each outcome",
           scale_levels = lvl_likelihood_res,
           pal = "Blues", pal_dir = 1, legend_rows = 2, fig_height = 8)
freq_matrix(data, r5_lik_cols, r5_labels, scale_levels = lvl_likelihood_res)
```

## Negative Outcomes: Problematic (research_6) {.unnumbered}

For each potential negative outcome of academic research, how problematic would it be?

```{r r6-prob, fig.height=7}
r6_prob_cols <- paste0("research_6.1_", 1:11)
r6_labels <- c("Researchers make mistakes and results are incorrect",
               "Research is slow to have an impact",
               "Few people can access or understand results",
               "Findings don't generalize across groups",
               "Studies fail to yield impactful results",
               "Research is conducted inefficiently and wastes money",
               "New technology resulting from research eliminates jobs",
               "New technology resulting from research invades privacy",
               "Research creates technology that causes widespread damage",
               "Research findings are misused",
               "Results reporting is biased by news outlets")

bar_matrix(data, r6_prob_cols, r6_labels,
           title        = "How problematic are potential negative outcomes of academic research?",
           scale_levels = lvl_problematic,
           pal = "Reds", pal_dir = 1, legend_rows = 2, fig_height = 7)
freq_matrix(data, r6_prob_cols, r6_labels, scale_levels = lvl_problematic)
```

## Negative Outcomes: Likelihood (research_6) {.unnumbered}

How likely is academic research to produce each negative outcome?

```{r r6-lik, fig.height=7}
r6_lik_cols <- paste0("research_6.2_", 1:11)

bar_matrix(data, r6_lik_cols, r6_labels,
           title        = "Likelihood that academic research produces each negative outcome",
           scale_levels = lvl_likelihood_res,
           pal = "Blues", pal_dir = 1, legend_rows = 2, fig_height = 7)
freq_matrix(data, r6_lik_cols, r6_labels, scale_levels = lvl_likelihood_res)
```

---

# 2. Government Funding Attitudes {.tabset}

## Overall Approval & Knowledge {.unnumbered}

**govtfund_1**: Do you approve or disapprove of the federal government using taxpayer funds to invest in scientific research at colleges and universities?

```{r gf1}
bar_single(data, "govtfund_1",
           title  = "Approval of federal funding for university research",
           levels = lvl_approve4)
freq_tab(data, "govtfund_1", levels = lvl_approve4)
```

**govtfund_2**: Which statement comes closer to your view?

```{r gf2}
bar_single(data, "govtfund_2",
           title = "Government funding: essential vs. private investment sufficient")
freq_tab(data, "govtfund_2")
```

**govtfund_3**: How much do you currently know about cuts to government funding for academic research?

```{r gf3}
bar_single(data, "govtfund_3",
           title  = "Knowledge of funding cuts to academic research",
           levels = lvl_know)
freq_tab(data, "govtfund_3", levels = lvl_know)
```

## Perceived Group Support (govtfund_4) {.unnumbered}

How do you think each of these groups feel about the government financially supporting academic research?

```{r gf4, fig.height=8}
gf4_cols   <- paste0("govtfund_4_", 1:13)
gf4_labels <- c("People who will directly benefit from the research",
                "Students at universities",
                "Scientists at universities",
                "The general public",
                "People in the military",
                "People who identify as liberals",
                "People who identify as conservatives",
                "People who favor minimal government spending",
                "Politicians",
                "People who don't believe in mainstream science",
                "Medical and mental health professionals",
                "Pharmaceutical companies",
                "Technology companies")

bar_matrix(data, gf4_cols, gf4_labels,
           title        = "Perceived group support for government funding of academic research",
           scale_levels = lvl_approve5,
           pal = "RdYlGn", pal_dir = 1, legend_rows = 2, fig_height = 8)
freq_matrix(data, gf4_cols, gf4_labels, scale_levels = lvl_approve5)
```

## Likelihood of Outcomes (govtfund_5) {.unnumbered}

How likely is it that these things happen when the government funds academic research?

```{r gf5, fig.height=7}
gf5_cols   <- paste0("govtfund_5_", 1:10)
gf5_labels <- c("Researchers have enough resources to explore ideas",
                "Research can focus on long-term projects",
                "Exciting research is sped up",
                "Results become publicly available",
                "Government-funded researchers are held to higher standards",
                "Money is spent on less important things",
                "Taxpayer money is wasted",
                "Research is delayed by government oversight",
                "Political agendas influence what research gets funded",
                "Researchers lie about results to maintain funding")

bar_matrix(data, gf5_cols, gf5_labels,
           title        = "Likelihood of outcomes when government funds academic research",
           scale_levels = lvl_likelihood_gov,
           pal = "Blues", pal_dir = 1, legend_rows = 2, fig_height = 7)
freq_matrix(data, gf5_cols, gf5_labels, scale_levels = lvl_likelihood_gov)
```

## Agreement: Research Governance (gotvfund_6) {.unnumbered}

Rate your agreement with the following statements:

```{r gf6, fig.height=7}
gf6_cols   <- paste0("gotvfund_6_", 1:9)
gf6_labels <- c("Rules should ensure government-funded research is done well",
                "Oversight committees protect against unethical research",
                "Many everyday tools are the result of academic research",
                "University research benefits day-to-day lives in ways hard to see",
                "University researchers are motivated primarily by profit",
                "Private companies conduct research primarily to benefit the public",
                "Govt-funded research is more objective than privately funded research",
                "Private company research is more likely to be biased toward company interests",
                "Results of private company research will become publicly accessible")

bar_matrix(data, gf6_cols, gf6_labels,
           title        = "Agreement: research governance and objectivity",
           scale_levels = lvl_agree5,
           pal = "RdYlBu", pal_dir = 1, legend_rows = 2, fig_height = 7)
freq_matrix(data, gf6_cols, gf6_labels, scale_levels = lvl_agree5)
```

## Research Priorities (govtfund_7) {.unnumbered}

What are the priorities of government-funded research at colleges and universities?

```{r gf7, fig.height=4}
gf7_cols   <- paste0("govtfund_7_", 1:4)
gf7_labels <- c("Making a profit",
                "Advance knowledge and benefit society",
                "Develop products that can be sold",
                "Serve the interests of the government")

bar_matrix(data, gf7_cols, gf7_labels,
           title        = "Perceived priorities of government-funded university research",
           scale_levels = lvl_priority,
           pal = "Blues", pal_dir = 1, legend_rows = 1, fig_height = 4)
freq_matrix(data, gf7_cols, gf7_labels, scale_levels = lvl_priority)
```

## Benefits of Tax Investment (govtfund_8) {.unnumbered}

Rate your agreement: "Investing tax dollars in academic research..."

```{r gf8, fig.height=5}
gf8_cols   <- paste0("govtfund_8_", 1:7)
gf8_labels <- c("...boosts the economy",
                "...improves health and saves lives",
                "...drives industry investment",
                "...makes America a leader",
                "...protects national security",
                "...leads to scientific breakthroughs",
                "...benefits people like you")

bar_matrix(data, gf8_cols, gf8_labels,
           title        = "Agreement: benefits of investing tax dollars in academic research",
           scale_levels = lvl_agree5,
           pal = "RdYlBu", pal_dir = 1, legend_rows = 2, fig_height = 5)
freq_matrix(data, gf8_cols, gf8_labels, scale_levels = lvl_agree5)
```

## Approval of Funding Cuts (govtfund_9) {.unnumbered}

Would you approve or disapprove if the federal government took the following actions?

```{r gf9, fig.height=4}
gf9_cols   <- paste0("govtfund_9_", 1:5)
gf9_labels <- c("Cutting funding for health research",
                "Cutting funding for education",
                "Cutting funding for science",
                "Cutting funding for the arts",
                "Cutting funding for the humanities")

bar_matrix(data, gf9_cols, gf9_labels,
           title        = "Approval of federal cuts to research and education funding",
           scale_levels = lvl_approve5,
           pal = "RdYlGn", pal_dir = -1, legend_rows = 2, fig_height = 4)
freq_matrix(data, gf9_cols, gf9_labels, scale_levels = lvl_approve5)
```

**govfund_10**: Do you think your local area would be positively or negatively impacted by cuts to funding for scientific research?

```{r gf10}
bar_single(data, "govfund_10",
           title  = "Perceived local impact of cuts to scientific research funding",
           levels = lvl_impact)
freq_tab(data, "govfund_10", levels = lvl_impact)
```

---

# 3. Behavioral Intentions {.tabset}

## Intent to Act {.unnumbered}

```{r intent, fig.height=4}
intent_cols   <- paste0("X", 1:4, "_intent")
intent_labels <- c("Contact reps to oppose cuts to university research funding",
                   "Talk to others about cuts to federal scientific research funding",
                   "Share information online about cuts to scientific research funding",
                   "Contact reps to support federal funding for university research")

bar_matrix(data, intent_cols, intent_labels,
           title        = "Behavioral intentions",
           scale_levels = lvl_intent,
           pal = "Blues", pal_dir = 1, legend_rows = 2, fig_height = 4)
freq_matrix(data, intent_cols, intent_labels, scale_levels = lvl_intent)
```

---

# 4. Past Engagement {.tabset}

## Science Engagement (past_engage) {.unnumbered}

Over the past 12 months, how often have you done the following?

```{r past-engage, fig.height=6}
pe_cols   <- paste0("past_engage_", 1:7)
pe_labels <- c("Conversations about science-related topics",
               "Shared or commented on social media posts about science",
               "Attended public rallies or protests related to science",
               "Shared info online about cuts to federal research funding",
               "Talked to others about cuts to federal research funding",
               "Contacted reps to oppose cuts to federal research funding",
               "Contacted reps to support federal funding for research")

bar_matrix(data, pe_cols, pe_labels,
           title        = "Past science engagement behaviors (past 12 months)",
           scale_levels = lvl_freq,
           pal = "Blues", pal_dir = 1, legend_rows = 2, fig_height = 6)
freq_matrix(data, pe_cols, pe_labels, scale_levels = lvl_freq)
```

---

# 5. Higher Education Attitudes {.tabset}

## Approval (highered_1) {.unnumbered}

Overall, how much do you approve or disapprove of:

```{r he1, fig.height=3.5}
he1_cols   <- paste0("highered_1_", 1:3)
he1_labels <- c("Private colleges and universities in the US",
                "Your state's public university system",
                "Your local community college(s)")

bar_matrix(data, he1_cols, he1_labels,
           title        = "Approval of higher education institutions",
           scale_levels = lvl_approve5_he,
           pal = "RdYlGn", pal_dir = 1, legend_rows = 2, fig_height = 3.5)
freq_matrix(data, he1_cols, he1_labels, scale_levels = lvl_approve5_he)
```

## Trust (highered_2) {.unnumbered}

How much do you trust each type of institution to do what is right?

```{r he2, fig.height=3.5}
he2_cols   <- paste0("highered_2_", 1:3)

bar_matrix(data, he2_cols, he1_labels,
           title        = "Trust in higher education institutions",
           scale_levels = lvl_know,
           pal = "Blues", pal_dir = 1, legend_rows = 1, fig_height = 3.5)
freq_matrix(data, he2_cols, he1_labels, scale_levels = lvl_know)
```

## Contribution to Scientific Achievements (highered_3) {.unnumbered}

How much do each of the following contribute to scientific achievements in the US?

```{r he3, fig.height=4.5}
he3_cols   <- paste0("highered_3_", 1:6)
he3_labels <- c("Private colleges and universities",
                "Private companies (pharma, tech, etc.)",
                "Federal government agencies",
                "Charitable foundations",
                "State colleges and universities",
                "Community colleges")

bar_matrix(data, he3_cols, he3_labels,
           title        = "Contribution to scientific achievements in the US",
           scale_levels = lvl_know_ns,
           pal = "Blues", pal_dir = 1, legend_rows = 1, fig_height = 4.5)
freq_matrix(data, he3_cols, he3_labels, scale_levels = lvl_know_ns)
```

## Proportion Nonprofit (highered_4) {.unnumbered}

What proportion of each type of institution do you think is nonprofit?

```{r he4, fig.height=4.5}
he4_cols   <- paste0("highered_4_", 1:6)
he4_labels <- c("Private colleges and universities",
                "Public state colleges and universities",
                "Community colleges",
                "Private companies (e.g., pharma and tech)",
                "Federal government agencies",
                "Charitable foundations")

bar_matrix(data, he4_cols, he4_labels,
           title        = "Estimated proportion nonprofit by institution type",
           scale_levels = lvl_proportion,
           pal = "Blues", pal_dir = 1, legend_rows = 1, fig_height = 4.5)
freq_matrix(data, he4_cols, he4_labels, scale_levels = lvl_proportion)
```

---

# 6. University Perceptions {.tabset}

## Outcomes (univ_2) {.unnumbered}

To what extent do you agree or disagree that colleges and universities contribute to each of the following outcomes in the US?

```{r univ2, fig.height=7}
u2_cols   <- paste0("univ_2_", 1:10)
u2_labels <- c("Greater innovation (scientific, medical, technological discoveries)",
               "Better jobs, promotions, and career advancement",
               "Higher household incomes",
               "A more knowledgeable population",
               "A competitive advantage for the US over other countries",
               "More entrepreneurship and business creation",
               "Increased compassion for and tolerance of others",
               "Overall economic growth",
               "Better relationships with other countries",
               "Benefits to surrounding communities")

bar_matrix(data, u2_cols, u2_labels,
           title        = "Agreement: universities contribute to these US outcomes",
           scale_levels = lvl_agree5,
           pal = "RdYlBu", pal_dir = 1, legend_rows = 2, fig_height = 7)
freq_matrix(data, u2_cols, u2_labels, scale_levels = lvl_agree5)
```

## Knowledge Functions (univ_4) {.unnumbered}

Do you agree or disagree that colleges and universities:

```{r univ4, fig.height=3.5}
u4_cols   <- paste0("univ_4_", 1:3)
u4_labels <- c("Discover new knowledge through original research",
               "Apply existing knowledge and connect ideas across contexts",
               "Apply knowledge-based solutions to society's needs")

bar_matrix(data, u4_cols, u4_labels,
           title        = "Agreement: university knowledge functions",
           scale_levels = lvl_agree5,
           pal = "RdYlBu", pal_dir = 1, legend_rows = 1, fig_height = 3.5)
freq_matrix(data, u4_cols, u4_labels, scale_levels = lvl_agree5)
```

## Who Benefits (univ_5) {.unnumbered}

How much do each of the following people benefit from colleges and universities?

```{r univ5, fig.height=5}
u5_cols   <- paste0("univ_5_", 1:7)
u5_labels <- c("You personally",
               "People you care about",
               "Local communities",
               "Students who attend",
               "Students' families",
               "Employers and businesses",
               "Society as a whole")

bar_matrix(data, u5_cols, u5_labels,
           title        = "Who benefits from colleges and universities?",
           scale_levels = lvl_know,
           pal = "Blues", pal_dir = 1, legend_rows = 1, fig_height = 5)
freq_matrix(data, u5_cols, u5_labels, scale_levels = lvl_know)
```

---

# 7. Climate Attitudes {.tabset}

## Global Warming Beliefs {.unnumbered}

**climate_1**: Do you think global warming is happening?

```{r clim1}
bar_single(data, "climate_1", title = "Global warming is happening")
freq_tab(data, "climate_1")
```

**climate_2**: Assuming global warming is happening, do you think it is...

```{r clim2}
bar_single(data, "climate_2", title = "Cause of global warming")
freq_tab(data, "climate_2")
```

**climate_3**: To what extent do you trust scientists who work on climate change?

```{r clim3}
bar_single(data, "climate_3",
           title  = "Trust in climate scientists",
           levels = lvl_climate_trust)
freq_tab(data, "climate_3", levels = lvl_climate_trust)
```

## Climate Research Priorities {.unnumbered}

How important is it for colleges and universities to do research on the following climate-related topics?

```{r clim4, fig.height=5}
c4_cols   <- paste0("climate_4_", 1:4)
c4_labels <- c("Climate science and earth systems\n(greenhouse gases, sea levels, past climate cycles)",
               "Climate mitigation approaches\n(renewable energy, carbon capture, sustainable agriculture)",
               "Climate adaptation and resilience\n(urban infrastructure, ecosystem management)",
               "Climate policy, economics, and human impact\n(environmental justice, climate finance, psychology)")

bar_matrix(data, c4_cols, c4_labels,
           title        = "Importance of university climate research topics",
           scale_levels = lvl_importance,
           pal = "Blues", pal_dir = 1, legend_rows = 1, fig_height = 5)
freq_matrix(data, c4_cols, c4_labels, scale_levels = lvl_importance)
```

---

# 8. Demographics {.tabset}

## Age {.unnumbered}

```{r demo-age}
data %>%
  mutate(age = as.numeric(age)) %>%
  summarise(M = round(mean(age, na.rm = TRUE), 1), SD = round(sd(age, na.rm = TRUE), 1),
            Min = min(age, na.rm = TRUE), Max = max(age, na.rm = TRUE)) %>%
  reactable(compact = TRUE)

ggplot(data %>% mutate(age = as.numeric(age)), aes(x = age)) +
  geom_histogram(binwidth = 5, fill = palette_main, color = "white") +
  labs(x = "Age", y = "Count", title = "Age distribution") +
  plot_aes
```

## Gender {.unnumbered}

```{r demo-gender}
bar_single(data, "gender", title = "Gender identity")
freq_tab(data, "gender")
```

## Race / Ethnicity {.unnumbered}

```{r demo-race}
bar_single(data, "race", title = "Race / ethnicity")
freq_tab(data, "race")
```

## LGBTQ+ {.unnumbered}

```{r demo-lgbtq}
bar_single(data, "LGBTQ", title = "LGBTQ+ identity")
freq_tab(data, "LGBTQ")
```

## Education {.unnumbered}

```{r demo-edu}
bar_single(data, "ses_degree", title = "Highest education level", levels = lvl_degree)
freq_tab(data, "ses_degree", levels = lvl_degree)
```

## Income {.unnumbered}

```{r demo-income}
bar_single(data, "ses_income_household", title = "Household income", levels = lvl_income)
freq_tab(data, "ses_income_household", levels = lvl_income)
```

## Subjective SES {.unnumbered}

MacArthur ladder (1 = bottom, 10 = top): relative standing in the US by money, education, and job prestige.

```{r demo-ses-ladder}
data %>%
  filter(!is.na(ses_ladder)) %>%
  summarise(M = round(mean(ses_ladder), 1), SD = round(sd(ses_ladder), 1),
            Min = min(ses_ladder), Max = max(ses_ladder)) %>%
  reactable(compact = TRUE)

ggplot(data %>% filter(!is.na(ses_ladder)), aes(x = factor(ses_ladder))) +
  geom_bar(fill = palette_main) +
  labs(x = "Ladder rung", y = "Count", title = "Subjective SES (MacArthur ladder)") +
  plot_aes
```

## Political Ideology {.unnumbered}

```{r demo-ideology}
bar_single(data, "politics_ideology", title = "Political ideology", levels = lvl_ideology)
freq_tab(data, "politics_ideology", levels = lvl_ideology)
```

## Urbanicity {.unnumbered}

```{r demo-urban}
bar_single(data, "urbanicity", title = "Urbanicity")
freq_tab(data, "urbanicity")
```

## University Affiliation {.unnumbered}

```{r demo-affil}
bar_single(data, "univ_affiliate", title = "Current university affiliation")
freq_tab(data, "univ_affiliate")
```

---

# 9. Open-Ended Responses {.tabset}

## Effects of Research on You (research_3b) {.unnumbered}

"Please describe the positive or negative effects that academic research has had on you personally."

```{r oe-r3b}
data %>%
  select(research_3b) %>%
  filter(!is.na(research_3b), !research_3b %in% c("", "n/a", "N/A", "None", "none", "NA")) %>%
  rename(Response = research_3b) %>%
  reactable(striped = TRUE, filterable = TRUE,
            columns = list(Response = colDef(minWidth = 400)))
```

## Views on Federal Funding (govtfund_1b) {.unnumbered}

"Please describe your viewpoint on federal funding of academic research — why do you approve or disapprove?"

```{r oe-gf1b}
data %>%
  select(govtfund_1b) %>%
  filter(!is.na(govtfund_1b), !govtfund_1b %in% c("", "n/a", "N/A", "None", "none", "NA")) %>%
  rename(Response = govtfund_1b) %>%
  reactable(striped = TRUE, filterable = TRUE,
            columns = list(Response = colDef(minWidth = 400)))
```

## End-of-Survey Feedback {.unnumbered}

"Please type below any comments or suggestions you might have for the research team."

```{r oe-feedback}
data %>%
  select(end_feedback) %>%
  filter(!is.na(end_feedback), !end_feedback %in% c("", "n/a", "N/A", "None", "none", "NA")) %>%
  rename(Response = end_feedback) %>%
  reactable(striped = TRUE, filterable = TRUE,
            columns = list(Response = colDef(minWidth = 400)))
```
