---
title: "Step 1: Correlations with Behavioral Intentions"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, reactable, plotly)
```

```{r load-data}
path <- "~/Documents/GitHub/UniversityNews"

dir.create(file.path(path, "Output"), showWarnings = FALSE)

data <- readRDS(sprintf("%s/Data/Cleaned/UnivNews_Step1_combined.rds", path))

N <- nrow(data)
```

```{r scale-levels}
lvl_know         <- c("None at all","A little","A moderate amount","A lot","A great deal")
lvl_agree5       <- c("Strongly disagree","Somewhat disagree","Neither agree nor disagree",
                      "Somewhat agree","Strongly agree")
lvl_pos_neg      <- c("Extremely negative","Somewhat negative","Neither positive nor negative",
                      "Somewhat positive","Extremely positive")
lvl_importance   <- c("Not at all important","Slightly important","Moderately important",
                      "Very important","Extremely important")
lvl_likelihood_r <- c("Very unlikely","Somewhat unlikely","Neutral","Somewhat likely","Very likely")
lvl_problematic  <- c("Not at all problematic","Slightly problematic","Moderately problematic",
                      "Very problematic","Extremely problematic")
lvl_approve4     <- c("Strongly disapprove","Somewhat disapprove","Somewhat approve","Strongly approve")
lvl_approve5     <- c("Strongly disapprove","Somewhat disapprove","Neither approve nor disapprove",
                      "Somewhat approve","Strongly approve")
lvl_approve5_he  <- c("Strongly disapprove","Somewhat disapprove",
                      "Neutral / neither approve nor disapprove","Somewhat approve","Strongly approve")
lvl_likelihood_g <- c("Extremely unlikely","Somewhat unlikely","Neither likely nor unlikely",
                      "Somewhat likely","Extremely likely")
lvl_priority     <- c("Not a priority","Low priority","Somewhat priority",
                      "Moderate priority","High priority")
lvl_freq         <- c("Never","Once or twice a year","Once or twice a month",
                      "Once or twice a week","Almost every day","Once or more per day")
lvl_impact       <- c("Strong negative impact","Somewhat negative impact",
                      "Neither positive nor negative impact",
                      "Somewhat positive impact","Strong positive impact")
lvl_climate_trust <- c("Not at all","Slightly","Moderately","Very strongly")
lvl_proportion   <- c("None","Less than half","About half","Most","All")
lvl_intent       <- c("Definitely will not","Probably will not","Maybe will not",
                      "Unsure","Maybe will","Probably will","Definitely will")
lvl_ideology     <- c("Extremely liberal","Liberal","Slightly liberal","Moderate / middle of the road",
                      "Slightly conservative","Conservative","Extremely conservative")
lvl_degree       <- c("No formal education","Did not complete high school",
                      "High school graduate (diploma)","High school graduate (GED)",
                      "Some college (1-4 years, no degree)",
                      "Associate's degree (including occupational or academic degrees)",
                      "Bachelor's degree (BA, BS, etc.)",
                      "Master's degree (MA, MS, MEng, MSW, etc.)",
                      "Professional school degree (MD, DDC, JD, etc.)","Doctoral degree (PhD, EdD, etc.)")
lvl_income       <- c("Less than $5,000","$5,000 through $11,999","$12,000 through $15,999",
                      "$16,000 through $24,999","$25,000 through $34,999","$35,000 through $49,999",
                      "$50,000 through $74,999","$75,000 through $99,999",
                      "$100,000 through $149,999","$150,000 or greater",
                      "Prefer not to say / I don't know")
```

```{r to-num}
to_num <- function(x, levels) {
  as.integer(factor(x, levels = levels, ordered = TRUE))
}
```

```{r recode}
d <- data |>
  mutate(
    research_1  = to_num(research_1, lvl_know),
    research_2  = to_num(research_2, lvl_agree5),
    across(paste0("research_3_",   1:13), \(x) to_num(x, lvl_pos_neg)),
    across(paste0("research_4_",   1:8),  \(x) to_num(x, lvl_agree5)),
    across(paste0("research_5.1_", 1:13), \(x) to_num(x, lvl_importance)),
    across(paste0("research_5.2_", 1:13), \(x) to_num(x, lvl_likelihood_r)),
    across(paste0("research_6.1_", 1:11), \(x) to_num(x, lvl_problematic)),
    across(paste0("research_6.2_", 1:11), \(x) to_num(x, lvl_likelihood_r)),
    govtfund_1 = to_num(govtfund_1, lvl_approve4),
    govtfund_2 = case_when(
      grepl("ESSENTIAL", govtfund_2) ~ 1L,
      govtfund_2 == ""               ~ NA_integer_,
      TRUE                           ~ 0L
    ),
    govtfund_3  = to_num(govtfund_3, lvl_know),
    across(paste0("govtfund_4_", 1:13), \(x) to_num(x, lvl_approve5)),
    across(paste0("govtfund_5_", 1:10), \(x) to_num(x, lvl_likelihood_g)),
    across(paste0("gotvfund_6_", 1:9),  \(x) to_num(x, lvl_agree5)),
    across(paste0("govtfund_7_", 1:4),  \(x) to_num(x, lvl_priority)),
    across(paste0("govtfund_8_", 1:7),  \(x) to_num(x, lvl_agree5)),
    across(paste0("govtfund_9_", 1:5),  \(x) to_num(x, lvl_approve5)),
    govfund_10  = to_num(govfund_10, lvl_impact),
    across(paste0("past_engage_", 1:7), \(x) to_num(x, lvl_freq)),
    across(paste0("highered_1_", 1:3), \(x) to_num(x, lvl_approve5_he)),
    across(paste0("highered_2_", 1:3), \(x) to_num(x, lvl_know)),
    across(paste0("highered_3_", 1:6), \(x) to_num(x, lvl_know)),
    across(paste0("highered_4_", 1:6), \(x) to_num(x, lvl_proportion)),
    across(paste0("univ_2_", 1:10), \(x) to_num(x, lvl_agree5)),
    across(paste0("univ_4_", 1:3),  \(x) to_num(x, lvl_agree5)),
    across(paste0("univ_5_", 1:7),  \(x) to_num(x, lvl_know)),
    climate_1 = case_when(climate_1 == "Yes" ~ 1L, climate_1 == "No" ~ 0L, TRUE ~ NA_integer_),
    climate_2 = case_when(
      grepl("humans", climate_2, ignore.case = TRUE) ~ 1L,
      climate_2 == ""                                ~ NA_integer_,
      TRUE                                           ~ 0L
    ),
    climate_3  = to_num(climate_3, lvl_climate_trust),
    across(paste0("climate_4_", 1:4), \(x) to_num(x, lvl_importance)),
    age               = as.numeric(age),
    ses_ladder        = as.numeric(ses_ladder),
    politics_ideology = to_num(politics_ideology, lvl_ideology),
    ses_degree        = to_num(ses_degree, lvl_degree),
    ses_income        = to_num(ses_income_household, lvl_income),
    lgbtq             = case_when(LGBTQ == "Yes" ~ 1L, LGBTQ == "No" ~ 0L, TRUE ~ NA_integer_)
  )
```

```{r intents}
intent_cols <- paste0("X", 1:4, "_intent")
intent_labels <- c(
  "Contact reps to oppose cuts",
  "Talk to others about cuts",
  "Share info online about cuts",
  "Contact reps to support funding"
)

d <- d |>
  mutate(
    across(all_of(intent_cols), \(x) to_num(x, lvl_intent)),
    intent_composite = rowMeans(pick(all_of(intent_cols)), na.rm = TRUE)
  )
```

```{r registry}
make_entries <- function(cols, labels, block) {
  map2(cols, labels, \(c, l) list(col = c, label = l, block = block))
}

registry <- c(
  list(list(col = "research_1", label = "Knowledge of university research", block = "Research Beliefs")),
  list(list(col = "research_2", label = "Scientific methods are the best way to find truth", block = "Research Beliefs")),
  make_entries(
    paste0("research_3_", 1:13),
    paste("Effects on:", c("You personally","People you care about","Local community","People in the US",
                           "Students at universities","Scientists at universities","Universities themselves",
                           "Pharmaceutical companies","Technology companies","The military",
                           "The US government","Wealthy individuals","Disadvantaged individuals")),
    "Research Beliefs"
  ),
  make_entries(
    paste0("research_4_", 1:8),
    c("I usually understand academic research findings",
      "I know where to look up academic research",
      "Clear how to apply research findings in my life",
      "I think about the impact of science on my daily life",
      "Benefits of scientific research outweigh harms",
      "Science makes our way of life change too fast",
      "Scientific research will create opportunities for next generation",
      "Research advancing knowledge is necessary even w/o immediate benefits"),
    "Research Beliefs"
  ),
  make_entries(
    paste0("research_5.1_", 1:13),
    paste("Importance:", c("Advancing social science","Developing new medicines",
                           "Protecting the environment","Developing new energy technologies",
                           "Technologies for economic growth","Innovative manufacturing",
                           "Defense and national security technologies","AI and machine learning",
                           "Exploring space","Improving education systems",
                           "Better public policies","Helping individuals improve their lives",
                           "Awareness of others' experiences")),
    "Research Beliefs"
  ),
  make_entries(
    paste0("research_5.2_", 1:13),
    paste("Likelihood:", c("Advancing social science","Developing new medicines",
                           "Protecting the environment","Developing new energy technologies",
                           "Technologies for economic growth","Innovative manufacturing",
                           "Defense and national security technologies","AI and machine learning",
                           "Exploring space","Improving education systems",
                           "Better public policies","Helping individuals improve their lives",
                           "Awareness of others' experiences")),
    "Research Beliefs"
  ),
  make_entries(
    paste0("research_6.1_", 1:11),
    paste("Problematic:", c("Researchers make mistakes","Research is slow to have impact",
                            "Few people can access results","Findings don't generalize",
                            "Studies fail to yield results","Research wastes money",
                            "New tech eliminates jobs","New tech invades privacy",
                            "Research creates dangerous technology","Findings are misused",
                            "Results reporting is biased by media")),
    "Research Beliefs"
  ),
  make_entries(
    paste0("research_6.2_", 1:11),
    paste("Neg. likelihood:", c("Researchers make mistakes","Research is slow to have impact",
                                "Few people can access results","Findings don't generalize",
                                "Studies fail to yield results","Research wastes money",
                                "New tech eliminates jobs","New tech invades privacy",
                                "Research creates dangerous technology","Findings are misused",
                                "Results reporting is biased by media")),
    "Research Beliefs"
  ),
  list(list(col = "govtfund_1", label = "Approval of federal funding for university research", block = "Govt Funding")),
  list(list(col = "govtfund_2", label = "Govt investment is ESSENTIAL (vs. private sufficient)", block = "Govt Funding")),
  list(list(col = "govtfund_3", label = "Knowledge of funding cuts", block = "Govt Funding")),
  make_entries(
    paste0("govtfund_4_", 1:13),
    paste("Perceived support:", c("People who directly benefit","Students at universities",
                                  "Scientists at universities","The general public","People in the military",
                                  "People who identify as liberals","People who identify as conservatives",
                                  "People who favor minimal govt spending","Politicians",
                                  "People who don't believe in mainstream science",
                                  "Medical and mental health professionals",
                                  "Pharmaceutical companies","Technology companies")),
    "Govt Funding"
  ),
  make_entries(
    paste0("govtfund_5_", 1:10),
    paste("Govt funding likelihood:", c("Researchers have enough resources","Research can focus long-term",
                                        "Exciting research is sped up","Results become publicly available",
                                        "Funded researchers held to higher standards",
                                        "Money spent on less important things","Taxpayer money is wasted",
                                        "Research delayed by oversight","Political agendas influence funding",
                                        "Researchers lie to maintain funding")),
    "Govt Funding"
  ),
  make_entries(
    paste0("gotvfund_6_", 1:9),
    c("Rules should ensure govt-funded research is done well",
      "Oversight committees protect against unethical research",
      "Many everyday tools are the result of academic research",
      "University research benefits lives in ways hard to see",
      "University researchers motivated primarily by profit",
      "Private companies research primarily to benefit the public",
      "Govt-funded research is more objective than privately funded",
      "Private company research is biased toward company interests",
      "Results of private company research will become publicly accessible"),
    "Govt Funding"
  ),
  make_entries(
    paste0("govtfund_7_", 1:4),
    paste("Priority:", c("Making a profit","Advance knowledge and benefit society",
                         "Develop products that can be sold","Serve interests of the government")),
    "Govt Funding"
  ),
  make_entries(
    paste0("govtfund_8_", 1:7),
    paste("Tax investment:", c("...boosts the economy","...improves health and saves lives",
                               "...drives industry investment","...makes America a leader",
                               "...protects national security","...leads to scientific breakthroughs",
                               "...benefits people like you")),
    "Govt Funding"
  ),
  make_entries(
    paste0("govtfund_9_", 1:5),
    paste("Approve cuts to:", c("Health research funding","Education funding","Science funding",
                                "Arts funding","Humanities funding")),
    "Govt Funding"
  ),
  list(list(col = "govfund_10", label = "Local area would be negatively impacted by cuts", block = "Govt Funding")),
  make_entries(
    paste0("past_engage_", 1:7),
    c("Conversations about science topics","Shared/commented social media posts about science",
      "Attended rallies or protests about science",
      "Shared info online about cuts to research funding",
      "Talked to others about cuts to research funding",
      "Contacted reps to oppose cuts to research funding",
      "Contacted reps to support research funding"),
    "Past Engagement"
  ),
  make_entries(
    paste0("highered_1_", 1:3),
    paste("Approval:", c("Private colleges and universities","State public university system",
                         "Local community college(s)")),
    "Higher Education"
  ),
  make_entries(
    paste0("highered_2_", 1:3),
    paste("Trust:", c("Private colleges and universities","State public university system",
                      "Local community college(s)")),
    "Higher Education"
  ),
  make_entries(
    paste0("highered_3_", 1:6),
    paste("Contribution to science:", c("Private colleges and universities",
                                        "Private companies (pharma, tech)","Federal government agencies",
                                        "Charitable foundations","State colleges and universities",
                                        "Community colleges")),
    "Higher Education"
  ),
  make_entries(
    paste0("highered_4_", 1:6),
    paste("Proportion nonprofit:", c("Private colleges and universities",
                                     "Public state colleges and universities","Community colleges",
                                     "Private companies (pharma, tech)","Federal government agencies",
                                     "Charitable foundations")),
    "Higher Education"
  ),
  make_entries(
    paste0("univ_2_", 1:10),
    paste("Univ. contributes to:", c("Greater innovation","Better jobs and career advancement",
                                     "Higher household incomes","A more knowledgeable population",
                                     "US competitive advantage","More entrepreneurship",
                                     "Increased compassion and tolerance","Overall economic growth",
                                     "Better international relations","Benefits to local communities")),
    "University Perceptions"
  ),
  make_entries(
    paste0("univ_4_", 1:3),
    c("Universities discover new knowledge","Universities apply and connect knowledge",
      "Universities apply knowledge-based solutions"),
    "University Perceptions"
  ),
  make_entries(
    paste0("univ_5_", 1:7),
    paste("Benefits:", c("You personally","People you care about","Local communities",
                         "Students who attend","Students' families","Employers and businesses",
                         "Society as a whole")),
    "University Perceptions"
  ),
  list(list(col = "climate_1", label = "Believes global warming is happening", block = "Climate")),
  list(list(col = "climate_2", label = "Believes global warming is caused by humans", block = "Climate")),
  list(list(col = "climate_3", label = "Trust in climate scientists", block = "Climate")),
  make_entries(
    paste0("climate_4_", 1:4),
    paste("Climate research importance:", c("Climate science and earth systems",
                                            "Climate mitigation approaches",
                                            "Climate adaptation and resilience",
                                            "Climate policy, economics, and human impact")),
    "Climate"
  ),
  list(list(col = "age",               label = "Age",                       block = "Demographics")),
  list(list(col = "ses_ladder",        label = "Subjective SES (ladder)",   block = "Demographics")),
  list(list(col = "politics_ideology", label = "Political ideology (liberal → conservative)", block = "Demographics")),
  list(list(col = "ses_degree",        label = "Education level",           block = "Demographics")),
  list(list(col = "ses_income",        label = "Household income",          block = "Demographics")),
  list(list(col = "lgbtq",             label = "LGBTQ+ identity",           block = "Demographics"))
)
```

```{r correlations}
outcome_cols   <- c(intent_cols, "intent_composite")

cor_results <- map_dfr(registry, function(entry) {
  x <- d[[entry$col]]
  cors <- map_dfc(outcome_cols, function(oc) {
    y       <- d[[oc]]
    ct      <- suppressWarnings(cor.test(x, y, method = "spearman", exact = FALSE))
    n_pairs <- sum(!is.na(x) & !is.na(y))
    se      <- sqrt((1 - ct$estimate^2) / max(n_pairs - 2, 1))
    tibble(r = round(ct$estimate, 3), p = round(ct$p.value, 3), se = round(se, 3))
  }) |>
    set_names(nm = as.vector(
      outer(c("r_","p_","se_"), c("intent1","intent2","intent3","intent4","composite"), paste0)
    ))
  bind_cols(tibble(variable = entry$col, label = entry$label, block = entry$block), cors)
})

results <- cor_results |>
  mutate(abs_r_composite = abs(r_composite)) |>
  arrange(desc(abs_r_composite))
```

```{r save-csv}
write_csv(
  results |> select(-abs_r_composite),
  file.path(path, "Output", "03_correlations_intent.csv")
)
```

**N = `r N`** (Cohorts 1–3 combined). Spearman correlations between all predictor variables and each of the four behavioral intention items, plus their mean composite. Sorted by |r| with composite. p-values are exploratory only.

---

# Outcome measures

```{r intent-corr-table}
intent_labels_short <- c("Oppose cuts", "Talk to others", "Share online", "Support funding")

intent_cor <- d |>
  select(all_of(intent_cols)) |>
  setNames(intent_labels_short) |>
  cor(method = "spearman", use = "pairwise.complete.obs") |>
  round(2) |>
  as.data.frame() |>
  tibble::rownames_to_column("Outcome")

intent_desc <- d |>
  select(all_of(intent_cols)) |>
  setNames(intent_labels_short) |>
  summarise(across(everything(), list(
    Mean = \(x) round(mean(x, na.rm = TRUE), 2),
    SD   = \(x) round(sd(x,   na.rm = TRUE), 2)
  ))) |>
  tidyr::pivot_longer(everything(), names_to = c("Outcome", ".value"), names_sep = "_")

intent_cor |>
  left_join(intent_desc, by = "Outcome") |>
  reactable(
    striped    = TRUE,
    compact    = TRUE,
    pagination = FALSE,
    columns    = list(
      Outcome        = colDef(minWidth = 160, style = list(fontWeight = "bold")),
      `Talk to others`   = colDef(width = 110, align = "center"),
      `Share online`     = colDef(width = 110, align = "center"),
      `Oppose cuts`      = colDef(width = 110, align = "center"),
      `Support funding`  = colDef(width = 120, align = "center"),
      Mean = colDef(width = 70,  align = "center"),
      SD   = colDef(width = 70,  align = "center")
    )
  )
```

Spearman correlations among the four behavioral intention outcomes (N = `r N`). Scale: 1 = *Definitely will not*, 7 = *Definitely will*. The Oppose ↔ Support pairing is the strongest (r = `r intent_cor |> filter(Outcome == "Oppose cuts") |> pull("Support funding")`), consistent with both being representative-contact behaviors. Talk to others is the most distinct from the other three.

---

# Results {.tabset}

```{r split-results}
beliefs_results <- results |> filter(block != "Past Engagement")
past_results    <- results |> filter(block == "Past Engagement")

block_colors <- c(
  "Research Beliefs"       = "#4E79A7",
  "Govt Funding"           = "#F28E2B",
  "Higher Education"       = "#59A14F",
  "University Perceptions" = "#76B7B2",
  "Climate"                = "#EDC948",
  "Demographics"           = "#B07AA1"
)

make_top20_plot <- function(r_col, se_col, p_col, x_label) {
  top20 <- beliefs_results |>
    mutate(abs_r = abs(.data[[r_col]])) |>
    arrange(desc(abs_r)) |>
    slice_head(n = 20)

  p <- top20 |>
    mutate(
      label_wrap = fct_reorder(str_wrap(label, width = 42), .data[[r_col]]),
      r_lo     = .data[[r_col]] - .data[[se_col]],
      r_hi     = .data[[r_col]] + .data[[se_col]],
      sig      = case_when(.data[[p_col]] < .001 ~ "***",
                           .data[[p_col]] < .01  ~ "**",
                           .data[[p_col]] < .05  ~ "*",
                           TRUE                  ~ ""),
      tip_text = paste0(
        "<b>", label, "</b><br>",
        "Block: ", block, "<br>",
        "r = ", .data[[r_col]], " ± ", .data[[se_col]], " SE",
        "  (p = ", .data[[p_col]], ")", sig
      )
    ) |>
    ggplot(aes(x = .data[[r_col]], y = label_wrap, color = block, text = tip_text)) +
    geom_segment(aes(x = 0, xend = .data[[r_col]], yend = label_wrap),
                 color = "gray82", linewidth = 0.6) +
    geom_errorbarh(aes(xmin = r_lo, xmax = r_hi),
                   height = 0.3, linewidth = 0.5, color = "gray55") +
    geom_point(size = 3.5) +
    scale_color_manual(values = block_colors, name = NULL) +
    scale_x_continuous(limits = c(0, 0.75), breaks = seq(0, 0.7, 0.1),
                       labels = c("0", "0.1", "0.2", "0.3", "0.4", "0.5", "0.6", "0.7")) +
    labs(x = x_label, y = NULL,
         caption = "Error bars = ±1 SE. Sorted by |r|; Past Engagement excluded. * p<.05  ** p<.01  *** p<.001") +
    theme_minimal(base_size = 11) +
    theme(
      legend.position    = "bottom",
      panel.grid.major.y = element_blank(),
      panel.grid.minor   = element_blank(),
      axis.text.y        = element_text(size = 9, lineheight = 1.2),
      axis.text.x        = element_text(size = 10),
      axis.title.x       = element_text(size = 10, margin = margin(t = 8))
    )

  ggplotly(p, tooltip = "text") |>
    layout(
      legend = list(orientation = "h", y = -0.12),
      margin = list(l = 220, b = 60),
      xaxis  = list(tickfont = list(size = 12), title = list(font = list(size = 12)))
    )
}
```

## Composite Intent

### Top 20 predictors {-}

```{r top20-composite, fig.height=9, fig.width=10}
make_top20_plot("r_composite", "se_composite", "p_composite",
                "Spearman r  (composite intent)")
```

### All items {-}

```{r beliefs-table}
cor_table <- function(df) {
  df |>
    select(block, label, r_composite, p_composite,
           r_intent1, r_intent2, r_intent3, r_intent4) |>
    rename(
      Block                 = block,
      Predictor             = label,
      `r (composite)`       = r_composite,
      `p (composite)`       = p_composite,
      `r (oppose cuts)`     = r_intent1,
      `r (talk to others)`  = r_intent2,
      `r (share online)`    = r_intent3,
      `r (support funding)` = r_intent4
    ) |>
    reactable(
      filterable      = TRUE,
      sortable        = TRUE,
      striped         = TRUE,
      compact         = TRUE,
      defaultPageSize = 25,
      columns = list(
        Predictor       = colDef(minWidth = 260),
        `r (composite)` = colDef(
          style = function(value) {
            color <- if (is.numeric(value) && value > 0) "#2166ac"
                     else if (is.numeric(value) && value < 0) "#d6604d"
                     else "black"
            list(color = color, fontWeight = "bold")
          }
        )
      )
    )
}

cor_table(beliefs_results)
```

## Oppose cuts (intent 1)

### Top 20 predictors {-}

```{r top20-intent1, fig.height=9, fig.width=10}
make_top20_plot("r_intent1", "se_intent1", "p_intent1",
                "Spearman r  (contact reps to oppose cuts)")
```

### All items {-}

```{r table-intent1}
cor_table(beliefs_results)
```

## Talk to others (intent 2)

### Top 20 predictors {-}

```{r top20-intent2, fig.height=9, fig.width=10}
make_top20_plot("r_intent2", "se_intent2", "p_intent2",
                "Spearman r  (talk to others about cuts)")
```

### All items {-}

```{r table-intent2}
cor_table(beliefs_results)
```

## Share online (intent 3)

### Top 20 predictors {-}

```{r top20-intent3, fig.height=9, fig.width=10}
make_top20_plot("r_intent3", "se_intent3", "p_intent3",
                "Spearman r  (share info online about cuts)")
```

### All items {-}

```{r table-intent3}
cor_table(beliefs_results)
```

## Support funding (intent 4)

### Top 20 predictors {-}

```{r top20-intent4, fig.height=9, fig.width=10}
make_top20_plot("r_intent4", "se_intent4", "p_intent4",
                "Spearman r  (contact reps to support funding)")
```

### All items {-}

```{r table-intent4}
cor_table(beliefs_results)
```

## Past Engagement

Included for reference. These items reflect prior behavior rather than modifiable beliefs, so they are shown separately.

```{r past-table}
cor_table(past_results)
```
