---
title: "Step 1: Belief Network Analysis"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, qgraph, igraph, ggrepel, reactable, RColorBrewer)
```

# Overview

Belief network analysis following Lydic, Torres-Grillo, Levine, Cosme et al. (2025).
Pipeline: GLASSO partial correlation network → walktrap community detection →
eigenvector centrality → combine with Hornik & Woolf PTG to identify priority targets.

**Node selection note (2026-05-20):** Subscale means are used only for batteries
with internally consistent items (Cronbach α ≥ 0.65). Three batteries were revised:
`research_4` split into literacy/engagement (items 1–4, α = 0.750) and benefit beliefs
(items 5, 7, 8, α = 0.677) — item 6 dropped (reverse-coded item that does not behave
as expected empirically); `govtfund_4` restricted to non-partisan stakeholder items
(items 1–5, 11–13, α = 0.835) — partisan perception items (6–10) dropped; `gotvfund_6`
restricted to items 2–4, 7 (α = 0.694) — private-company comparison items and
profit-motive item dropped. Node selection finalized at N = 300.

**PTG note:** Percentage-to-gain follows Hornik & Woolf (1999). For single Likert / binary
items "strong" endorsement is the *scale endpoint* ("strongly (dis)agree"), matching the reference
method. The four continuous composites have no natural endpoint, so for those (only) we substitute
the top/bottom quartile. Thresholds based on full N = 300 sample. See Section 7.

**Correspondence to the reference method (Lydic et al., 2025; OSF a6xf5):**

| Step | Reference paper | This script |
|---|---|---|
| Network model | Gaussian Graphical Model, GLASSO-regularized (`qgraph`) | `qgraph::EBICglasso`, γ = 0.5 |
| Correlation input | ordinal-appropriate (belief-network standard) | `qgraph::cor_auto` (polychoric / polyserial / Pearson) |
| Community detection | walktrap (`igraph`) | `cluster_walktrap` on absolute weights |
| Centrality | eigenvector; validated vs. belief–intention r (Fisher-z, abs) | same |
| Promising beliefs | Hornik & Woolf percentage-to-gain (scale endpoint) | same (§7) |

**This revision (2026-07-15)** fixed bugs in the prior version: (1) network estimated from
ordinal-appropriate correlations (`cor_auto`) instead of Pearson; (2) all downstream objects keyed
by node id, removing a fragile display-label round-trip that could mis-map communities/centrality;
(3) percentage-to-gain now uses the H&W scale-endpoint rule for items (quartiles only for the four
continuous composites) rather than a blanket 75th-percentile split; (4) added the Fisher-z transform
to the centrality-validation step; (5) removed dead code and the stale "N = 10 pilot" note.

---

# 1. Data

## 1.1 Load and clean

```{r load}
path <- "~/Documents/GitHub/UniversityNews"

data <- readRDS(sprintf("%s/Data/Cleaned/UnivNews_Step1_combined.rds", path))

cat(sprintf("N = %d\n", nrow(data)))
```

## 1.2 Scale levels and numeric recoding

```{r scale-levels}
lvl_know         <- c("None at all","A little","A moderate amount","A lot","A great deal")
lvl_agree5       <- c("Strongly disagree","Somewhat disagree","Neither agree nor disagree",
                      "Somewhat agree","Strongly agree")
lvl_pos_neg      <- c("Extremely negative","Somewhat negative","Neither positive nor negative",
                      "Somewhat positive","Extremely positive")
lvl_importance   <- c("Not at all important","Slightly important","Moderately important",
                      "Very important","Extremely important")
lvl_likelihood_r <- c("Very unlikely","Somewhat unlikely","Neutral","Somewhat likely","Very likely")
lvl_problematic  <- c("Not at all problematic","Slightly problematic","Moderately problematic",
                      "Very problematic","Extremely problematic")
lvl_approve4     <- c("Strongly disapprove","Somewhat disapprove","Somewhat approve","Strongly approve")
lvl_approve5     <- c("Strongly disapprove","Somewhat disapprove","Neither approve nor disapprove",
                      "Somewhat approve","Strongly approve")
lvl_approve5_he  <- c("Strongly disapprove","Somewhat disapprove",
                      "Neutral / neither approve nor disapprove","Somewhat approve","Strongly approve")
lvl_likelihood_g <- c("Extremely unlikely","Somewhat unlikely","Neither likely nor unlikely",
                      "Somewhat likely","Extremely likely")
lvl_priority     <- c("Not a priority","Low priority","Somewhat priority",
                      "Moderate priority","High priority")
lvl_freq         <- c("Never","Once or twice a year","Once or twice a month",
                      "Once or twice a week","Almost every day","Once or more per day")
lvl_impact       <- c("Strong negative impact","Somewhat negative impact",
                      "Neither positive nor negative impact",
                      "Somewhat positive impact","Strong positive impact")
lvl_climate_trust <- c("Not at all","Slightly","Moderately","Very strongly")
lvl_proportion   <- c("None","Less than half","About half","Most","All")
lvl_intent       <- c("Definitely will not","Probably will not","Maybe will not",
                      "Unsure","Maybe will","Probably will","Definitely will")

to_num <- function(x, levels) {
  as.integer(factor(x, levels = levels, ordered = TRUE))
}
```

```{r recode}
d <- data |>
  mutate(
    # ── Research beliefs ─────────────────────────────────────────────────────
    research_1  = to_num(research_1, lvl_know),
    research_2  = to_num(research_2, lvl_agree5),

    across(paste0("research_3_",   1:13), \(x) to_num(x, lvl_pos_neg)),
    across(paste0("research_4_",   1:8),  \(x) to_num(x, lvl_agree5)),
    across(paste0("research_5.1_", 1:13), \(x) to_num(x, lvl_importance)),
    across(paste0("research_5.2_", 1:13), \(x) to_num(x, lvl_likelihood_r)),
    across(paste0("research_6.1_", 1:11), \(x) to_num(x, lvl_problematic)),
    across(paste0("research_6.2_", 1:11), \(x) to_num(x, lvl_likelihood_r)),

    # ── Government funding ───────────────────────────────────────────────────
    govtfund_1 = to_num(govtfund_1, lvl_approve4),
    govtfund_2 = case_when(
      grepl("ESSENTIAL", govtfund_2) ~ 1L,
      govtfund_2 == ""               ~ NA_integer_,
      TRUE                           ~ 0L
    ),
    govtfund_3  = to_num(govtfund_3, lvl_know),

    across(paste0("govtfund_4_", 1:13), \(x) to_num(x, lvl_approve5)),
    across(paste0("govtfund_5_", 1:10), \(x) to_num(x, lvl_likelihood_g)),
    across(paste0("gotvfund_6_", 1:9),  \(x) to_num(x, lvl_agree5)),
    across(paste0("govtfund_7_", 1:4),  \(x) to_num(x, lvl_priority)),
    across(paste0("govtfund_8_", 1:7),  \(x) to_num(x, lvl_agree5)),
    across(paste0("govtfund_9_", 1:5),  \(x) to_num(x, lvl_approve5)),

    govfund_10  = to_num(govfund_10, lvl_impact),

    # ── Higher education ─────────────────────────────────────────────────────
    across(paste0("highered_1_", 1:3), \(x) to_num(x, lvl_approve5_he)),
    across(paste0("highered_2_", 1:3), \(x) to_num(x, lvl_know)),
    across(paste0("highered_3_", 1:6), \(x) to_num(x, lvl_know)),
    across(paste0("highered_4_", 1:6), \(x) to_num(x, lvl_proportion)),

    # ── University perceptions ───────────────────────────────────────────────
    across(paste0("univ_2_", 1:10), \(x) to_num(x, lvl_agree5)),
    across(paste0("univ_4_", 1:3),  \(x) to_num(x, lvl_agree5)),
    across(paste0("univ_5_", 1:7),  \(x) to_num(x, lvl_know)),

    # ── Climate ──────────────────────────────────────────────────────────────
    climate_1 = case_when(climate_1 == "Yes" ~ 1L, climate_1 == "No" ~ 0L, TRUE ~ NA_integer_),
    climate_2 = case_when(
      grepl("humans", climate_2, ignore.case = TRUE) ~ 1L,
      climate_2 == ""                                ~ NA_integer_,
      TRUE                                           ~ 0L
    ),
    climate_3  = to_num(climate_3, lvl_climate_trust),
    across(paste0("climate_4_", 1:4), \(x) to_num(x, lvl_importance))
  )
```

## 1.3 Intent outcomes

```{r intent}
intent_cols   <- paste0("X", 1:4, "_intent")
intent_labels <- c(
  "Contact reps: oppose cuts",
  "Talk to others about cuts",
  "Share info online",
  "Contact reps: support funding"
)

d <- d |>
  mutate(
    across(all_of(intent_cols), \(x) to_num(x, lvl_intent)),
    intent_composite = rowMeans(pick(all_of(intent_cols)), na.rm = TRUE)
  )
```

---

# 2. Node construction

Nodes are defined here.

Two types:
- **Subscale means** — item batteries aggregated to a single score per construct (α ≥ 0.65)
- **Individual items** — standalone items or small batteries where items are conceptually distinct

`govtfund_5` is split into positive (items 1–5: benefits of govt funding) and negative
(items 6–10: costs/risks of govt funding) subscales because they have opposite valences.
`research_4` is split into science literacy/engagement (items 1–4) and science benefit
beliefs (items 5, 7, 8); item 6 ("Science makes our way of life change too fast") is
excluded because reversing it reduces rather than increases internal consistency,
suggesting it measures a distinct construct. `govtfund_4` uses items 1–5 and 11–13
(workers, students, scientists, general public, community members, health researchers,
pharma, tech) — partisan/political perception items 6–10 are excluded (α = 0.209 for
those items alone). `gotvfund_6` uses items 2–4, 7 (oversight, everyday tools, daily
benefits, objectivity of government-funded research); private-company comparison items
and profit-motive item excluded.

```{r nodes}
# ── Subscale means ────────────────────────────────────────────────────────────

d_nodes <- d |>
  mutate(
    # ── Research beliefs ───────────────────────────────────────────────────────
    # research_3: high-PTG items kept as individual nodes; residual national/political
    # impact items (4=US people, 11=US govt) retained as a 2-item subscale (α=0.669)
    research_3_nat_mean = rowMeans(pick(all_of(paste0("research_3_", c(4, 11)))), na.rm = TRUE),
    # research_3 items 1,2,3,13: individual nodes (high PTG; see Section 2.2)
    # research_4 items 1-3: all kept as individual nodes (residual 2-item α=0.642 < threshold)
    # research_4 benefit items 5, 7, 8: individual nodes (no mean)
    # govtfund_5 items 1-10: all individual nodes
    #   pos items (1-4): composite α=0.641 < threshold; all individualised
    #   neg items (6-10): pulling high-PTG items 6 and 10 leaves residual α=0.618 < threshold
    #   item 5 ("held to higher standards") already standalone

    # ── Climate ───────────────────────────────────────────────────────────────
    climate_4_mean      = rowMeans(pick(all_of(paste0("climate_4_", 1:4))), na.rm = TRUE)
  )

# ── Importance × likelihood composites ────────────────────────────────────────
# research_5: perceived value = importance × likelihood for each of 13 research areas
for (i in 1:13) d_nodes[[paste0(".r5p_", i)]] <-
  d_nodes[[paste0("research_5.1_", i)]] * d_nodes[[paste0("research_5.2_", i)]]
d_nodes$research_5_composite <- rowMeans(d_nodes[paste0(".r5p_", 1:13)], na.rm = TRUE)
d_nodes[paste0(".r5p_", 1:13)] <- NULL

# research_6: perceived risk = severity × likelihood for each of 11 negative outcomes
for (i in 1:11) d_nodes[[paste0(".r6p_", i)]] <-
  d_nodes[[paste0("research_6.1_", i)]] * d_nodes[[paste0("research_6.2_", i)]]
d_nodes$research_6_composite <- rowMeans(d_nodes[paste0(".r6p_", 1:11)], na.rm = TRUE)
d_nodes[paste0(".r6p_", 1:11)] <- NULL

# ── Select all nodes in one matrix ────────────────────────────────────────────

node_cols <- c(
  # Subscale means / composites (4 nodes)
  "research_3_nat_mean",                           # national impact (items 4,11; α=0.669)
  "research_5_composite", "research_6_composite",  # product composites
  "climate_4_mean",                                # climate research importance
  # Individual items — Research Beliefs (13 nodes)
  "research_1", "research_2",
  "research_3_1", "research_3_2", "research_3_3", "research_3_13",
  "research_4_1", "research_4_2", "research_4_3",
  "research_4_4", "research_4_5", "research_4_7", "research_4_8",
  # Individual items — Government Funding (30 nodes)
  "govtfund_1", "govtfund_2", "govtfund_3",
  "govtfund_5_1", "govtfund_5_2", "govtfund_5_3", "govtfund_5_4",
  "govtfund_5_5",
  "govtfund_5_6", "govtfund_5_7", "govtfund_5_8", "govtfund_5_9", "govtfund_5_10",
  "govtfund_7_1", "govtfund_7_2", "govtfund_7_3", "govtfund_7_4",
  "govtfund_8_1", "govtfund_8_2", "govtfund_8_3", "govtfund_8_4",
  "govtfund_8_5", "govtfund_8_6", "govtfund_8_7",
  "govtfund_9_1", "govtfund_9_2", "govtfund_9_3", "govtfund_9_4", "govtfund_9_5",
  "govfund_10",
  # Individual items — Higher Education (4 nodes)
  "highered_1_1", "highered_2_1", "highered_3_1", "highered_4_1",
  # Individual items — University Perceptions (4 nodes)
  "univ_2_7", "univ_2_9",
  "univ_5_1", "univ_5_2",
  # Individual items — Climate (3 nodes)
  "climate_1", "climate_2", "climate_3"
)

cat(sprintf("Total nodes: %d\n", length(node_cols)))
```

## 2.1 Node registry

Human-readable labels and block membership for each node.

```{r node-registry}
node_registry <- tribble(
  ~col,                        ~label,                                                              ~block,
  # ── Subscale means / composites (4 nodes) ────────────────────────────────────────────────────
  "research_3_nat_mean",       "Research impact: US people & government (nat. subscale)",           "Research Beliefs",
  "research_5_composite",      "Research value (importance × likelihood)",                          "Research Beliefs",
  "research_6_composite",      "Perceived research risk (severity × likelihood)",                   "Research Beliefs",
  "climate_4_mean",            "Climate research importance",                                       "Climate",
  # ── Individual items — Research Beliefs (13 nodes) ───────────────────────────────────────────
  "research_1",                "Knowledge of university research",                                  "Research Beliefs",
  "research_2",                "Science is the best way to find truth",                             "Research Beliefs",
  "research_3_1",              "Research impact: you personally",                                   "Research Beliefs",
  "research_3_2",              "Research impact: people you care about",                            "Research Beliefs",
  "research_3_3",              "Research impact: local community",                                  "Research Beliefs",
  "research_3_13",             "Research impact: disadvantaged individuals",                        "Research Beliefs",
  "research_4_1",              "Usually understand academic research findings",                      "Research Beliefs",
  "research_4_2",              "Know where to look up academic research",                           "Research Beliefs",
  "research_4_3",              "Clear how to apply research findings in my life",                   "Research Beliefs",
  "research_4_4",              "Often think about science impact on daily life",                    "Research Beliefs",
  "research_4_5",              "Science benefits outweigh harms",                                   "Research Beliefs",
  "research_4_7",              "Science creates opportunities for next generation",                 "Research Beliefs",
  "research_4_8",              "Basic science has value without immediate benefits",                "Research Beliefs",
  # ── Individual items — Government Funding (30 nodes) ─────────────────────────────────────────
  "govtfund_1",                "Approval of federal research funding",                              "Govt Funding",
  "govtfund_2",                "Govt investment in research is ESSENTIAL",                          "Govt Funding",
  "govtfund_3",                "Knowledge of recent funding cuts",                                  "Govt Funding",
  "govtfund_5_1",              "Govt funding benefit: researchers have enough resources",           "Govt Funding",
  "govtfund_5_2",              "Govt funding benefit: research can focus long-term",                "Govt Funding",
  "govtfund_5_3",              "Govt funding benefit: exciting research is sped up",                "Govt Funding",
  "govtfund_5_4",              "Govt funding benefit: results become publicly available",           "Govt Funding",
  "govtfund_5_5",              "Govt funding benefit: researchers held to higher standards",        "Govt Funding",
  "govtfund_5_6",              "Govt funding risk: money spent on less important things",           "Govt Funding",
  "govtfund_5_7",              "Govt funding risk: taxpayer money is wasted",                      "Govt Funding",
  "govtfund_5_8",              "Govt funding risk: research delayed by oversight",                  "Govt Funding",
  "govtfund_5_9",              "Govt funding risk: political agendas influence funding",            "Govt Funding",
  "govtfund_5_10",             "Govt funding risk: researchers lie to maintain funding",            "Govt Funding",
  "govtfund_7_1",              "Perceived university priority: making a profit",                    "Govt Funding",
  "govtfund_7_2",              "Perceived university priority: advance knowledge & society",        "Govt Funding",
  "govtfund_7_3",              "Perceived university priority: develop products to sell",           "Govt Funding",
  "govtfund_7_4",              "Perceived university priority: serve govt interests",               "Govt Funding",
  "govtfund_8_1",              "Tax investment in research: boosts economy",                        "Govt Funding",
  "govtfund_8_2",              "Tax investment in research: improves health & saves lives",         "Govt Funding",
  "govtfund_8_3",              "Tax investment in research: drives industry investment",            "Govt Funding",
  "govtfund_8_4",              "Tax investment in research: makes US a leader",                    "Govt Funding",
  "govtfund_8_5",              "Tax investment in research: protects national security",            "Govt Funding",
  "govtfund_8_6",              "Tax investment in research: leads to breakthroughs",               "Govt Funding",
  "govtfund_8_7",              "Tax investment in research: benefits people like you",              "Govt Funding",
  "govtfund_9_1",              "Approve cutting: health research funding",                          "Govt Funding",
  "govtfund_9_2",              "Approve cutting: education funding",                                "Govt Funding",
  "govtfund_9_3",              "Approve cutting: science funding",                                  "Govt Funding",
  "govtfund_9_4",              "Approve cutting: arts funding",                                     "Govt Funding",
  "govtfund_9_5",              "Approve cutting: humanities funding",                               "Govt Funding",
  "govfund_10",                "Local area negatively impacted by funding cuts",                    "Govt Funding",
  # ── Individual items — Higher Education (4 nodes) ────────────────────────────────────────────
  "highered_1_1",              "Approval: private colleges & universities",                         "Higher Education",
  "highered_2_1",              "Trust: private colleges & universities",                            "Higher Education",
  "highered_3_1",              "Scientific contribution: private colleges",                         "Higher Education",
  "highered_4_1",              "Perception: private colleges are nonprofit",                        "Higher Education",
  # ── Individual items — University Perceptions (4 nodes) ──────────────────────────────────────
  "univ_2_7",                  "Universities contribute: compassion & tolerance",                   "University Perceptions",
  "univ_2_9",                  "Universities contribute: better intl relationships",                "University Perceptions",
  "univ_5_1",                  "Universities benefit: you personally",                              "University Perceptions",
  "univ_5_2",                  "Universities benefit: people you care about",                       "University Perceptions",
  # ── Individual items — Climate (3 nodes) ─────────────────────────────────────────────────────
  "climate_1",                 "Believes global warming is happening",                              "Climate",
  "climate_2",                 "Believes warming caused by humans",                                 "Climate",
  "climate_3",                 "Trust in climate scientists",                                       "Climate"
)

cat(sprintf("Registry: %d nodes\n", nrow(node_registry)))
```

## 2.2 Node inclusion decisions

Documents all inclusion decisions relative to the full survey instrument.
Cronbach's α reported for subscale means; product composites do not have a
traditional α.

```{r inclusion-alpha}
alpha_raw <- function(cols) {
  mat <- na.omit(as.matrix(d[cols]))
  k   <- ncol(mat)
  if (k < 2 || var(rowSums(mat)) == 0) return(NA_real_)
  V <- var(mat)
  round((k / (k - 1)) * (1 - sum(diag(V)) / var(rowSums(mat))), 3)
}
```

### Subscale means and composites

```{r inclusion-subscales}
subscale_df <- tribble(
  ~Node,                   ~`Survey battery`,                    ~`k`,
  ~`Items included`,
  ~`Items dropped from battery`,
  ~alpha_cols,

  "research_3_nat_mean",
  "research_3 (13 items)", 2L,
  "Items 4,11 — impact on: people in the US, US government (national/political impact subscale)",
  "Items 1,2,3,13 kept as individual nodes (high PTG); items 5–10,12 dropped (not theoretically central)",
  list(paste0("research_3_", c(4, 11))),

  "research_5_composite",
  "research_5.1 × research_5.2 (13 areas × 2 ratings)", 13L,
  "All 13 research areas — importance × likelihood product per area, mean across areas",
  "None — all 13 areas used",
  list(NULL),

  "research_6_composite",
  "research_6.1 × research_6.2 (11 outcomes × 2 ratings)", 11L,
  "All 11 negative research outcomes — severity × likelihood product per outcome, mean across outcomes",
  "None — all 11 outcomes used",
  list(NULL),

  "climate_4_mean",
  "climate_4 (4 items)", 4L,
  "Items 1–4 — importance of climate science, climate mitigation, climate adaptation, climate policy research",
  "None — all 4 items used",
  list(paste0("climate_4_", 1:4))
) |>
  mutate(
    α = map_chr(alpha_cols, \(cols) {
      if (is.null(cols[[1]])) return("product composite")
      as.character(alpha_raw(cols[[1]]))
    })
  ) |>
  select(-alpha_cols)

reactable(
  subscale_df,
  columns = list(
    Node              = colDef(minWidth = 160),
    `Survey battery`  = colDef(minWidth = 160),
    k                 = colDef(maxWidth = 40),
    `Items included`  = colDef(minWidth = 220),
    `Items dropped from battery` = colDef(minWidth = 220),
    α                 = colDef(maxWidth = 120)
  ),
  striped = TRUE, wrap = TRUE
)
```

### Individual items

All `r nrow(filter(node_registry, !grepl("_mean$|_composite$", col)))` individual items retained in the network:

```{r inclusion-individual}
node_registry |>
  filter(!grepl("_mean$|_composite$", col)) |>
  select(block, col, label) |>
  rename(Block = block, Variable = col, `Survey item` = label) |>
  reactable(striped = TRUE, sortable = TRUE, filterable = TRUE, groupBy = "Block")
```

### Dropped batteries and items

```{r inclusion-dropped}
dropped_df <- tribble(
  ~`Battery / item`,                     ~`Original k`, ~`Reason for exclusion`,

  "research_4_6",
  "1 item",
  "Reverse-coded item ('Science makes our way of life change too fast'): reversing it reduces rather than increases internal consistency (α drops from 0.715 to 0.652), indicating it measures a distinct construct",

  "research_3 items 5,6,7,8,9,10,12",
  "7 of 13 items",
  "Beneficiary targets not theoretically central to this study: students, scientists, universities themselves, pharma companies, tech companies, military, wealthy individuals. Items 1,2,3,13 kept as individual nodes; items 4,11 retained in research_3_nat_mean subscale.",

  "govtfund_4 (all 13 items)",
  "13 items",
  "Perceived stakeholder support for research funding: dropped entirely. Partisan perception items (liberals, conservatives, politicians, climate skeptics, limited-govt advocates) had α = 0.21 in isolation, destroying overall battery coherence (full-battery α = 0.67)",

  "govtfund_6 (all 9 items)",
  "9 items",
  "Heterogeneous battery (full α = 0.41): combines research governance beliefs, everyday-benefit claims, and private-company comparisons that measure distinct constructs and do not form a coherent scale",

  "highered_1 items 2–3",
  "2 of 3 items",
  "Restricted to private colleges only: state university system and community college items dropped",

  "highered_2 items 2–3",
  "2 of 3 items",
  "Restricted to private colleges only: state university system and community college items dropped",

  "highered_3 items 2–6",
  "5 of 6 items",
  "Restricted to private colleges only: private companies, federal agencies, charitable foundations, state colleges, community colleges dropped",

  "highered_4 items 2–6",
  "5 of 6 items",
  "Restricted to private colleges only: public colleges, community colleges, private companies, federal agencies, charitable foundations dropped",

  "univ_5 items 3–7",
  "5 of 7 items",
  "Restricted to personal benefit perception: local communities, students who attend, students' families, employers and businesses, society as a whole dropped",

  "univ_2 items 1–6, 8, 10",
  "8 of 10 items",
  "Low composite PTG (lb < 4%) and high node count: innovation, jobs, incomes, knowledgeable population, competitiveness, entrepreneurship, economic growth, local benefits dropped. Items 7 (compassion & tolerance, lb=6.7%) and 9 (intl relations, lb=5.9%) retained as individual nodes.",

  "univ_4 (all 3 items)",
  "3 items",
  "Low composite PTG (lb < 4%) across all outcomes and theoretical overlap with research_4 literacy items: dropped entirely to reduce node count.",

  "research_4_literacy_mean",
  "3 items (formerly composite)",
  "Composite α = 0.720 but residual 2-item composite after extracting r4_3 would fall to α = 0.642, below the 0.65 threshold. All three items (1,2,3) retained as individual nodes.",

  "govtfund_5_pos_mean",
  "4 items (formerly composite)",
  "Full composite α = 0.641, below threshold. All four items retained as individual nodes.",

  "govtfund_5_neg_mean",
  "5 items (formerly composite)",
  "Extracting high-PTG items 6 and 10 as individual nodes leaves residual α = 0.618, below threshold. All five items retained as individual nodes."
)

reactable(
  dropped_df,
  columns = list(
    `Battery / item`       = colDef(minWidth = 180),
    `Original k`           = colDef(maxWidth = 90),
    `Reason for exclusion` = colDef(minWidth = 300)
  ),
  striped = TRUE, wrap = TRUE
)
```

---

# 3. Correlations: nodes × intent outcomes

Spearman r used throughout (ordinal data on different scales).

```{r node-intent-cors}
cor_fun <- function(x, y) {
  suppressWarnings(cor.test(x, y, method = "spearman", exact = FALSE)) |>
    broom::tidy() |>
    select(estimate, p.value) |>
    rename(r = estimate, p = p.value)
}

node_cors <- map_dfr(node_cols, function(nc) {
  x <- d_nodes[[nc]]
  map_dfr(seq_along(intent_cols), function(i) {
    y <- d_nodes[[intent_cols[i]]]
    ct <- cor_fun(x, y)
    tibble(node = nc, outcome = intent_labels[i],
           r = round(ct$r, 3), p = round(ct$p, 3))
  }) |>
    bind_rows(
      tibble(node = nc, outcome = "Composite",
             r    = round(suppressWarnings(cor(x, d_nodes$intent_composite,
                                               method = "spearman",
                                               use = "complete.obs")), 3),
             p = NA_real_)
    )
}) |>
  left_join(node_registry, by = c("node" = "col"))

node_cors |>
  filter(outcome == "Composite") |>
  arrange(desc(abs(r))) |>
  select(block, label, r) |>
  rename(Block = block, Node = label, `r (composite)` = r) |>
  reactable(filterable = TRUE, sortable = TRUE, striped = TRUE)
```

---

# 4. Belief network

## 4.1 Correlation matrix

The network is estimated from an association matrix among the nodes. Because most nodes are
**ordinal Likert items** (and a few are binary), we do NOT use raw Pearson correlations — those
assume continuous, normally distributed variables and distort associations among ordinal / binary
items. Instead we use `qgraph::cor_auto()`, which automatically applies **polychoric** correlations
to ordinal pairs, **polyserial** to ordinal–continuous pairs, and **Pearson** to continuous pairs
(the product composites), and returns a positive-definite matrix suitable for GLASSO. This matches
the belief-network standard (Turner-Zwinkels et al., 2022) that Lydic et al. (2025) follow.

```{r cor-matrix}
# ---- Assemble the node data frame ------------------------------------------------
# One column per node, rows = participants. Keep it as a data frame (not a matrix) so
# cor_auto() can detect each variable's measurement level (ordinal vs. continuous).
node_df <- d_nodes |> select(all_of(node_cols))

# ---- Drop zero-variance nodes ----------------------------------------------------
# A constant column has no correlations and breaks both cor_auto() and GLASSO.
node_sds      <- vapply(node_df, sd, numeric(1), na.rm = TRUE)
dropped_nodes <- names(node_sds)[is.na(node_sds) | node_sds == 0]
if (length(dropped_nodes) > 0) {
  cat(sprintf("Dropping %d zero-variance node(s): %s\n",
              length(dropped_nodes), paste(dropped_nodes, collapse = ", ")))
}
node_cols_net <- setdiff(node_cols, dropped_nodes)   # nodes that enter the network
node_df       <- node_df[, node_cols_net, drop = FALSE]

# ---- Association matrix ----------------------------------------------------------
# cor_auto(): polychoric / polyserial / Pearson as appropriate; forcePD guarantees a
# positive-definite matrix (required by GLASSO). Falls back to Spearman only if
# cor_auto() errors, so the document still renders and prints a message if it happens.
cor_mat <- tryCatch(
  qgraph::cor_auto(node_df, forcePD = TRUE, verbose = FALSE),
  error = function(e) {
    message("cor_auto() failed (", conditionMessage(e),
            "); falling back to Spearman correlations.")
    cor(as.matrix(node_df), method = "spearman", use = "pairwise.complete.obs")
  }
)

# ---- Display labels (wrapped) keyed by node id -----------------------------------
node_labels    <- node_registry$label |>
  stringr::str_wrap(width = 18) |>
  setNames(node_registry$col)
labels_ordered <- node_labels[node_cols_net]   # same order as cor_mat rows/cols
```

## 4.2 Network estimator

EBIC-GLASSO Gaussian Graphical Model (partial-correlation network), following Lydic et al. (2025):
graphical-LASSO regularization (Friedman et al., 2008) with EBIC model selection
(`qgraph::EBICglasso`, tuning `gamma = 0.5`, the standard default). Regularization shrinks small
partial correlations to exactly zero, yielding a sparse, interpretable network. GLASSO is stable at
roughly N/p ≥ 5–10 observations per node. With `r length(node_cols_net)` nodes and
N = `r nrow(node_df)`, N/p = `r round(nrow(node_df) / length(node_cols_net), 1)` — at the lower end
of the acceptable range, so edges should be read as exploratory (consistent with the "post-hoc"
framing in the reference paper).

```{r cor-network, fig.width=12, fig.height=12}
n_obs <- nrow(node_df)
p     <- ncol(cor_mat)

# ---- Estimate the regularized partial-correlation weights ONCE -------------------
# EBICglasso() returns a p x p weights matrix of regularized partial correlations
# (zeros = no edge). n = sample size for the EBIC penalty. cor_auto() used pairwise
# deletion, so n_obs is an upper bound on the effective N (documented, not a bug).
glasso_mat <- tryCatch(
  qgraph::EBICglasso(cor_mat, n = n_obs, gamma = 0.5, returnAllResults = FALSE),
  error = function(e) { cat(sprintf("GLASSO failed: %s\n", conditionMessage(e))); NULL }
)

# Ensure the weights matrix is keyed by node id so every downstream step can join on it.
if (!is.null(glasso_mat)) dimnames(glasso_mat) <- list(node_cols_net, node_cols_net)

n_edges    <- if (!is.null(glasso_mat)) sum(glasso_mat[upper.tri(glasso_mat)] != 0) else 0
network_ok <- !is.null(glasso_mat) && n_edges > 0
cat(sprintf("GLASSO edges retained: %d (of %d possible)\n", n_edges, p * (p - 1) / 2))

# ---- Plot the estimated weights matrix directly (input = weights, not raw data) --
if (network_ok) {
  qgraph(
    glasso_mat,
    layout      = "spring",   # force-directed: strongly connected nodes are pulled together
    repulsion   = 1.5,
    negCol      = "#2D93AD",  # negative partial correlations
    posCol      = "#c44535",  # positive partial correlations
    edge.labels = FALSE,
    labels      = labels_ordered,
    label.scale = FALSE,
    label.cex   = 0.5,
    shape       = "ellipse",
    vsize       = 5,
    vsize2      = 3,
    legend      = FALSE,
    title       = sprintf("Belief Network (EBIC-GLASSO, N = %d)", n_obs)
  )
} else {
  cat(sprintf(
    "GLASSO produced an empty network at N = %d, p = %d (N/p = %.1f). Downstream network sections are skipped.\n",
    n_obs, p, n_obs / p
  ))
}
```

---

# 5. Community detection

Walktrap community detection on the absolute edge weights (Pons & Latapy, 2005), as in Lydic et al.
(2025). Walktrap finds densely connected clusters via short random walks; absolute weights are used
because community structure concerns connection *strength*, not sign.

```{r communities}
if (network_ok) {
  # Build an undirected weighted igraph directly from the GLASSO weights.
  # Vertex names come from dimnames(glasso_mat) = node ids, so EVERYTHING downstream
  # is keyed by node id — no fragile matching on wrapped display labels (a prior bug).
  g <- igraph::graph_from_adjacency_matrix(
    abs(glasso_mat), mode = "undirected", weighted = TRUE, diag = FALSE
  )

  wtc  <- igraph::cluster_walktrap(g)   # random-walk clustering; uses E(g)$weight (absolute)
  memb <- igraph::membership(wtc)       # named integer vector: names = node ids

  cat(sprintf("Communities detected: %d\n", length(igraph::communities(wtc))))
  cat(sprintf("Modularity: %.3f\n", igraph::modularity(wtc)))

  # Node id -> community, joined to the registry for labels/blocks.
  community_df <- tibble(col = names(memb), community_id = as.integer(memb)) |>
    left_join(node_registry, by = "col") |>
    arrange(community_id, block, label)

  # For qgraph plotting: a named list of node *indices* (into node_cols_net) per community.
  # glasso_mat columns are in node_cols_net order, so these indices line up with the plot.
  communities <- split(match(names(memb), node_cols_net), as.integer(memb))
  names(communities) <- paste("Community", sort(unique(as.integer(memb))))
} else {
  cat("Community detection skipped (empty GLASSO network).\n")
  community_df <- tibble(col = character(), community_id = integer(),
                         label = character(), block = character())
  communities <- list()
}
```

## 5.1 Community membership

```{r community-membership}
if (network_ok) {
  community_df |>
    select(community_id, block, label) |>
    rename(`Community` = community_id, Block = block, Node = label) |>
    reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, groupBy = "Community")
} else {
  cat("Community membership table skipped (empty GLASSO network).\n")
}
```

## 5.2 Network plot with communities

```{r network-communities, fig.width=12, fig.height=12}
if (network_ok) {
  n_communities       <- length(communities)
  palette_communities <- RColorBrewer::brewer.pal(max(n_communities, 3), "Set2")[seq_len(n_communities)]

  qgraph(
    glasso_mat,
    layout      = "spring",
    repulsion   = 1.5,
    negCol      = "#2D93AD",
    posCol      = "#c44535",
    edge.labels = FALSE,
    groups      = communities,
    colors      = palette_communities,
    labels      = labels_ordered,
    label.scale = FALSE,
    label.cex   = 0.5,
    shape       = "ellipse",
    vsize       = 5,
    vsize2      = 3,
    legend      = TRUE,
    title       = sprintf("Belief Network by Community (GLASSO, N = %d)", n_obs)
  )
} else {
  cat("Community network plot skipped (empty GLASSO network).\n")
}
```

---

# 6. Centrality

Eigenvector centrality: reflects both the number of connections and how influential
those connections are. Predicts actual causal influence of nodes reasonably well
(Dablander & Hinne, 2019).

```{r centrality}
if (network_ok) {
  # Eigenvector centrality on the absolute-weight graph. eigen_centrality() returns a
  # vector NAMED by vertex id, so we key on names() rather than assuming the vector is
  # in node_cols_net order (the prior positional assignment could mis-map centrality).
  ec <- igraph::eigen_centrality(g, weights = igraph::E(g)$weight)$vector

  centrality_df <- tibble(
    col             = names(ec),
    eigenvector     = ec,
    eigenvector_abs = abs(ec)
  ) |>
    left_join(node_registry, by = "col") |>
    left_join(community_df |> select(col, community_id), by = "col") |>
    arrange(desc(eigenvector_abs))

  centrality_df |>
    select(community_id, block, label, eigenvector_abs) |>
    rename(Community = community_id, Block = block, Node = label, Centrality = eigenvector_abs) |>
    mutate(Centrality = round(Centrality, 3)) |>
    reactable(filterable = TRUE, sortable = TRUE, striped = TRUE)
} else {
  centrality_df <- node_registry |>
    mutate(eigenvector = NA_real_, eigenvector_abs = NA_real_, community_id = NA_integer_)
  cat("Centrality skipped (empty GLASSO network).\n")
}
```

## 6.1 Centrality plot

```{r centrality-plot, fig.width=7, fig.height=10}
if (network_ok) {
  print(
    centrality_df |>
      mutate(
        label_wrap   = stringr::str_wrap(label, 35),
        community_id = factor(community_id)
      ) |>
      ggplot(aes(reorder(label_wrap, eigenvector_abs), eigenvector_abs, fill = community_id)) +
      geom_col() +
      coord_flip() +
      scale_fill_brewer(palette = "Set2", name = "Community") +
      labs(x = "", y = "Eigenvector centrality") +
      theme_minimal() +
      theme(axis.text.y = element_text(size = 8), legend.position = "top")
  )
} else {
  cat("Centrality plot skipped (empty GLASSO network).\n")
}
```

## 6.2 Centrality × correlation with composite

Replicates Figure 1C from Lydic et al. (2025): tests whether more central nodes
are also more strongly correlated with the behavioral outcome.

```{r centrality-vs-r, fig.width=7, fig.height=6}
if (network_ok) {
  # Match Lydic et al.: correlate node centrality with the strength of each node's
  # association with the outcome. Per the paper, the belief-intention correlations are
  # Fisher z-transformed (atanh) and the absolute value taken (centrality ignores sign).
  cent_cor <- centrality_df |>
    left_join(node_cors |> filter(outcome == "Composite") |> select(node, r),
              by = c("col" = "node")) |>
    mutate(
      r_clip = pmax(pmin(r, 0.999), -0.999),   # guard atanh() against +/-1
      z_abs  = abs(atanh(r_clip))
    )

  ct <- cor.test(cent_cor$eigenvector_abs, cent_cor$z_abs, method = "pearson")
  cat(sprintf("r(centrality, |Fisher z of Spearman r with composite|) = %.2f, p = %.3f\n",
              ct$estimate, ct$p.value))

  print(
    ggplot(cent_cor, aes(eigenvector_abs, z_abs)) +
      geom_point(aes(color = factor(community_id)), size = 3) +
      geom_smooth(method = "lm", color = "grey40", se = TRUE) +
      geom_label_repel(aes(label = stringr::str_wrap(label, 20)),
                       size = 2.5, alpha = 0.8,
                       box.padding = 0.4, point.padding = 0.2,
                       segment.color = "grey60", max.overlaps = 20) +
      scale_color_brewer(palette = "Set2", name = "Community") +
      labs(x = "Eigenvector centrality",
           y = "|Fisher z of Spearman r with intent composite|",
           title = "Centrality vs. association with intent (Lydic et al., Fig 1C)") +
      theme_minimal() +
      theme(legend.position = "top")
  )
} else {
  cat("Centrality vs. r plot skipped (empty GLASSO network).\n")
}
```

---

# 7. Percentage to gain (per node × per intent outcome)

**Hornik & Woolf (1999) method, as used by Lydic et al. (2025).** For each belief × intent item:

- **Outcome ("intender")** = top box of the 7-point intent scale ("Definitely will").
- **"Strong" belief** = the *extreme scale point in the pro-intention direction*. For each Likert /
  binary item we take the endpoint (the max value if the belief correlates positively with intent,
  the min value if it correlates negatively — this reproduces the H&W "strongly (dis)agree"
  reorientation). The four **continuous composites** have no natural scale endpoint, so for those
  (only) we substitute the top/bottom quartile. The rule actually used is reported per row in the
  `rule` column.
- **Percentage to gain** = P(intender | strong belief) − P(intender overall), in points — exactly
  the Table 2 definition in the reference paper (a − b).

N = `r nrow(d_nodes)`. A node × outcome cell returns NA when there is no "strong" group or no
"other" group (no contrast can be formed).

```{r ptg-function}
INTENT_TOP <- 7L   # top box of the 7-point intent scale = "Definitely will"

# Continuous composites have no natural "strongly agree" endpoint, so PTG uses the
# top/bottom quartile for these; every other node uses the scale endpoint (H&W rule).
continuous_nodes <- c("research_3_nat_mean", "research_5_composite",
                      "research_6_composite", "climate_4_mean")

compute_ptg <- function(node_name, x_num, y_num) {
  # Direction: the sign of the belief-outcome association orients "strong" toward the
  # pro-intention pole (positive r -> high values are pro; negative r -> low values are pro).
  r_xy <- suppressWarnings(cor(x_num, y_num, method = "spearman", use = "complete.obs"))
  if (is.na(r_xy) || r_xy == 0) return(NULL)
  direction <- if (r_xy > 0) "positive" else "negative"

  # ---- Define "strong belief in the pro-intention direction" ---------------------
  if (node_name %in% continuous_nodes) {
    thr_hi <- quantile(x_num, 0.75, na.rm = TRUE)
    thr_lo <- quantile(x_num, 0.25, na.rm = TRUE)
    strong <- if (r_xy > 0) x_num >= thr_hi else x_num <= thr_lo
    rule   <- "quartile"
  } else {
    hi <- max(x_num, na.rm = TRUE); lo <- min(x_num, na.rm = TRUE)  # observed scale endpoints
    strong <- if (r_xy > 0) x_num == hi else x_num == lo
    rule   <- "endpoint"
  }

  pred_01 <- ifelse(is.na(x_num), NA_integer_, as.integer(strong))          # 1 = strong belief
  out_01  <- ifelse(is.na(y_num), NA_integer_, as.integer(y_num == INTENT_TOP))  # 1 = intender

  ok <- !is.na(pred_01) & !is.na(out_01)
  p  <- pred_01[ok]; o <- out_01[ok]
  n_total <- length(p); n_strong <- sum(p == 1L); n_other <- sum(p == 0L)
  rate_overall <- mean(o)   # 'b' in Table 2: overall intender rate

  # Need both a "strong" and an "other" group to form the contrast.
  if (n_strong == 0 || n_other == 0) {
    return(tibble(direction, rule,
                  pct_strong   = round(n_strong / n_total * 100, 1),
                  rate_strong  = NA_real_, rate_other = NA_real_,
                  rate_overall = round(rate_overall * 100, 1),
                  pct_to_gain  = NA_real_, ror = NA_real_))
  }

  rate_s <- mean(o[p == 1L])   # 'a' in Table 2: P(intender | strong belief)
  rate_o <- mean(o[p == 0L])   # P(intender | weak belief)
  ptg    <- (rate_s - rate_overall) * 100          # H&W: a - b
  ror    <- if (rate_o %in% c(0, 1) || rate_s %in% c(0, 1)) NA_real_ else
              (rate_s / (1 - rate_s)) / (rate_o / (1 - rate_o))   # relative odds ratio

  tibble(direction, rule,
         pct_strong   = round(n_strong / n_total * 100, 1),
         rate_strong  = round(rate_s * 100, 1),
         rate_other   = round(rate_o * 100, 1),
         rate_overall = round(rate_overall * 100, 1),
         pct_to_gain  = round(ptg, 1),
         ror          = round(ror, 2))
}
```

```{r ptg-compute}
ptg_results <- map_dfr(node_cols, function(nc) {
  x <- d_nodes[[nc]]
  map_dfr(seq_along(intent_cols), function(i) {
    y  <- d_nodes[[intent_cols[i]]]
    pt <- compute_ptg(nc, x, y)          # pass node id so the fn can pick endpoint vs. quartile
    if (is.null(pt)) return(NULL)
    bind_cols(tibble(node = nc, outcome = intent_labels[i]), pt)
  })
}) |>
  left_join(node_registry, by = c("node" = "col"))
```

---

# 8. Centrality × PTG: combined analysis

One plot per intent outcome. Upper-right quadrant = above-average on both centrality
and PTG → highest-priority targets. Follows Figure 1C approach from Lydic et al. (2025).

```{r combined-data}
if (network_ok) {
  combined <- centrality_df |>
    select(col, label, block, community_id, eigenvector_abs) |>
    left_join(
      ptg_results |> select(node, outcome, pct_to_gain),
      by = c("col" = "node")
    ) |>
    left_join(
      node_cors |>
        filter(outcome != "Composite") |>
        select(node, outcome, r_spearman = r),
      by = c("col" = "node", "outcome")
    )
} else {
  combined <- NULL
}
```

```{r centrality-ptg-plots, fig.width=8, fig.height=7, results='asis'}
if (is.null(combined)) {
  cat("Centrality × PTG plots skipped (empty GLASSO network).\n")
} else walk(intent_labels, function(ol) {
  cat(sprintf("\n\n## 8.%d %s\n\n", which(intent_labels == ol), ol))

  plot_data <- combined |>
    filter(outcome == ol) |>
    filter(!is.na(pct_to_gain), !is.na(eigenvector_abs))

  if (nrow(plot_data) == 0) {
    cat("No data for this outcome (all PTG values NA — no data).\n")
    return(invisible(NULL))
  }

  mean_cent <- mean(plot_data$eigenvector_abs, na.rm = TRUE)
  mean_ptg  <- mean(plot_data$pct_to_gain,     na.rm = TRUE)

  p <- ggplot(plot_data, aes(eigenvector_abs, pct_to_gain)) +
    geom_hline(yintercept = mean_ptg,  linetype = "dashed", color = "grey60") +
    geom_vline(xintercept = mean_cent, linetype = "dashed", color = "grey60") +
    annotate("rect",
             xmin = mean_cent, xmax = Inf,
             ymin = mean_ptg,  ymax = Inf,
             alpha = 0.06, fill = "#2D93AD") +
    geom_point(aes(color = factor(community_id)), size = 3) +
    geom_label_repel(
      aes(label = stringr::str_wrap(label, 22)),
      size = 2.5, alpha = 0.85,
      box.padding = 0.4, point.padding = 0.2,
      segment.color = "grey60", max.overlaps = 30
    ) +
    scale_color_brewer(palette = "Set2", name = "Community") +
    labs(
      x     = "Eigenvector centrality",
      y     = "% to gain",
      title = sprintf("Centrality × PTG: %s", ol),
      subtitle = "Shaded = above-average on both (priority targets) | Dashed lines = means"
    ) +
    theme_minimal() +
    theme(legend.position = "top")

  print(p)
  cat("\n")

  # Print top nodes in upper-right quadrant
  top_nodes <- plot_data |>
    filter(eigenvector_abs > mean_cent, pct_to_gain > mean_ptg) |>
    arrange(desc(eigenvector_abs + pct_to_gain / max(pct_to_gain, na.rm = TRUE))) |>
    select(block, label, eigenvector_abs, pct_to_gain) |>
    mutate(across(where(is.numeric), \(x) round(x, 2)))

  if (nrow(top_nodes) > 0) {
    cat(sprintf("**%d nodes above average on both metrics:**\n\n", nrow(top_nodes)))
    print(reactable(top_nodes,
                    columns = list(
                      block          = colDef(name = "Block"),
                      label          = colDef(name = "Node"),
                      eigenvector_abs = colDef(name = "Centrality"),
                      pct_to_gain    = colDef(name = "% to gain")
                    ),
                    striped = TRUE))
  } else {
    cat("No nodes above average on both metrics .\n")
  }
}) # end walk / end else
```

---

# 9. Summary table

Full metrics for all nodes × all outcomes.

```{r summary-table}
if (network_ok) {
  summary_out <- centrality_df |>
    select(col, label, block, community_id, eigenvector_abs) |>
    left_join(
      node_cors |>
        filter(outcome != "Composite") |>
        select(node, outcome, r_spearman = r, p_spearman = p),
      by = c("col" = "node")
    ) |>
    left_join(
      ptg_results |> select(node, outcome, pct_to_gain, ror, direction),
      by = c("col" = "node", "outcome")
    )

  summary_out |>
    mutate(across(where(is.numeric), \(x) round(x, 3))) |>
    select(outcome, block, label, community_id, eigenvector_abs,
           r_spearman, pct_to_gain, ror) |>
    rename(
      Outcome    = outcome,
      Block      = block,
      Node       = label,
      Community  = community_id,
      Centrality = eigenvector_abs,
      `r (Spearman)` = r_spearman,
      `% to gain`    = pct_to_gain,
      ROR        = ror
    ) |>
    reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, groupBy = "Outcome")
} else {
  # Show PTG + correlations only (no centrality/community — empty network)
  node_cors |>
    filter(outcome != "Composite") |>
    left_join(
      ptg_results |> select(node, outcome, pct_to_gain, ror, direction),
      by = c("node", "outcome")
    ) |>
    mutate(across(where(is.numeric), \(x) round(x, 3))) |>
    select(outcome, block, label, r, p, pct_to_gain, ror) |>
    rename(
      Outcome = outcome, Block = block, Node = label,
      `r (Spearman)` = r, `p` = p,
      `% to gain` = pct_to_gain, ROR = ror
    ) |>
    reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, groupBy = "Outcome")
}
```

---

# 10. Export

```{r export}
dir.create(file.path(path, "Output"), showWarnings = FALSE)

out_path <- file.path(path, "Output", "05_belief_network.csv")

ptg_wide <- ptg_results |>
  select(node, outcome, pct_to_gain, ror) |>
  pivot_wider(names_from = outcome,
              values_from = c(pct_to_gain, ror),
              names_glue = "{.value}_{outcome}")

cors_composite <- node_cors |>
  filter(outcome == "Composite") |>
  select(node, r_composite = r)

if (network_ok) {
  export_df <- centrality_df |>
    select(col, label, block, community_id, eigenvector_abs) |>
    left_join(cors_composite, by = c("col" = "node")) |>
    left_join(ptg_wide,       by = c("col" = "node"))
} else {
  export_df <- node_registry |>
    select(col, label, block) |>
    mutate(community_id = NA_integer_, eigenvector_abs = NA_real_) |>
    left_join(cors_composite, by = c("col" = "node")) |>
    left_join(ptg_wide,       by = c("col" = "node"))
}

write_csv(export_df, out_path)
cat(sprintf("Saved: %s\n", out_path))
cat(sprintf("Rows: %d | Columns: %d\n", nrow(export_df), ncol(export_df)))
```
