---
title: "Step 1: Belief Item Distributions"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 9, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse)
```

```{r load-data}
path <- "~/Documents/GitHub/UniversityNews"
data <- readRDS(sprintf("%s/Data/Cleaned/UnivNews_Step1_combined.rds", path))
```

```{r aesthetics}
plot_aes <- theme_minimal() +
  theme(
    legend.position    = "bottom",
    legend.text        = element_text(size = 9),
    text               = element_text(size = 12),
    axis.text          = element_text(color = "black"),
    axis.ticks.y       = element_blank(),
    panel.grid.major.y = element_blank()
  )

palette_main <- "#197278"
```

Full library of response scales used across the Step 1 instrument (copied from `02_descriptives_step1_pilot.Rmd` — keep in sync if that file's scale levels ever change).

```{r scale-levels}
# ── Amount / knowledge (None at all → A great deal) ─────────────────────────
lvl_know    <- c("None at all", "A little", "A moderate amount", "A lot", "A great deal")
lvl_know_ns <- c(lvl_know, "Not sure")

# ── Agree / disagree (5-point, Somewhat variant) ────────────────────────────
lvl_agree5 <- c("Strongly disagree", "Somewhat disagree", "Neither agree nor disagree",
                "Somewhat agree", "Strongly agree")

# ── Positive / negative effect ───────────────────────────────────────────────
lvl_pos_neg <- c("Extremely negative", "Somewhat negative", "Neither positive nor negative",
                 "Somewhat positive", "Extremely positive")

# ── Importance ───────────────────────────────────────────────────────────────
lvl_importance <- c("Not at all important", "Slightly important", "Moderately important",
                    "Very important", "Extremely important")

# ── Likelihood: research_5#2 and research_6#2 (Very unlikely → Very likely) ─
lvl_likelihood_res <- c("Very unlikely", "Somewhat unlikely", "Neutral",
                        "Somewhat likely", "Very likely")

# ── Likelihood: govtfund_5 (Extremely unlikely → Extremely likely) ───────────
lvl_likelihood_gov <- c("Extremely unlikely", "Somewhat unlikely", "Neither likely nor unlikely",
                        "Somewhat likely", "Extremely likely")

# ── Problematic ──────────────────────────────────────────────────────────────
lvl_problematic <- c("Not at all problematic", "Slightly problematic", "Moderately problematic",
                     "Very problematic", "Extremely problematic")

# ── Approve / disapprove (4-point, no midpoint) ─────────────────────────────
lvl_approve4 <- c("Strongly disapprove", "Somewhat disapprove",
                  "Somewhat approve", "Strongly approve")

# ── Approve / disapprove (5-point, "Neither approve nor disapprove") ─────────
# Used for govtfund_4, govtfund_9
lvl_approve5 <- c("Strongly disapprove", "Somewhat disapprove",
                  "Neither approve nor disapprove",
                  "Somewhat approve", "Strongly approve")

# ── Approve / disapprove (5-point, "Neutral / neither…" wording) ─────────────
# Used for highered_1
lvl_approve5_he <- c("Strongly disapprove", "Somewhat disapprove",
                     "Neutral / neither approve nor disapprove",
                     "Somewhat approve", "Strongly approve")

# ── Priority ─────────────────────────────────────────────────────────────────
lvl_priority <- c("Not a priority", "Low priority", "Somewhat priority",
                  "Moderate priority", "High priority")

# ── Frequency (past engagement) ──────────────────────────────────────────────
lvl_freq <- c("Never", "Once or twice a year", "Once or twice a month",
              "Once or twice a week", "Almost every day", "Once or more per day")

# ── Behavioral intention (7-point, includes "Unsure") ────────────────────────
lvl_intent <- c("Definitely will not", "Probably will not", "Maybe will not",
                "Unsure", "Maybe will", "Probably will", "Definitely will")

# ── Local impact of cuts ─────────────────────────────────────────────────────
lvl_impact <- c("Strong negative impact", "Somewhat negative impact",
                "Neither positive nor negative impact",
                "Somewhat positive impact", "Strong positive impact")

# ── Climate scientist trust ──────────────────────────────────────────────────
lvl_climate_trust <- c("Not at all", "Slightly", "Moderately", "Very strongly")

# ── Proportion nonprofit ─────────────────────────────────────────────────────
lvl_proportion <- c("None", "Less than half", "About half", "Most", "All", "Not sure")
```

## Function

```{r plot-fn}
# Bar chart of one item's raw response distribution, with N and % labels.
# col      - column name in `data` (string; back-tick if it contains a period, e.g. "research_6.2_1")
# question - exact question/item text to use as the plot title
# levels   - the ordered response scale (one of the lvl_* vectors above)
# out_file - filename (no path) to save under Output/; skip saving with out_file = NULL
plot_item_distribution <- function(data, col, question, levels, out_file = NULL) {
  df <- data %>%
    filter(!is.na(.data[[col]]), .data[[col]] != "") %>%
    count(response = .data[[col]]) %>%
    mutate(response = factor(response, levels = levels),
           pct = n / sum(n) * 100)

  p <- ggplot(df, aes(x = response, y = n)) +
    geom_col(fill = palette_main) +
    geom_text(aes(label = paste0(n, " (", round(pct, 1), "%)")), hjust = -0.1, size = 3.8) +
    coord_flip() +
    expand_limits(y = max(df$n) * 1.2) +
    labs(x = "", y = "Count", title = str_wrap(question, width = 68)) +
    plot_aes +
    theme(plot.title = element_text(size = 11))

  if (!is.null(out_file)) {
    ggsave(sprintf("%s/Output/%s", path, out_file), p, width = 9, height = 5, dpi = 200)
  }
  p
}
```

Before plotting a new item, check `Output/03_correlations_intent.csv` (r_composite, p_composite) and `Output/04_promising_beliefs.csv` (`pct_at_strongest`, `small_n_flag`, `ceiling_flag`) for that variable — the `small_n_flag` in particular means fewer than 30 people sit at the "strongest" position, so any PTG number for that item is unreliable even though the raw distribution below is still accurate.

## Examples

### Approval of federal funding for university research (`govtfund_1`)

r_composite = .358, p < .001. 55.9% already at "Strongly approve" — a strong correlate that's ceiling-limited.

```{r govtfund_1}
plot_item_distribution(
  data, "govtfund_1",
  "Do you approve or disapprove of the federal government using taxpayer funds to invest in scientific research at colleges and universities?",
  lvl_approve4,
  "govtfund1_distribution.png"
)
```

### Research advancing knowledge is necessary even without immediate benefits (`research_4_8`)

r_composite = .137, p = .018. 58.3% at "Strongly agree" — correlated but weaker, also ceiling-limited.

```{r research_4_8}
plot_item_distribution(
  data, "research_4_8",
  "Research advancing knowledge is necessary, even w/o immediate benefits",
  lvl_agree5,
  "research4_8_distribution.png"
)
```

### University researchers are motivated primarily by profit (`gotvfund_6_5`)

r_composite = -.027, p = .64 (n.s.). 20.3% at "Strongly disagree" (the outcome-aligned pole). Not correlated, moderate prevalence.

```{r gotvfund_6_5}
plot_item_distribution(
  data, "gotvfund_6_5",
  "University researchers are motivated primarily by profit",
  lvl_agree5,
  "gotvfund6_5_distribution.png"
)
```

### Researchers make mistakes and results are incorrect — likelihood (`research_6.2_1`)

r_composite = -.108, p = .061 (borderline n.s.). Only 5.3% at "Very unlikely" (n=16) — **small_n_flag = TRUE**, so treat any PTG figure for this item as unreliable.

```{r research_6.2_1}
plot_item_distribution(
  data, "research_6.2_1",
  "How likely is academic research to produce this outcome: Researchers make mistakes and results are incorrect",
  lvl_likelihood_res,
  "research6_2_1_distribution.png"
)
```

### I think about the impact of science on my daily life (`research_4_4`)

r_composite = .46, p < .001 — the strongest correlate in the survey. Only 19.3% at "Strongly agree" (n=58). Correlated + headroom: a genuine high-value target.

```{r research_4_4}
plot_item_distribution(
  data, "research_4_4",
  "I often think about the impact of science on my everyday life",
  lvl_agree5,
  "research4_4_distribution.png"
)
```

### Priority: Making a profit (`govtfund_7_1`)

r_composite = -.026, p = .656 (n.s.). Nearly uniform spread across all 5 priority levels (12.7% / 24.0% / 23.3% / 15.0% / 25.0%) — genuine disagreement in the sample, but it doesn't track intent to talk/share/contact reps.

```{r govtfund_7_1}
plot_item_distribution(
  data, "govtfund_7_1",
  "What are the priorities of government-funded research at colleges and universities? Making a profit",
  lvl_priority,
  "govtfund7_1_distribution.png"
)
```

## Adding a new item

1. Find the variable name and exact question wording in `UnivNews_Step1_Survey_Reference.md` (or the labels vectors in `02_descriptives_step1_pilot.Rmd`).
2. Confirm which `lvl_*` scale it uses (check the matching `bar_matrix`/`bar_single` call in `02_descriptives_step1_pilot.Rmd`).
3. Optionally pull `r_composite`/`pct_at_strongest`/flags from `Output/03_correlations_intent.csv` and `Output/04_promising_beliefs.csv`.
4. Copy one of the chunks above and swap in the new `col`, `question`, `levels`, and `out_file`.
