---
title: "Step 1: Self-Relevance of Research — Item Structure & Correlations with Key Outcomes"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 8, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, reactable, plotly, psych)
```

```{r load-data}
path <- "~/Documents/GitHub/UniversityNews"

dir.create(file.path(path, "Output"), showWarnings = FALSE)

data <- readRDS(sprintf("%s/Data/Cleaned/UnivNews_Step1_combined.rds", path))

N <- nrow(data)
```

```{r scale-levels}
lvl_know       <- c("None at all","A little","A moderate amount","A lot","A great deal")
lvl_agree5     <- c("Strongly disagree","Somewhat disagree","Neither agree nor disagree",
                    "Somewhat agree","Strongly agree")
lvl_pos_neg    <- c("Extremely negative","Somewhat negative","Neither positive nor negative",
                    "Somewhat positive","Extremely positive")
lvl_importance <- c("Not at all important","Slightly important","Moderately important",
                    "Very important","Extremely important")
lvl_impact     <- c("Strong negative impact","Somewhat negative impact",
                    "Neither positive nor negative impact",
                    "Somewhat positive impact","Strong positive impact")
lvl_approve4   <- c("Strongly disapprove","Somewhat disapprove","Somewhat approve","Strongly approve")
lvl_intent     <- c("Definitely will not","Probably will not","Maybe will not",
                    "Unsure","Maybe will","Probably will","Definitely will")

to_num <- function(x, levels) as.integer(factor(x, levels = levels, ordered = TRUE))
```

```{r recode}
intent_cols <- paste0("X", 1:4, "_intent")

d <- data |>
  mutate(
    # --- Self-relevance items ---
    research_3_1    = to_num(research_3_1,    lvl_pos_neg),
    research_3_2    = to_num(research_3_2,    lvl_pos_neg),
    univ_5_1        = to_num(univ_5_1,        lvl_know),
    univ_5_2        = to_num(univ_5_2,        lvl_know),
    govtfund_8_7    = to_num(govtfund_8_7,    lvl_agree5),
    research_4_3    = to_num(research_4_3,    lvl_agree5),
    research_4_4    = to_num(research_4_4,    lvl_agree5),
    gotvfund_6_3    = to_num(gotvfund_6_3,    lvl_agree5),
    gotvfund_6_4    = to_num(gotvfund_6_4,    lvl_agree5),
    research_5.1_12 = to_num(research_5.1_12, lvl_importance),
    govfund_10      = to_num(govfund_10,      lvl_impact),
    # govfund_10 is reverse-keyed: high = local area helped BY CUTS = low research self-relevance.
    # Reverse so that high = research matters locally, consistent with the other items.
    govfund_10r     = 6 - govfund_10,

    # --- Key outcomes ---
    govtfund_1 = to_num(govtfund_1, lvl_approve4),            # 1 disapprove -> 4 approve
    govtfund_2 = case_when(                                   # 1 = govt investment essential
      grepl("ESSENTIAL", govtfund_2) ~ 1L,
      govtfund_2 == ""               ~ NA_integer_,
      TRUE                           ~ 0L
    ),
    across(all_of(intent_cols), \(x) to_num(x, lvl_intent))  # 1 -> 7
  )

# Behavioral-intention composite (mean of the 4 intent items)
d$intent_composite <- rowMeans(d[, intent_cols], na.rm = TRUE)
```

```{r selfrel-registry}
# Self-relevance items grouped by conceptual facet.
selfrel_registry <- tribble(
  ~col,              ~label,                                              ~facet,
  "research_3_1",    "Research effect on you personally",                 "Personal / close-other benefit",
  "research_3_2",    "Research effect on people you care about",          "Personal / close-other benefit",
  "univ_5_1",        "You personally benefit from universities",          "Personal / close-other benefit",
  "univ_5_2",        "People you care about benefit",                     "Personal / close-other benefit",
  "govtfund_8_7",    "Tax investment benefits people like you",           "Tangible / everyday relevance",
  "gotvfund_6_3",    "Everyday tools result from academic research",      "Tangible / everyday relevance",
  "gotvfund_6_4",    "Research benefits everyone's day-to-day lives",     "Tangible / everyday relevance",
  "research_4_3",    "Clear how to apply research in my own life",        "Personal applicability / salience",
  "research_4_4",    "I often think about research's impact on my life",  "Personal applicability / salience",
  "research_5.1_12", "Importance: understanding to improve own life",     "Adjunct (weak / distinct)",
  "govfund_10r",     "Local area harmed by funding cuts (reverse-keyed)", "Adjunct (weak / distinct)"
)

selfrel_items <- selfrel_registry$col
lab <- setNames(selfrel_registry$label, selfrel_registry$col)
```

# Overview

This document (1) examines whether the survey's self-relevance items form a coherent
construct, and (2) correlates each item — and derived composites — against the study's
key attitudinal and behavioral outcomes.

**Self-relevance** is operationalized as the `r nrow(selfrel_registry)` items whose wording
ties academic research to the respondent *personally*, to *people they care about*, to their
*everyday life*, or to their *local area*. All items are recoded so that **higher = research is
more self-relevant / beneficial to me**. `govfund_10` is reverse-keyed (`govfund_10r`) because
its raw scale runs the opposite direction (high = local area *helped by cuts*).

**N = `r N`** (Cohorts 1–3 combined). All correlations are Spearman; p-values are exploratory only.

---

# Item structure {.tabset}

## Descriptives

```{r item-descriptives}
selfrel_registry |>
  mutate(
    n    = map_int(col, \(v) sum(!is.na(d[[v]]))),
    Mean = map_dbl(col, \(v) round(mean(d[[v]], na.rm = TRUE), 2)),
    SD   = map_dbl(col, \(v) round(sd(d[[v]],   na.rm = TRUE), 2))
  ) |>
  select(Item = label, Facet = facet, Variable = col, n, Mean, SD) |>
  reactable(striped = TRUE, compact = TRUE, pagination = FALSE,
            columns = list(
              Item     = colDef(minWidth = 230, style = list(fontWeight = "bold")),
              Facet    = colDef(minWidth = 190),
              Variable = colDef(width = 130),
              n        = colDef(width = 60,  align = "center"),
              Mean     = colDef(width = 70,  align = "center"),
              SD       = colDef(width = 70,  align = "center")
            ))
```

All items are on 1–5 scales except `govfund_10r` (1–5, reverse-keyed). Every item has complete
data (n = `r N`).

## Correlation matrix

```{r item-cormat}
cmat <- d |>
  select(all_of(selfrel_items)) |>
  cor(method = "spearman", use = "pairwise.complete.obs")

# Save numeric matrix
cmat_out <- round(cmat, 3) |> as.data.frame() |> tibble::rownames_to_column("variable")
write_csv(cmat_out, file.path(path, "Output", "10_selfrelevance_item_cormat.csv"))

heat <- function(v) {
  colDef(width = 62, align = "center",
         style = function(value) {
           if (is.na(value)) return(list())
           a <- abs(value)
           bg <- if (value >= 0) sprintf("rgba(78,121,167,%.2f)", a)
                 else            sprintf("rgba(225,87,89,%.2f)", a)
           list(background = bg, color = if (a > 0.6) "white" else "black")
         },
         format = colFormat(digits = 2))
}

cmat |>
  round(2) |>
  as.data.frame() |>
  setNames(seq_len(ncol(cmat))) |>
  tibble::rownames_to_column("Item") |>
  mutate(Item = lab[Item], `#` = row_number()) |>
  relocate(`#`, .before = Item) |>
  reactable(
    striped = FALSE, compact = TRUE, pagination = FALSE,
    columns = c(
      list(`#`  = colDef(width = 34, align = "center", style = list(fontWeight = "bold")),
           Item = colDef(minWidth = 250, style = list(fontWeight = "bold"))),
      setNames(lapply(seq_len(ncol(cmat)), \(i) heat(i)), seq_len(ncol(cmat)))
    )
  )
```

Spearman correlations among the self-relevance items. Column numbers match the `#` in the first
column. Blue = positive, red = negative; saturation ∝ |r|. Full matrix saved to
`Output/10_selfrelevance_item_cormat.csv`.

## Strongest pairs

```{r item-pairs}
pairs_tbl <- as.data.frame(as.table(cmat)) |>
  filter(as.character(Var1) < as.character(Var2)) |>
  transmute(`Item A` = lab[as.character(Var1)],
            `Item B` = lab[as.character(Var2)],
            r = round(Freq, 2)) |>
  arrange(desc(abs(r)))

reactable(pairs_tbl, striped = TRUE, compact = TRUE, defaultPageSize = 15,
          columns = list(
            `Item A` = colDef(minWidth = 220),
            `Item B` = colDef(minWidth = 220),
            r        = colDef(width = 70, align = "center")
          ))
```

The set breaks into three sub-clusters rather than one dimension: **personal / close-other
benefit** (self and close others move nearly together), **tangible / everyday relevance**, and
**personal applicability / salience**.

## Reliability

```{r alpha}
core_items  <- selfrel_registry |> filter(facet != "Adjunct (weak / distinct)") |> pull(col)

a_all  <- psych::alpha(d[, selfrel_items], warnings = FALSE, check.keys = FALSE)
a_core <- psych::alpha(d[, core_items],    warnings = FALSE, check.keys = FALSE)

facet_alpha <- selfrel_registry |>
  filter(facet != "Adjunct (weak / distinct)") |>
  group_by(facet) |>
  summarise(items = list(col), .groups = "drop") |>
  mutate(k = map_int(items, length),
         alpha = map_dbl(items, \(v) if (length(v) > 1)
           round(psych::alpha(d[, v], warnings = FALSE)$total$raw_alpha, 2) else NA_real_))

drop_tbl <- tibble(
  Item      = lab[rownames(a_all$alpha.drop)],
  `α if dropped` = round(a_all$alpha.drop[, "raw_alpha"], 3)
) |> arrange(`α if dropped`)
```

```{r alpha-table}
bind_rows(
  tibble(Scale = "All items",  k = length(selfrel_items), `Cronbach α` = round(a_all$total$raw_alpha, 2)),
  tibble(Scale = "Core (9 items, adjuncts dropped)", k = length(core_items),
         `Cronbach α` = round(a_core$total$raw_alpha, 2)),
  facet_alpha |> transmute(Scale = facet, k, `Cronbach α` = alpha)
) |>
  reactable(striped = TRUE, compact = TRUE, pagination = FALSE,
            columns = list(Scale = colDef(minWidth = 240, style = list(fontWeight = "bold")),
                           k = colDef(width = 60, align = "center"),
                           `Cronbach α` = colDef(width = 110, align = "center")))
```

```{r alpha-drop-table}
reactable(drop_tbl, striped = TRUE, compact = TRUE, pagination = FALSE,
          columns = list(Item = colDef(minWidth = 260, style = list(fontWeight = "bold")),
                         `α if dropped` = colDef(width = 120, align = "center")))
```

The full set reaches α = `r round(a_all$total$raw_alpha, 2)`. Dropping the two adjunct items
(`research_5.1_12`, `govfund_10r`) raises reliability to α = `r round(a_core$total$raw_alpha, 2)`,
so the **9-item core** is the cleaner composite.

---

# Composites

```{r composites}
personal_items <- selfrel_registry |> filter(facet == "Personal / close-other benefit") |> pull(col)
everyday_items <- selfrel_registry |> filter(facet == "Tangible / everyday relevance") |> pull(col)
applic_items   <- selfrel_registry |> filter(facet == "Personal applicability / salience") |> pull(col)

d <- d |>
  mutate(
    selfrel_personal  = rowMeans(across(all_of(personal_items)), na.rm = TRUE),
    selfrel_everyday  = rowMeans(across(all_of(everyday_items)), na.rm = TRUE),
    selfrel_applic    = rowMeans(across(all_of(applic_items)),   na.rm = TRUE),
    selfrel_composite = rowMeans(across(all_of(core_items)),     na.rm = TRUE)
  )

composite_registry <- tribble(
  ~col,                 ~label,
  "selfrel_composite",  "Self-relevance composite (9-item core)",
  "selfrel_personal",   "Facet: Personal / close-other benefit",
  "selfrel_everyday",   "Facet: Tangible / everyday relevance",
  "selfrel_applic",     "Facet: Personal applicability / salience"
)
```

Four composites (all means of their constituent items, higher = more self-relevant):

- **`selfrel_composite`** — 9-item core (α = `r round(a_core$total$raw_alpha, 2)`)
- **`selfrel_personal`** — research helps me / people I care about
- **`selfrel_everyday`** — research shows up in everyday life
- **`selfrel_applic`** — I can apply / think about research in my life

---

# Correlations with key outcomes {.tabset}

```{r outcome-registry}
outcome_registry <- tribble(
  ~col,               ~label,                                          ~scale_note,
  "govtfund_1",       "Approve federal funding of univ. research",     "1 disapprove – 4 approve",
  "govtfund_2",       "Govt investment is ESSENTIAL (vs private)",     "0/1",
  "intent_composite", "Behavioral-intention composite",               "1–7 mean",
  "X1_intent",        "Intent: contact reps to oppose cuts",           "1–7",
  "X2_intent",        "Intent: talk to others about cuts",             "1–7",
  "X3_intent",        "Intent: share info online about cuts",          "1–7",
  "X4_intent",        "Intent: contact reps to support funding",       "1–7"
)
outcome_cols <- outcome_registry$col
olab <- setNames(outcome_registry$label, outcome_registry$col)

# Generic: correlate a set of predictor columns against all outcomes
corr_against_outcomes <- function(pred_cols, pred_labels) {
  map_dfr(pred_cols, function(pc) {
    x <- d[[pc]]
    row <- map_dfc(outcome_cols, function(oc) {
      y  <- d[[oc]]
      ct <- suppressWarnings(cor.test(x, y, method = "spearman", exact = FALSE))
      tibble(!!oc := round(ct$estimate, 2), !!paste0("p_", oc) := ct$p.value)
    })
    bind_cols(tibble(Measure = pred_labels[pc]), row)
  })
}

star <- function(p) case_when(p < .001 ~ "***", p < .01 ~ "**", p < .05 ~ "*", TRUE ~ "")

# Reactable column defs for outcome r columns with significance shading
r_coldefs <- function(cols) {
  setNames(lapply(cols, function(oc) {
    colDef(
      minWidth = 92, align = "center",
      cell = function(value, index, name) {
        p <- rt_data[[paste0("p_", oc)]][index]
        s <- star(p)
        htmltools::span(sprintf("%.2f%s", value, s))
      },
      style = function(value) {
        a <- min(abs(value), 1)
        bg <- if (value >= 0) sprintf("rgba(78,121,167,%.2f)", a)
              else            sprintf("rgba(225,87,89,%.2f)", a)
        list(background = bg, color = if (a > 0.5) "white" else "black")
      }
    )
  }), cols)
}
```

Spearman correlations. Cells show *r* with significance stars (`*` p<.05, `**` p<.01, `***` p<.001);
blue = positive, red = negative, saturation ∝ |r|.

## Composites × outcomes

```{r composite-outcomes}
comp_res <- corr_against_outcomes(composite_registry$col, setNames(composite_registry$label, composite_registry$col))
write_csv(comp_res, file.path(path, "Output", "10_selfrelevance_composite_x_outcomes.csv"))

rt_data <- comp_res
reactable(
  comp_res |> select(Measure, all_of(outcome_cols)) |> setNames(c("Measure", olab[outcome_cols])),
  striped = TRUE, compact = TRUE, pagination = FALSE,
  columns = c(list(Measure = colDef(minWidth = 240, style = list(fontWeight = "bold"))),
              setNames(r_coldefs(outcome_cols), olab[outcome_cols]))
)
```

## Items × outcomes

```{r item-outcomes}
item_res <- corr_against_outcomes(selfrel_items, lab)
write_csv(item_res, file.path(path, "Output", "10_selfrelevance_items_x_outcomes.csv"))

rt_data <- item_res
reactable(
  item_res |> select(Measure, all_of(outcome_cols)) |> setNames(c("Measure", olab[outcome_cols])),
  striped = TRUE, compact = TRUE, pagination = FALSE,
  columns = c(list(Measure = colDef(minWidth = 240, style = list(fontWeight = "bold"))),
              setNames(r_coldefs(outcome_cols), olab[outcome_cols]))
)
```

## Composite × approval (plot)

```{r composite-plot, fig.height=4.5}
plot_df <- comp_res |>
  transmute(Measure,
            r  = govtfund_1,
            p  = p_govtfund_1,
            se = sqrt((1 - govtfund_1^2) / (N - 2))) |>
  mutate(
    Measure = fct_reorder(Measure, r),
    sig = star(p),
    tip = sprintf("<b>%s</b><br>r = %.2f ± %.2f SE (p = %.3g)%s", Measure, r, se, p, sig)
  )

p <- ggplot(plot_df, aes(x = r, y = Measure, text = tip)) +
  geom_segment(aes(x = 0, xend = r, yend = Measure), color = "gray82", linewidth = 0.6) +
  geom_errorbarh(aes(xmin = r - se, xmax = r + se), height = 0.25, color = "gray55") +
  geom_point(size = 4, color = "#4E79A7") +
  labs(x = "Spearman r with approval of federal funding (govtfund_1)", y = NULL) +
  theme_minimal(base_size = 12)

ggplotly(p, tooltip = "text")
```

Association between each self-relevance composite and approval of federal research funding.

---

# What explains self-relevance? {.tabset}

Which beliefs elsewhere in the survey track feeling that research is personally relevant?
The natural hypothesis is that it is domain-driven — people who care about **health** or
**national defense** research feel research matters to them. The data say otherwise: self-relevance
is a broad *"research pays off for society"* orientation, and the specific domains that matter are
**not** the intuitive ones. All correlations use the 9-item core composite (`selfrel_composite`).

```{r predictor-recode}
lvl_likelihood_r <- c("Very unlikely","Somewhat unlikely","Neutral","Somewhat likely","Very likely")
lvl_ideology     <- c("Extremely liberal","Liberal","Slightly liberal","Moderate / middle of the road",
                      "Slightly conservative","Conservative","Extremely conservative")
lvl_climate_trust <- c("Not at all","Slightly","Moderately","Very strongly")
lvl_degree       <- c("No formal education","Did not complete high school",
                      "High school graduate (diploma)","High school graduate (GED)",
                      "Some college (1-4 years, no degree)",
                      "Associate's degree (including occupational or academic degrees)",
                      "Bachelor's degree (BA, BS, etc.)",
                      "Master's degree (MA, MS, MEng, MSW, etc.)",
                      "Professional school degree (MD, DDC, JD, etc.)","Doctoral degree (PhD, EdD, etc.)")

# Source these blocks from the raw `data` frame: some columns (e.g. research_5.1_12)
# were already recoded to numeric above, so re-applying to_num to `d` would wipe them to NA.
d[paste0("research_5.1_", 1:13)] <- lapply(data[paste0("research_5.1_", 1:13)], to_num, lvl_importance)
d[paste0("research_5.2_", 1:13)] <- lapply(data[paste0("research_5.2_", 1:13)], to_num, lvl_likelihood_r)
d[paste0("govtfund_8_", 1:6)]    <- lapply(data[paste0("govtfund_8_", 1:6)],    to_num, lvl_agree5)
d[paste0("univ_2_", 1:10)]       <- lapply(data[paste0("univ_2_", 1:10)],       to_num, lvl_agree5)
d[paste0("climate_4_", 1:4)]     <- lapply(data[paste0("climate_4_", 1:4)],     to_num, lvl_importance)
d$research_1        <- to_num(data$research_1, lvl_know)
d$research_2        <- to_num(data$research_2, lvl_agree5)
d$climate_3         <- to_num(data$climate_3, lvl_climate_trust)
d$politics_ideology <- to_num(data$politics_ideology, lvl_ideology)
d$ses_ladder        <- as.numeric(data$ses_ladder)
d$age               <- as.numeric(data$age)
d$ses_degree        <- to_num(data$ses_degree, lvl_degree)

# Domain labels (research_5.1 importance / research_5.2 payoff share the same areas)
dom_lab <- c(
  "1"="Social science", "2"="Medicine / cure disease", "3"="Environment / clean air & water",
  "4"="Energy independence", "5"="Economic growth / wages", "6"="Manufacturing / domestic production",
  "7"="Defense / national security", "8"="AI / machine learning", "9"="Space exploration",
  "10"="Education systems", "11"="Better public policy", "12"="Understanding to improve own life",
  "13"="Awareness of others' perspectives")
imp_cols <- paste0("research_5.1_", 1:13); names(imp_cols) <- dom_lab
eff_cols <- paste0("research_5.2_", 1:13); names(eff_cols) <- dom_lab

tax_cols <- c("Tax: boosts economy"="govtfund_8_1","Tax: improves health / saves lives"="govtfund_8_2",
              "Tax: drives industry investment"="govtfund_8_3","Tax: makes America a leader"="govtfund_8_4",
              "Tax: protects national security"="govtfund_8_5","Tax: scientific breakthroughs"="govtfund_8_6")
broad_cols <- c(
  "Univ → knowledgeable population"="univ_2_4","Univ → economic growth"="univ_2_8",
  "Univ → compassion / tolerance"="univ_2_7","Univ → innovation"="univ_2_1",
  "Univ → benefits communities"="univ_2_10","Climate research is important"="climate_4_1",
  "Trust in climate scientists"="climate_3","Trust: science is best route to truth"="research_2",
  "Self-rated research knowledge"="research_1","Ideology (liberal → conservative)"="politics_ideology",
  "Subjective SES (ladder)"="ses_ladder","Education"="ses_degree","Age"="age")

# Correlate a named vector of columns against the self-relevance composite
corr_selfrel <- function(named_cols) {
  map_dfr(seq_along(named_cols), function(i) {
    col <- named_cols[[i]]
    ct  <- suppressWarnings(cor.test(d[[col]], d$selfrel_composite, method = "spearman", exact = FALSE))
    tibble(Item = names(named_cols)[i], variable = col,
           r = round(ct$estimate, 2), p = ct$p.value)
  }) |> arrange(desc(r))
}

r_shade <- colDef(width = 80, align = "center",
  cell = function(value, index) {
    p <- rt_data$p[index]
    htmltools::span(sprintf("%.2f%s", value, star(p)))
  },
  style = function(value) {
    a <- min(abs(value), 1)
    bg <- if (value >= 0) sprintf("rgba(78,121,167,%.2f)", a) else sprintf("rgba(225,87,89,%.2f)", a)
    list(background = bg, color = if (a > 0.5) "white" else "black")
  })

show_corr <- function(tbl) {
  reactable(tbl |> select(Item, variable, r), striped = TRUE, compact = TRUE, pagination = FALSE,
            columns = list(Item = colDef(minWidth = 260, style = list(fontWeight = "bold")),
                           variable = colDef(width = 130), r = r_shade))
}
```

## Broad benefit & trust beliefs

```{r broad-corr}
broad_res <- corr_selfrel(broad_cols)
rt_data <- broad_res
show_corr(broad_res)
```

The strongest correlates of self-relevance are **general** "research benefits society" and
science-trust beliefs, not any single research area. Believing universities produce a more
knowledgeable population, economic growth, and tolerance — plus trusting science — each rivals or
exceeds any domain rating below. Ideology is a modest signal (liberals feel research is slightly
more self-relevant); SES and education are weak; age is null.

## Research domains: importance

```{r imp-corr}
imp_res <- corr_selfrel(imp_cols)
rt_data <- imp_res
show_corr(imp_res)
```

Counter to the intuitive hypothesis, **medicine (`research_5.1_2`) and defense
(`research_5.1_7`) are the two weakest** domain predictors. Both suffer a ceiling: almost everyone
rates curing disease as important, so it cannot distinguish who finds research personally relevant.
The domains that *do* track self-relevance are diffuse knowledge / society / discovery areas —
public policy, others' perspectives, space exploration, social science.

## Research domains: expected payoff

```{r eff-corr}
eff_res <- corr_selfrel(eff_cols)
rt_data <- eff_res
show_corr(eff_res)
```

Believing research *will actually deliver* an outcome (`research_5.2`) is more evenly related to
self-relevance than importance is — including for **medicine** (r = `r eff_res |> filter(variable == "research_5.2_2") |> pull(r)`),
which was a null on the importance side. For health, it is efficacy, not stated priority, that matters.

## Tax-investment payoff beliefs

```{r tax-corr}
tax_res <- corr_selfrel(tax_cols)
rt_data <- tax_res
show_corr(tax_res)
```

Beliefs that public research investment pays off (`govtfund_8_1`–`8_6`) are the single strongest
block, led by *boosts the economy* (r = `r tax_res |> filter(variable == "govtfund_8_1") |> pull(r)`).
(`govtfund_8_7`, "benefits people like you," is part of the self-relevance composite and is excluded here.)

## Response-style control

```{r response-style}
d <- d |>
  mutate(imp_mean = rowMeans(across(all_of(imp_cols)), na.rm = TRUE),   # "rate everything important"
         eff_mean = rowMeans(across(all_of(eff_cols)), na.rm = TRUE))   # "everything will pay off"

r_impmean <- round(cor(d$selfrel_composite, d$imp_mean, method = "spearman"), 2)
r_effmean <- round(cor(d$selfrel_composite, d$eff_mean, method = "spearman"), 2)

# Partial r of each domain payoff with selfrel, controlling the general payoff mean
pcor1 <- function(x, y, z) {
  ok <- complete.cases(x, y, z); x <- x[ok]; y <- y[ok]; z <- z[ok]
  rxy <- cor(x, y, method = "spearman"); rxz <- cor(x, z, method = "spearman"); ryz <- cor(y, z, method = "spearman")
  (rxy - rxz * ryz) / sqrt((1 - rxz^2) * (1 - ryz^2))
}
partial_res <- tibble(
  Item      = names(eff_cols),
  `raw r`   = eff_res$r[match(eff_cols, eff_res$variable)],
  `partial r` = map_dbl(eff_cols, \(c) round(pcor1(d[[c]], d$selfrel_composite, d$eff_mean), 2))
) |> arrange(desc(`partial r`))

reactable(partial_res, striped = TRUE, compact = TRUE, pagination = FALSE,
          columns = list(Item = colDef(minWidth = 260, style = list(fontWeight = "bold")),
                         `raw r` = colDef(width = 90, align = "center"),
                         `partial r` = colDef(width = 100, align = "center")))
```

A person's **average** domain rating correlates `r r_impmean` (importance) and `r r_effmean` (payoff)
with self-relevance — people who rate *everything* high also feel research is self-relevant. Partialling
out that general payoff tendency collapses nearly every domain-specific effect to ~0. The lone domain
that survives with a positive partial is **space exploration**
(partial r = `r partial_res |> filter(Item == "Space exploration") |> pull("partial r")`); **AI flips negative**
(partial r = `r partial_res |> filter(Item == "AI / machine learning") |> pull("partial r")`). Above the general
tendency, valuing *basic / curiosity-driven discovery* — not applied tech — distinguishes people who feel
research is personally relevant.

## Regressions (unique domain effects)

```{r domain-regressions}
zscale <- function(v) as.numeric(scale(v))

run_reg <- function(cols) {
  reg <- d |> transmute(selfrel = zscale(selfrel_composite), across(all_of(cols), zscale)) |> na.omit()
  names(reg) <- c("selfrel", names(cols))
  m <- lm(selfrel ~ ., data = reg)
  co <- summary(m)$coefficients
  tibble(Domain = rownames(co), beta = round(co[, 1], 3), p = co[, 4]) |>
    filter(Domain != "(Intercept)") |>
    mutate(sig = star(p)) |>
    arrange(desc(abs(beta)))
}

imp_reg <- run_reg(imp_cols); imp_reg$adjR2 <- round(summary(lm(selfrel ~ .,
  data = setNames(d |> transmute(selfrel = zscale(selfrel_composite), across(all_of(imp_cols), zscale)) |> na.omit(),
                  c("selfrel", names(imp_cols)))))$adj.r.squared, 3)
eff_reg <- run_reg(eff_cols); eff_reg$adjR2 <- round(summary(lm(selfrel ~ .,
  data = setNames(d |> transmute(selfrel = zscale(selfrel_composite), across(all_of(eff_cols), zscale)) |> na.omit(),
                  c("selfrel", names(eff_cols)))))$adj.r.squared, 3)

reg_show <- function(tbl, title) {
  reactable(tbl |> transmute(Domain, `std β` = beta, sig, p = round(p, 3)),
            striped = TRUE, compact = TRUE, pagination = FALSE,
            columns = list(Domain = colDef(minWidth = 260, style = list(fontWeight = "bold")),
                           `std β` = colDef(width = 80, align = "center"),
                           sig = colDef(width = 50, align = "center"),
                           p = colDef(width = 70, align = "center")))
}
```

**Importance model** (adj. R² = `r imp_reg$adjR2[1]`): all 13 importance ratings predicting the composite.

```{r imp-reg-table}
reg_show(imp_reg, "importance")
```

**Payoff model** (adj. R² = `r eff_reg$adjR2[1]`): all 13 expected-payoff ratings.

```{r eff-reg-table}
reg_show(eff_reg, "payoff")
```

Space exploration is the top unique predictor in both models. In the payoff model, **medicine
carries a unique β = `r eff_reg |> filter(Domain == "Medicine / cure disease") |> pull(beta)`**
despite its low raw correlation — again, expected payoff, not stated importance, is what links health
research to self-relevance. Defense is near zero throughout. (Domain ratings are collinear, so read
these as *unique* contributions, not standalone effects.)

```{r save-predictor-csv}
write_csv(broad_res |> select(Item, variable, r, p), file.path(path, "Output", "10_selfrelevance_broad_correlates.csv"))
write_csv(imp_res   |> select(Item, variable, r, p), file.path(path, "Output", "10_selfrelevance_domain_importance.csv"))
write_csv(eff_res   |> select(Item, variable, r, p), file.path(path, "Output", "10_selfrelevance_domain_payoff.csv"))
write_csv(partial_res, file.path(path, "Output", "10_selfrelevance_domain_partial.csv"))
write_csv(bind_rows(mutate(imp_reg, model = "importance"), mutate(eff_reg, model = "payoff")),
          file.path(path, "Output", "10_selfrelevance_domain_regressions.csv"))
```

---

# By facet: other measures × subcomposites {.tabset}

The analyses above use the overall 9-item composite. But the three facets have **different
drivers** — so the same "other measures" are correlated separately against each. Four blocks
follow: the overall composite (repeated) plus one per subcomposite. Each table lists every other
measure sorted by |r| with that target; blue = positive, red = negative, saturation ∝ |r|,
stars mark significance.

```{r facet-setup}
# Combine all "other measures" into one registry, disambiguating the domain labels
imp_named <- setNames(imp_cols, paste("Importance:",      names(imp_cols)))
eff_named <- setNames(eff_cols, paste("Expected payoff:", names(eff_cols)))
all_measures <- c(broad_cols, imp_named, eff_named, tax_cols)
all_groups <- setNames(
  c(rep("Broad benefit / trust", length(broad_cols)),
    rep("Domain importance",     length(imp_named)),
    rep("Domain payoff",         length(eff_named)),
    rep("Tax-investment payoff", length(tax_cols))),
  names(all_measures)
)

facet_targets <- c(
  "selfrel_composite" = "Overall composite (9 items)",
  "selfrel_personal"  = "Personal / close-other benefit",
  "selfrel_everyday"  = "Tangible / everyday relevance",
  "selfrel_applic"    = "Personal applicability / salience"
)

facet_corr <- function(target) {
  map_dfr(seq_along(all_measures), function(i) {
    col <- all_measures[[i]]
    ct  <- suppressWarnings(cor.test(d[[col]], d[[target]], method = "spearman", exact = FALSE))
    tibble(Group = all_groups[[i]], Measure = names(all_measures)[i], variable = col,
           r = round(ct$estimate, 2), p = ct$p.value)
  }) |> arrange(desc(abs(r)))
}

show_facet <- function(tbl) {
  reactable(tbl |> select(Group, Measure, variable, r),
            striped = TRUE, compact = TRUE, pagination = FALSE,
            columns = list(
              Group    = colDef(minWidth = 150),
              Measure  = colDef(minWidth = 230, style = list(fontWeight = "bold")),
              variable = colDef(width = 120),
              r        = r_shade))
}

# Long + wide tables for CSV export and inline references
facet_all  <- map_dfr(names(facet_targets), \(t) facet_corr(t) |> mutate(target = facet_targets[t]))
facet_wide <- facet_all |> select(Group, Measure, variable, target, r) |>
  pivot_wider(names_from = target, values_from = r)
write_csv(facet_all |> select(target, Group, Measure, variable, r, p),
          file.path(path, "Output", "10_selfrelevance_facets_x_othermeasures.csv"))

fw <- function(v, tgt) facet_wide |> filter(variable == v) |> pull(facet_targets[[tgt]])
```

**How the drivers differ.** The overall composite is carried by broad "research pays off / universities
do good" beliefs. But each facet has its own signature: **personal benefit** tracks university-contribution
beliefs (compassion r = `r fw("univ_2_7","selfrel_personal")`, economic growth r = `r fw("univ_2_8","selfrel_personal")`);
**everyday relevance** is where **health finally dominates** — "tax dollars improve health/save lives"
correlates r = `r fw("govtfund_8_2","selfrel_everyday")` and "produce breakthroughs" r = `r fw("govtfund_8_6","selfrel_everyday")`,
far above their links to the other facets; and **personal applicability** is driven not by societal-benefit
beliefs but by **self-rated research knowledge** (r = `r fw("research_1","selfrel_applic")`) — the single top
correlate for that facet. In short: personal benefit is about *society*, everyday relevance is about *tangible
health payoff*, and applicability is about *personal science literacy*.

### Side-by-side comparison {-}

```{r facet-sidebyside}
side <- facet_wide
names(side)[match(unname(facet_targets), names(side))] <- c("Composite", "Personal", "Everyday", "Applicability")
side <- side |> arrange(desc(abs(Composite)))   # order by strength with the overall composite

reactable(
  side |> select(Group, Measure, variable, Composite, Personal, Everyday, Applicability),
  striped = FALSE, compact = TRUE, pagination = FALSE,
  defaultColDef = colDef(headerStyle = list(fontSize = "12px")),
  columns = list(
    Group         = colDef(minWidth = 140),
    Measure       = colDef(minWidth = 210, style = list(fontWeight = "bold")),
    variable      = colDef(width = 110),
    Composite     = heat(),
    Personal      = heat(),
    Everyday      = heat(),
    Applicability = heat()
  )
)
```

Every other measure (rows, sorted by |r| with the composite) against all four targets (columns).
Blue = positive, red = negative; saturation ∝ |r|. Reading across a row shows how a belief's link to
self-relevance shifts by facet — e.g. `govtfund_8_2` (tax → health) jumps from
`r fw("govtfund_8_2","selfrel_personal")` on the personal facet to `r fw("govtfund_8_2","selfrel_everyday")`
on everyday relevance, while `research_1` (research knowledge) is near zero everywhere except
applicability (`r fw("research_1","selfrel_applic")`).

## Overall composite

```{r facet-composite}
rt_data <- facet_corr("selfrel_composite"); show_facet(rt_data)
```

## Personal / close-other benefit

```{r facet-personal}
rt_data <- facet_corr("selfrel_personal"); show_facet(rt_data)
```

## Tangible / everyday relevance

```{r facet-everyday}
rt_data <- facet_corr("selfrel_everyday"); show_facet(rt_data)
```

Note the jump for the health / breakthroughs payoff items relative to every other facet — everyday
self-relevance is the channel through which believing research *tangibly delivers* (especially in
health) matters.

## Personal applicability / salience

```{r facet-applic}
rt_data <- facet_corr("selfrel_applic"); show_facet(rt_data)
```

This facet is the odd one out: broad societal-benefit beliefs correlate only weakly (~.2–.3), while
self-rated research knowledge and expected-payoff beliefs lead. Feeling able to *apply* research is
tied to personal science literacy, not to endorsing research's societal value.

---

# Tax-payoff items × personal vs. applicability facets {.tabset}

Zooming in on the `govtfund_8` block ("public research investment pays off because…"): how does
each tax-payoff belief relate to the two most distinct facets — **personal / close-other benefit**
vs. **personal applicability / salience**? Every item aligns far more with *personal benefit* than
with *applicability*, mirroring the broader pattern that self-relevance is a societal "research pays
off" orientation, not a sense of personally applying research. `govtfund_8_7` is itself part of the
everyday-relevance facet in the core composite, so read its rows as partly overlapping, not independent.

```{r g8-facet-setup}
g8_cols <- paste0("govtfund_8_", 1:7)
g8_lab  <- c(
  govtfund_8_1 = "Tax: boosts economy",
  govtfund_8_2 = "Tax: improves health / saves lives",
  govtfund_8_3 = "Tax: drives industry investment",
  govtfund_8_4 = "Tax: makes America a leader",
  govtfund_8_5 = "Tax: protects national security",
  govtfund_8_6 = "Tax: scientific breakthroughs",
  govtfund_8_7 = "Tax: benefits people like you (in composite)"
)

g8_facet <- map_dfr(g8_cols, function(v) {
  cp <- suppressWarnings(cor.test(d[[v]], d$selfrel_personal, method = "spearman", exact = FALSE))
  ca <- suppressWarnings(cor.test(d[[v]], d$selfrel_applic,   method = "spearman", exact = FALSE))
  tibble(variable = v, Item = unname(g8_lab[v]),
         r_personal = round(cp$estimate, 2), p_personal = cp$p.value,
         r_applic   = round(ca$estimate, 2), p_applic   = ca$p.value)
}) |>
  mutate(gap = round(r_personal - r_applic, 2)) |>
  arrange(desc(r_personal))

write_csv(g8_facet, file.path(path, "Output", "10_selfrelevance_govtfund8_x_facets.csv"))

# Facet-facet overlap, referenced inline below
r_pers_applic <- round(cor(d$selfrel_personal, d$selfrel_applic,
                           method = "spearman", use = "pairwise.complete.obs"), 2)

# Shaded + starred cell for an r column, pulling its p from the matching column in g8_facet
g8_cell <- function(pcol, col_name) {
  colDef(name = col_name, minWidth = 118, align = "center",
    cell = function(value, index) {
      htmltools::span(sprintf("%.2f%s", value, star(g8_facet[[pcol]][index])))
    },
    style = function(value) {
      a  <- min(abs(value), 1)
      bg <- if (value >= 0) sprintf("rgba(78,121,167,%.2f)", a) else sprintf("rgba(225,87,89,%.2f)", a)
      list(background = bg, color = if (a > 0.5) "white" else "black")
    })
}
```

Spearman correlations (`*` p<.05, `**` p<.01, `***` p<.001); blue = positive, saturation ∝ |r|.
Full table saved to `Output/10_selfrelevance_govtfund8_x_facets.csv`.

## Table

```{r g8-facet-table}
reactable(
  g8_facet |> select(Item, variable, r_personal, r_applic, gap),
  striped = TRUE, compact = TRUE, pagination = FALSE,
  columns = list(
    Item       = colDef(minWidth = 250, style = list(fontWeight = "bold")),
    variable   = colDef(width = 120),
    r_personal = g8_cell("p_personal", "Personal / close-other"),
    r_applic   = g8_cell("p_applic",   "Applicability"),
    gap        = colDef(name = "Gap (P − A)", width = 100, align = "center",
                        format = colFormat(digits = 2))
  )
)
```

Every `govtfund_8` item correlates more strongly with **personal / close-other benefit** than with
**personal applicability** (positive gap throughout). The largest gaps are the most self-referential
items — "makes America a leader" and "benefits people like you." The two facets themselves correlate
r = `r r_pers_applic`: related, but the tax-payoff beliefs clearly attach to felt benefit rather than
felt applicability.

## Plot

```{r g8-facet-plot, fig.height=4.5}
plot_df <- g8_facet |>
  transmute(Item = fct_reorder(Item, r_personal),
            Personal = r_personal, Applicability = r_applic) |>
  pivot_longer(c(Personal, Applicability), names_to = "Facet", values_to = "r")

seg_df <- g8_facet |> transmute(Item = fct_reorder(Item, r_personal),
                                x = r_applic, xend = r_personal)

p <- ggplot(plot_df, aes(x = r, y = Item)) +
  geom_segment(data = seg_df, aes(x = x, xend = xend, y = Item, yend = Item),
               inherit.aes = FALSE, color = "gray80", linewidth = 1) +
  geom_point(aes(color = Facet,
                 text = sprintf("<b>%s</b><br>%s: r = %.2f", Item, Facet, r)), size = 3.5) +
  scale_color_manual(values = c(Personal = "#4E79A7", Applicability = "#E15759")) +
  labs(x = "Spearman r with facet", y = NULL, color = NULL) +
  theme_minimal(base_size = 12)

ggplotly(p, tooltip = "text")
```

Each row is one tax-payoff item; the gray segment spans its two facet correlations. Blue (personal
benefit) sits to the right of red (applicability) for every item.

---

# Takeaways

```{r takeaway-values}
comp_appr <- comp_res |> select(Measure, r = govtfund_1, p = p_govtfund_1)
g <- function(m) comp_appr |> filter(Measure == m) |> pull(r)
```

- **Self-relevance is not unidimensional.** Three facets emerge — personal/close-other benefit,
  tangible/everyday relevance, and personal applicability — correlated only modestly across
  clusters. The 9-item core composite has α = `r round(a_core$total$raw_alpha, 2)`.
- **`govfund_10` is reverse-keyed** and is a weak, distinct adjunct; it is excluded from the
  core composite.
- **The composite tracks approval of federal funding** (r = `r g("Self-relevance composite (9-item core)")`)
  and behavioral intentions (see tables above). Facet-level differences show which aspect of
  self-relevance carries the association.
- **Self-relevance is a broad "research pays off" orientation, not a domain preference.** Its
  strongest correlates are general benefit and science-trust beliefs (tax investment boosts the
  economy r = `r tax_res |> filter(variable == "govtfund_8_1") |> pull(r)`; universities → knowledgeable
  population r = `r broad_res |> filter(variable == "univ_2_4") |> pull(r)`), not any single research area.
- **It is not about health or defense.** Rating medicine and national-defense research "important"
  are the two *weakest* domain predictors (ceiling effect on medicine). What survives a response-style
  control is valuing **basic/curiosity-driven discovery** (space exploration, positive unique effect)
  over applied tech (AI, negative). For health, *expected payoff* — not stated importance — is what
  links it to self-relevance.
- **The facets have distinct drivers.** Personal/close-other benefit tracks *university-contribution*
  beliefs; tangible/everyday relevance is the channel where *health payoff* dominates
  (tax → health r = `r fw("govtfund_8_2","selfrel_everyday")`); personal applicability is driven by
  *self-rated research knowledge* (r = `r fw("research_1","selfrel_applic")`), not societal-benefit
  beliefs. The composite masks these differences.

All numeric outputs are saved under `Output/` (`10_selfrelevance_*.csv`).
