---
title: "Step 1 survey analyses"
author: "Nicole Cooper"
date: "5/05/2026"
output:
  html_document:
    code_folding: show
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  pdf_document:
    toc: yes
---

# Overview

**Pilot**: 10 adults (9 female, 1 male; Mean age = 38, SD = 9) were recruited on Prolific to complete the Step 1 survey in the pilot (Cohort 1).

**Cohort 2** 103 (??) adults (53 female, 49 male; Mean age = 39, SD = 13) were recruited on Prolific to complete the Step 1 survey.

**Inclusion criteria**: Adults who reside in the U.S., are fluent English speakers, who have completed at least 50 studies on Prolific, who have an approval rate 95-100, and who have not participated in previous pilot studies. 


```{r setup, include=FALSE,warning=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

```{r, echo = F, messages = F, warnings = F, include = F}
# Clear global environment
remove(list=ls())

# Open libraries
library("tidyverse")
library("tidytext")
library("ggwordcloud")
library("SnowballC")
library("wordcloud")
library("RColorBrewer")
library("wesanderson")
library("tidytext")
library("topicmodels")
library("reactable")
library("grid")
library("gridExtra")

# Set global ggplot theme
theme_set(theme_bw() +
            theme(plot.title = element_text(size=14),
                  axis.text=element_text(size=12),
                  axis.title=element_text(size=14),
                  axis.line = element_line(colour = "gray"),
                  panel.border = element_rect(colour = "gray"),
                  panel.grid.minor = element_blank(),
                  panel.grid.major = element_blank()))

# Set global theme and colors 
palette = c("#772e25", "#c44536", "#ee9b00", "#6F99ADFF", "#197278", "#283d3b")
condition_colors <- c("Gen Persp" = "#772e25", 
                      "Gen Mind" = "#ee9b00", 
                      "Alc Persp" = "#6F99ADFF",
                      "Alc Mind" = "#197278",
                      "Control" = "#283d3b")
palette_sentiment = c(palette[2], palette[5])
palette_schedule = palette[c(1,2,3,6)]
plot_aes = theme_minimal() +
  theme(legend.position = "top",
        legend.text = element_text(size = 8),
        text = element_text(size = 12),
        axis.text = element_text(color = "black"),
        axis.ticks.y = element_blank())
```

```{r, echo = F, messages = F, warnings = F, include = F}
# Define data path
path <- "~/Documents/GitHub/UniversityNews"
```

```{r, echo = F, messages = F, warnings = F, include = F}
# Define cohort
cohort <- 2
```

```{r, echo = F, messages = F, warnings = F, include = F}
# Open Prolific demographics file
d_demo <- read.csv(sprintf("%s/Data/Raw/UnivNews_Step1_Prolific_Cohort%s.csv", path, cohort)) %>%
  select(Participant.id, Age, Sex, Completion.code, Authenticity.check..QID444, Authenticity.check..Bots) %>%
  rename(PROLIFIC_PID = Participant.id,
         age = Age,
         sex = Sex, 
         prolific_check_llm = Authenticity.check..QID444, 
         prolific_check_bot = Authenticity.check..Bots) 

# Open Qualtrics survey dataset
data <- read.csv(sprintf("%s/Data/Raw/UnivNews_Step1_Cohort%s.csv", path, cohort)) %>%
  tail(-2) %>% # remove subtitles
  filter(!(Status == "Survey Preview")) %>% # remove test sessions
  filter(consent == "I agree to participate in this study.") %>%
  plyr::join(d_demo) %>%
  arrange(StartDate) 

# Check participants' gender distribution
data %>%
  group_by(sex) %>%
  tally()

# Check participants' age distribution
data %>%
  summarize(mean_age = mean(as.numeric(age)),
           sd_age = round(sd(as.numeric(age)),2))
 
```

# Feedback {.tabset}

## Open-ended Feedback {.unnumbered}

<p>&nbsp;</p>

`Open-Ended Feedback`: "Please type below any comments or suggestions you might have for the research team."

```{r, echo = F, messages = F, warnings = F}
data %>%
  select( end_feedback) %>%
  filter(!(is.na(end_feedback) | end_feedback == "" | end_feedback == "n/a" |
             end_feedback == "N/A" | end_feedback == "None" |
           end_feedback == "none"))  %>%
  reactable(striped = TRUE,
            filterable = TRUE)
```

# Study Duration {.tabset}

## Total study duration {.unnumbered}

<p>&nbsp;</p>

Below see the study duration (as calculated by Qualtrics) separately for each condition.

<p>&nbsp;</p>

```{r, echo = F, messages = F, warnings = F, fig.align='center'}
d3 <- data %>%
  mutate(time_list = strsplit(as.character(worktimeArray), ","),
         time_numeric = lapply(time_list, function(x) as.numeric(gsub("[^0-9.-]", "", x))),
         true_total_on_task_sec = sapply(time_numeric, function(x) sum(x[x > 0], na.rm = TRUE)),
         true_on_task_min = round(true_total_on_task_sec / 60, 2),
         true_total_off_task_sec = sapply(time_numeric, function(x) sum(abs(x[x < 0]), na.rm = TRUE)),
         true_off_task_min = round(true_total_off_task_sec / 60, 2),
         study_duration_min = round(as.numeric(`Duration..in.seconds.`) / 60, 2)) %>%
  select(PROLIFIC_PID, study_duration_min, true_on_task_min, true_off_task_min)

d3 %>%
  summarize(`duration (mins)` = round(mean(study_duration_min, na.rm = TRUE),2)) %>%
  arrange(desc(`duration (mins)`)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

## On Task Time {.unnumbered}

<p>&nbsp;</p>

Below see the time spent on task separately for each condition.

<p>&nbsp;</p>

```{r, echo = F, messages = F, warnings = F, fig.align='center'}
d3 %>%
  summarize(`on task time (mins)` = round(mean(true_on_task_min, na.rm = TRUE),2)) %>%
  arrange(desc(`on task time (mins)`)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```


## Off Task Time {.unnumbered}

<p>&nbsp;</p>

Below see the amount of time participants spent off task; separate by condition.

<p>&nbsp;</p>

```{r, echo = F, messages = F, warnings = F, fig.align='center'}
d3 %>%
  summarize(`off task time (mins)` = round(mean(true_off_task_min, na.rm = TRUE),2)) %>%
  arrange(desc(`off task time (mins)`)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

# Quality Checks {.tabset}

## Qualtrics reCAPTCHA {.unnumbered}

Qualtrics calculates  one value per participant, Q_RecaptchaScore, which measures bot likelihood (from 0 to 1) using Google reCAPTCHA v3. A score below 0.5 indicates a high likelihood of a bot, while 0.5 or higher suggests a human.

```{r, echo = F, messages = F, warnings = F, fig.align='center'}
data %>%
  group_by(Q_RecaptchaScore)  %>%
  mutate(Q_RecaptchaScore = round(as.numeric(Q_RecaptchaScore), 
                                  2)) %>%
  tally() %>%
  arrange(desc(Q_RecaptchaScore)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

## Prolific LLM Check {.unnumbered}

Prolific computes LLM authenticity checks which identify when participants are using LLMs (like ChatGPT) to answer free-text questions. These look for suspicious behaviors like copy-pasting and tab-switching on free-text questions only.
```{r, echo = F, messages = F, warnings = F, fig.align='center'}
data %>%
  group_by(prolific_check_llm)  %>%
  tally() %>%
  arrange(desc(n)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

## Prolific Both Check {.unnumbered}

Prolific performs bot checks to identify when AI agents or fully automated bots are answering the study. These look for non-human or scripted behaviour across all question types.
```{r, echo = F, messages = F, warnings = F, fig.align='center'}
data %>%
  group_by(prolific_check_bot)  %>%
  tally() %>%
  arrange(desc(n)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

## Attention Check 1 {.unnumbered}

Prolific performs bot checks to identify when AI agents or fully automated bots are answering the study. These look for non-human or scripted behaviour across all question types.
```{r, echo = F, messages = F, warnings = F, fig.align='center'}
data %>%
  group_by(attention_1)  %>%
  tally() %>%
  arrange(desc(n)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

## Attention Check 2 {.unnumbered}

Prolific performs bot checks to identify when AI agents or fully automated bots are answering the study. These look for non-human or scripted behaviour across all question types.
```{r, echo = F, messages = F, warnings = F, fig.align='center'}
data %>%
  group_by(attention_2)  %>%
  tally() %>%
  arrange(desc(n)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```

## Attention Check 3 {.unnumbered}

Prolific performs bot checks to identify when AI agents or fully automated bots are answering the study. These look for non-human or scripted behaviour across all question types.
```{r, echo = F, messages = F, warnings = F, fig.align='center'}
data %>%
  group_by(attention_3)  %>%
  tally() %>%
  arrange(desc(n)) %>%
  knitr::kable(format = "pandoc", digits = 2)
```


