---
title: "Study 1: Promising beliefs"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, fig.path = "figs/")
knitr::opts_chunk$set(dev = "svglite")

options(scipen=999)
```

# prep {.tabset}
## load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, qgraph, igraph, netcontrol, reactable, broom, stringr, DescTools, ggrepel, svglite)
```


IMPORTANT NOTE: re-knitting this notebook will require X11.  

## define functions

*IMPORTANT NOTE* "cluster" and "community" are used interchangeably in this script. "Community" is used to refer to data-derived clusters of nodes in the belief network. 

```{r}
# function to count the number of connections between clusters

detect_connection = function(c1, c2, c1_name, c2_name) {
  community1 = communities[[c1]]
  community2 = communities[[c2]]
  
  connections = sum(
    (edges[,1] %in% community2 & edges[,2] %in% community1) |
    (edges[,1] %in% community1 & edges[,2] %in% community2)
    )
  
  sprintf("connections between %s & %s = %s", c1_name, c2_name, connections)
}

# function to convert a qgraph object to an igraph object
# adapted from {qgraph::as.igraph.qgraph}
as.igraph.qgraph <- function(x,...,attributes=TRUE)
{
  if (!"qgraph"%in%class(x))
  {
    stop("Input must be qgraph x")
  }

  # Extract graph:
  edgesort <- x$graphAttributes$Graph$edgesort
  E <- as.matrix(as.data.frame(x$Edgelist[c("from","to")]))
  E <- E[edgesort,,drop=FALSE]
  srt <- cbind(pmin(E[,1],E[,2]),pmax(E[,1],E[,2]))
  Dir <- x$Edgelist$directed[edgesort]
  Bi <-  x$Edgelist$bidirectional[edgesort]
  
  Graph <- graph.edgelist(E, any(Dir))
  E(Graph)$weight <- x$Edgelist$weight[edgesort]
  
  # Arrow mode:
  aMode <- ifelse(Dir,2,0)
  # Set duplicated and bidir to doubleheaded:
  aMode <- ifelse(Bi & (duplicated(srt)|duplicated(srt,fromLast=TRUE)), 3, aMode)
  # Store in graph:
  E(Graph)$arrow.mode <- aMode
  
  ## Set attributes:
  if (attributes)
  {
    ## Node attributes:
    V(Graph)$frame.color <- x$graphAttributes$Nodes$border.color
    V(Graph)$frame.color[!x$graphAttributes$Nodes$borders] <- NA
    V(Graph)$label.color <- x$graphAttributes$Nodes$label.color
    V(Graph)$label <- x$graphAttributes$Nodes$labels
    V(Graph)$shape <- x$graphAttributes$Nodes$shape
    V(Graph)$shape[!V(Graph)$shape%in%c("circle", "square", "csquare", "rectangle", "crectangle", "vrectangle", "pie")] <- "none"
    V(Graph)$color <- x$graphAttributes$Nodes$color
    V(Graph)$size <- x$graphAttributes$Nodes$width / max((-1/72)*(x$nNodes)+5.35,1) * 4
    V(Graph)$size2 <- x$graphAttributes$Nodes$height / max((-1/72)*(x$nNodes)+5.35,1) * 4
    
    ## Edge attributes:
    E(Graph)$curved <- x$graphAttributes$Edges$curve[edgesort]
    E(Graph)$color <- x$graphAttributes$Edges$color[edgesort]
    if (is.character(x$graphAttributes$Edges$labels)) E(Graph)$label <- x$graphAttributes$Edges$labels[edgesort]
    if (!is.null(x$graphAttributes$Edges$label.color)) E(Graph)$label.color <- x$graphAttributes$Edges$label.color[edgesort]
    E(Graph)$lty <- x$graphAttributes$Edges$lty[edgesort]
    E(Graph)$width <- x$graphAttributes$Edges$width[edgesort]
  }
  
  return(Graph)
}
```

## define aesthetics
```{r}
palette_valence = c("#2D93AD","#c44535")
palette_communities_network = c("#98D7BF", "#B4C6E4", "#DE6C5F", "#6087BF", "#F3B61F")
palette_communities = c("instrumentality" =  "#98D7BF", 
                        "impact" =  "#B4C6E4", 
                        "control" =  "#DE6C5F", 
                        "importance/negative" =  "#6087BF", 
                        "belonging" =  "#F3B61F")

plot_aes = theme_minimal() +
  theme(legend.position = "top",
        # legend.text = element_text(size = 14),
        # text = element_text(size = 16),
        # panel.grid.major = element_blank(),
        # panel.grid.minor = element_blank(),
        axis.text = element_text(color = "black"),
        axis.line = element_line(colour = "black"),
        axis.ticks.y = element_blank())
```

## load and tidy {.tabset}
```{r}
data_dir = "~/Documents/GitHub/PLTV-GOTV-2024/data/"

data_tpb = read.csv(file.path(data_dir, "ind_diffs_gotv_2024_beliefs.csv")) %>%
  filter(grepl("TPB|motiv", scale_name)) %>%
  mutate(scale_name = ifelse(scale_name == "vote_motive" & item %in% 1:2 , "vote_motive_controlled", scale_name),
         scale_name = ifelse(scale_name == "vote_motive" & item %in% 3:5 , "vote_motive_autonomous", scale_name),
         item = gsub("reg$", "register", item),
         item = case_when(item == "vote_attitude_1" ~ "attitude_instrumental",
                          item == "vote_attitude_2" ~ "attitude_experiential",
                          item == "vote_efficacy_1" ~ "efficacy_capacity",
                          item == "vote_efficacy_2" ~ "efficacy_autonomy",
                          item == "vote_norms_injunctive" ~ "norms_injunctive",
                          item == "vote_norms_descriptiv" ~ "norms_descriptive", .default = item),
         item = ifelse(grepl("motive", scale_name), sprintf("%s_%s", scale_name, item), item),
         item = ifelse(scale_name == "vote_motive_controlled", gsub("_motive", "", item),
                ifelse(scale_name == "vote_motive_autonomous", gsub("_motive", "", item), item)),
         item = gsub("vote_", "", item),
         value = as.numeric(value)) %>%
  select(study, pID, scale_name, item, value)

data_tpb_mean = data_tpb %>%
  filter(scale_name == "TPB") %>%
  mutate(item = ifelse(grepl("behav|intention", item), sprintf("%s_1", item), item)) %>%
  extract(item, c("item", "number"), "(attitude|behav_past|efficacy|intention_plan|intention_register|intention_vote|norms)_(.*)") %>%
  group_by(pID, item) %>%
  summarize(value = mean(value, na.rm = TRUE))

belief_text = read.csv("belief_text.csv") %>%
  select(text, text_abbreviated, community)

targeted_beliefs = read.csv("targeted_beliefs.csv") %>%
  mutate(text = case_when(grepl("personally vote", text) ~ "It doesn’t matter if I personally vote",
                          .default = text)) %>%
  left_join(., belief_text)

data_beliefs = read.csv(file.path(data_dir, "beliefs_gotv_2024_beliefs.csv")) %>%
  left_join(., belief_text) %>%
  mutate(text = gsub(" ", "_", text))

categories = data_beliefs %>%
  select(text_abbreviated, community) %>%
  unique() %>%
  mutate(text_abbreviated = gsub("_", " ", text_abbreviated)) %>%
  arrange(text_abbreviated)

merged = data_tpb_mean %>%
  mutate(value = ifelse(is.nan(value), NA, value)) %>%
  spread(item, value) %>%
  mutate(intender = ifelse(intention_vote == 7, "yes", "no"),
         intender = factor(intender, levels = c("yes", "no")),
         behav_past = case_when(behav_past == 1 ~ "voted",
                                behav_past == 0 ~ "didn't vote",
                                is.na(behav_past) ~ "not eligible", .default = NA),
         behav_past = factor(behav_past, levels = c("not eligible", "didn't vote", "voted"))) %>%
  left_join(., select(data_beliefs, pID, scale_name, text, value, valence, community))
```

# correlations {.tabset}
## voting intention
```{r}
cor_fun = function(df) {
  cor.test(df$intention_vote, df$value, method = "pearson") %>%
    broom::tidy()
}

cor_vote = merged %>%
  select(pID, intention_vote, text, value) %>%
  mutate(text = gsub(" ", "_", text)) %>%
  group_by(text) %>%
  nest() %>%
  mutate(cor = map(data, cor_fun)) %>%
  select(-data) %>%
  unnest(cor) %>%
  mutate(p.value = round(p.value, 3),
         `r [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  rename("df" = parameter) %>%
  select(text, estimate, `r [95% CI]`, df, p.value)

cor_vote %>%
  select(-estimate) %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)
```

## among beliefs {.tabset}
### network {.tabset}
```{r, fig.width=10, fig.height=8, dev="svg"}
cor_mat = data_beliefs %>%
  select(pID, text_abbreviated, value) %>%
  mutate(text_abbreviated = gsub(" ", "_", text_abbreviated)) %>%
  spread(text_abbreviated, value) %>%
  select(-pID) %>%
  cor(., use = "pairwise.complete.obs")

labels = colnames(cor_mat) %>%
  gsub("_", " ", .) %>%
  stringr::str_wrap(., width = 15)

shape = "ellipse"
width = 4
height = 4

graph = cor_mat %>%
  qgraph::qgraph(graph = "glasso", sampleSize = 274, threshold = .05,
                 DoNotPlot = TRUE, labels = labels)

graph_converted_abs = as.igraph.qgraph(graph)

# convert edge weights to absolute values
edge_weights <- E(graph_converted_abs)$weight
abs_weights <- abs(edge_weights)
E(graph_converted_abs)$weight <- abs_weights

# cluster (i.e., "community") detection
wtc <- cluster_walktrap(graph_converted_abs)

communities = communities(wtc)

# plot
cor_mat %>%
  qgraph::qgraph(layout = "spring", repulsion = 2,
       graph = "glasso", sampleSize = 274, threshold = .05,
       nonsig = "hide", edge.labels = FALSE, 
       negCol = "#2D93AD", posCol = "#c44535",
       groups = communities,
       colors = palette_communities_network,
       labels = labels, label.scale = FALSE, label.cex = .3,
       shape = shape, vsize = width, vsize2 = height,
       legend = FALSE)
```

### connections between clusters
```{r}
edges <- as_edgelist(as.igraph(graph))

detect_connection(2,1, "impact", "instrumentality")
detect_connection(2,3, "impact", "control")
detect_connection(2,4, "impact", "negative")
detect_connection(2,5, "impact", "belonging")

detect_connection(4,1, "negative", "instrumentality")
detect_connection(4,3, "negative", "control")
detect_connection(4,5, "negative", "belonging")

detect_connection(3,1, "control", "instrumentality")
detect_connection(3,5, "control", "belonging")

detect_connection(1,5, "belonging", "instrumentality")

```

### modularity
```{r}
modularity(wtc)
```

### centrality {.tabset}
```{r}
graph_converted = as.igraph.qgraph(graph)

centrality_eigen = igraph::eigen_centrality(graph_converted)$vector %>%
  as.data.frame() %>%
  rename("eigenvector" = ".") %>%
  mutate(eigenvector_abs = abs(eigenvector))

node_centrality = data.frame(text_abbreviated = labels) %>%
  mutate(text_abbreviated = gsub("\n", " ", text_abbreviated)) %>%
  bind_cols(., centrality_eigen)

corr_centrality = cor_vote %>%
  mutate(text = gsub("_", " ", text),
         valence = ifelse(estimate > 0, "positive", "negative"),
         z = DescTools::FisherZ(rho = estimate),
         z_abs = abs(z)) %>%
  left_join(., belief_text) %>%
  ungroup() %>%
  select(text_abbreviated, z, z_abs, valence) %>%
  left_join(., node_centrality) %>%
  mutate(text_abbreviated = stringr::str_wrap(text_abbreviated, width = 15))

centrality_targeted = corr_centrality %>%
  mutate(targeted = ifelse(text_abbreviated %in% stringr::str_wrap(targeted_beliefs$text_abbreviated, width = 15), "yes", "no")) %>%
  filter(targeted == "yes")
```

#### relationship with intention correlation
```{r, fig.width=8, fig.height=6}
corr_centrality %>%
  left_join(., categories %>%
              mutate(text_abbreviated = stringr::str_wrap(text_abbreviated, width = 15))) %>%
  ggplot(aes(eigenvector_abs, z_abs)) +
  geom_point(aes(color = community), size = 3) +
  geom_smooth(method = "lm", color = "grey50") +
  labs(x = "belief eigenvector centrality (absolute value)", y = "mean absolute correlation with voting intention") +
  ggrepel::geom_label_repel(data = centrality_targeted, aes(label = text_abbreviated),
                            fill = "white",
                            alpha = .7,
                            box.padding = .5, 
                            point.padding = .25,
                            label.size = .5, size = 3,
                            segment.color = 'grey50', show.legend = FALSE) +
  scale_color_manual(values = palette_communities) +
  plot_aes +
  theme(legend.position = "none")

cor.test(corr_centrality$z_abs, corr_centrality$eigenvector_abs)
```

#### centrality comparison {.tabset}
```{r, fig.width=6, fig.height=12}
node_centrality %>%
  left_join(., categories) %>%
  group_by(community) %>%
  summarize(M = round(mean(eigenvector_abs), 2)) %>%
  arrange(desc(M))

node_centrality %>%
  left_join(., categories) %>%
  mutate(z = scale(eigenvector_abs, center = TRUE, scale = FALSE)) %>%
  ggplot(aes(reorder(text_abbreviated, z), z, fill = community)) +
  geom_bar(stat = "identity", position = position_dodge(.9)) +
  coord_flip() +
  scale_fill_manual(values = palette_communities, name = "") +
  labs(x = "", y = "eigenvector centrality (mean centered)") +
  plot_aes +
  theme(legend.position = "none")
```


# percent of people who intend to vote
* Voting intention = "strongly agree"

```{r}
percent_intenders = merged %>%
  select(pID, intender) %>%
  unique() %>%
  group_by(intender) %>%
  summarize(n = n()) %>%
  spread(intender, n) %>%
  ungroup() %>%
  mutate(yes_percent = round((yes / (no + yes)) * 100, 1),
         no_percent = round((no / (no + yes)) * 100, 1))

percent_intenders %>%
  reactable::reactable(striped = TRUE, resizable = TRUE)
```

# percent to move
* Percent of people who do not currently endorse the belief at the highest level ("strongly agree" or "strongly disagree")

```{r}
pecent_move = data_beliefs %>%
  filter(!is.na(value)) %>%
  mutate(value_rev = ifelse(valence == "Negative", 8 - value, value),
         strongest = ifelse(value_rev == 7, "yes", "no")) %>%
  select(pID, text, strongest) %>%
  group_by(text, strongest) %>%
  summarize(n = n()) %>%
  spread(strongest, n) %>%
  ungroup() %>%
  mutate(percent = round((no / (yes + no)) * 100, 1),
         text = gsub("_", " ", text)) %>%
  arrange(desc(percent))

pecent_move %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)

write.csv(pecent_move, "output/percent_move_table.csv", row.names = FALSE)
```

# example of calculating percent to gain

* Percent to gain = the potential increase in people who intend to vote (i.e. endorse "strongly agree") that could be achieved if everyone strongly held the belief (i.e. endorsed "strongly agree" or "strongly disagree")

* Percent to gain calculation = percentage of people who intend to vote and strongly endorse the belief (97.8%) - total percentage of people who intend to vote (70.3%)

* Example belief = Voting is consistent with my core values

```{r}
percents = merged %>%
  select(pID, valence, text, value, intender) %>%
  unique() %>%
  filter(!is.na(value)) %>%
  mutate(value_rev = ifelse(valence == "Negative", 8 - value, value),
         strongest = ifelse(value_rev == 7, "strongest_yes", "strongest_no")) %>%
  select(pID, intender, text, strongest) %>%
  group_by(text, intender, strongest) %>%
  summarize(n = n()) %>%
  spread(intender, n) %>%
  ungroup() %>%
  mutate(no = ifelse(is.na(no), 0, no),
         total = yes + no) %>%
  group_by(text, strongest) %>%
  mutate(yes_percent = round((yes / total) * 100, 1),
         no_percent = round((no / total) * 100, 1),
         total_percent = round((total / total) * 100, 1))

belief_ns = percents %>%
  filter(text == "Voting_is_consistent_with_my_core_values") %>%
  select(text, strongest, yes, no) %>%
  gather(intender, n, yes, no) %>%
  spread(strongest, n) %>%
  mutate(total = strongest_no + strongest_yes) 

belief_ns %>%
  bind_rows(data.frame(text = "Voting_is_consistent_with_my_core_values",
                       intender = "total",
                       strongest_no = sum(belief_ns$strongest_no),
                       strongest_yes = sum(belief_ns$strongest_yes),
                       total = sum(belief_ns$total))) %>%
  mutate(strongest_no = sprintf("%s (%.1f percent)", strongest_no, ((strongest_no / sum(belief_ns$strongest_no)) * 100)),
         strongest_yes = sprintf("%s (%.1f percent)", strongest_yes, ((strongest_yes / sum(belief_ns$strongest_yes)) * 100)),
         total = sprintf("%s (%.1f percent)", total, ((total / sum(belief_ns$total)) * 100))) %>%
  ungroup() %>%
  select(-text) %>%
  reactable::reactable(striped = TRUE, resizable = TRUE)

```

# means, correlations, percentage to gain table

* `mean_vote-yes` = mean belief strength for people who intend to vote (i.e. responded "strongly agree") 

* `mean_vote-no` = mean belief strength for people who do not (strongly) intend to vote (i.e. responded something other than "strongly agree") 

* `diff [95% CI]` = mean difference in belief strength and 95% confidence interval for people who intend versus don't intend to vote (yes > no)

* ` r [95% CI]` = correlation and 95% confidence interval between the belief strength and continuous voting intention

* `percent_strongest_vote-yes` = percentage of people who intend to vote who hold this belief strongly (i.e. endorsed "strongly agree" or "strongly disagree")

* `percent_strongest_vote-no` = percentage of people who don't intend to vote who hold this belief strongly (i.e. endorsed "strongly agree" or "strongly disagree")

* `percent_gain` = the potential increase in people who intend to vote (i.e. endorse "strongly agree") that could be achieved if everyone strongly held the belief (i.e. endorsed "strongly agree" or "strongly disagree")


```{r}
t_fun = function(df) {
  t.test(value ~ intender, data = df) %>%
    broom::tidy()
}

percent_gain = percents %>%
  select(text, strongest, contains("percent")) %>%
  mutate(percent_gain = round(yes_percent - percent_intenders$yes_percent[1], 1)) %>%
  filter(strongest == "strongest_yes") %>%
  ungroup() %>%
  select(text, yes_percent, no_percent, percent_gain)
  

table_data = merged %>%
  select(pID, intention_vote, text, value, intender) %>%
  group_by(text) %>%
  nest() %>%
  mutate(mod = map(data, t_fun)) %>%
  select(-data) %>%
  unnest(mod) %>%
  mutate(estimate1 = round(estimate1, 2),
         estimate2 = round(estimate2, 2),
         p.value = round(p.value, 3),
         `diff [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  rename("mean_vote-yes" = estimate1,
         "mean_vote-no" = estimate2) %>%
  rename("df" = parameter) %>%
  select(text, estimate, `mean_vote-yes`, `mean_vote-no`, `diff [95% CI]`) %>%
  left_join(., select(cor_vote, text, `r [95% CI]`)) %>%
  left_join(., percent_gain) %>%
  rename("percent_strongest_vote-yes" = yes_percent,
         "percent_strongest_vote-no" = no_percent) %>%
  mutate(text = gsub("_", " ", text)) %>%
  arrange(desc(percent_gain))

write.csv(select(table_data, -estimate), "output/belief_table.csv", row.names = FALSE)

table_data %>%
  select(-estimate) %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)
```

# beliefs with >20% to gain {.tabset}
```{r}
merged %>%
  select(pID, intention_vote, text, value, intender, community) %>%
  group_by(text, community) %>%
  nest() %>%
  mutate(mod = map(data, t_fun)) %>%
  select(-data) %>%
  unnest(mod) %>%
  mutate(estimate1 = round(estimate1, 2),
         estimate2 = round(estimate2, 2),
         p.value = round(p.value, 3),
         `diff [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  rename("mean_vote-yes" = estimate1,
         "mean_vote-no" = estimate2) %>%
  rename("df" = parameter) %>%
  select(community, text, `mean_vote-yes`, `mean_vote-no`, `diff [95% CI]`) %>%
  left_join(., select(cor_vote, text, `r [95% CI]`)) %>%
  left_join(., percent_gain) %>%
  rename("percent_strongest_vote-yes" = yes_percent,
         "percent_strongest_vote-no" = no_percent) %>%
    mutate(text = gsub("\\,", "", text),
           text = gsub("\\'", "", text),
           text = gsub("\\’", "", text),
           text = gsub("\\(", "", text),
           text = gsub("\\)", "", text),
           text = gsub("_", " ", text)) %>%
  filter(percent_gain >= 20) %>%
  arrange(-percent_gain) %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)
```

# correlations among beliefs & TPB measures {.tabset}
```{r}
cor_fun = function(df) {
  cor.test(df$tpb_value, df$value, method = "pearson") %>%
    broom::tidy()
}

cor_vote = merged %>%
  gather(tpb_variable, tpb_value, intention_vote, intention_plan, attitude, efficacy, norms) %>%
  select(pID, tpb_variable, tpb_value, text, value) %>%
  mutate(text = gsub(" ", "_", text)) %>%
  group_by(tpb_variable, text) %>%
  nest() %>%
  mutate(cor = map(data, cor_fun)) %>%
  select(-data) %>%
  unnest(cor) %>%
  mutate(p.value = round(p.value, 3),
         `r [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  rename("df" = parameter) %>%
  select(tpb_variable, text, estimate, `r [95% CI]`, df, p.value)

cor_register = merged %>%
  filter(!intention_register == 8) %>%
  gather(tpb_variable, tpb_value, intention_register) %>%
  select(pID, tpb_variable, tpb_value, text, value) %>%
  mutate(text = gsub(" ", "_", text)) %>%
  group_by(tpb_variable, text) %>%
  nest() %>%
  mutate(cor = map(data, cor_fun)) %>%
  select(-data) %>%
  unnest(cor) %>%
  mutate(p.value = round(p.value, 3),
         `r [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  rename("df" = parameter) %>%
  select(tpb_variable, text, estimate, `r [95% CI]`, df, p.value)

cor_vote_registration = merged %>%
  mutate(registration_status = ifelse(intention_register == 8, "registered", "unregistered")) %>%
  gather(tpb_variable, tpb_value, intention_vote, intention_plan, attitude, efficacy, norms) %>%
  select(pID, registration_status, tpb_variable, tpb_value, text, value) %>%
  mutate(text = gsub(" ", "_", text)) %>%
  group_by(registration_status, tpb_variable, text) %>%
  nest() %>%
  mutate(cor = map(data, cor_fun)) %>%
  select(-data) %>%
  unnest(cor) %>%
  mutate(p.value = round(p.value, 3),
         `r [95% CI]` = sprintf("%.2f [%.2f, %.2f]", estimate, conf.low, conf.high)) %>%
  rename("df" = parameter) %>%
  select(tpb_variable, text, estimate, `r [95% CI]`, df, p.value)
```

## all
Intention to register is only among people who have not yet registered
```{r}
cor_tpb = cor_vote %>%
  bind_rows(., cor_register) %>%
  select(-df, -p.value, -estimate) %>%
  spread(tpb_variable, `r [95% CI]`) %>%
  left_join(., select(data_beliefs, text, community) %>% unique()) %>%
  select(community, text, intention_register, intention_vote, intention_plan, everything()) %>%
  arrange(community, desc(intention_vote)) %>%
  mutate(text = gsub("_", " ", text)) 

cor_tpb %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)

cor_tpb %>%
  select(community, text, intention_register, intention_plan, attitude, norms, efficacy) %>%
  mutate(community = gsub("_", " ", community),
         intention_register = gsub(" \\[", "\n\\[", intention_register),
         intention_plan = gsub(" \\[", "\n\\[", intention_plan),
         attitude = gsub(" \\[", "\n\\[", attitude),
         norms = gsub(" \\[", "\n\\[", norms),
         efficacy = gsub(" \\[", "\n\\[", efficacy)) %>%
  rename("category" = community) %>%
  write.csv(., "output/tpb_correlations.csv", row.names = FALSE)
```

## average by category 
```{r}
cor_vote %>%
  bind_rows(., cor_register) %>%
  left_join(., select(data_beliefs, text, valence, community) %>% unique()) %>%
  mutate(estimate = ifelse(valence == "Negative" & !grepl("dis|control", community), estimate * -1, estimate)) %>% 
  group_by(tpb_variable, community) %>%
  summarize(r_mean = round(mean(estimate, na.rm = TRUE), 2)) %>%
  spread(tpb_variable, r_mean) %>%
  select(community, intention_register, intention_vote, intention_plan, everything()) %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)
```

## by registration status
```{r}
cor_vote_registration %>%
  select(-df, -p.value, -estimate) %>%
  spread(tpb_variable, `r [95% CI]`) %>%
  left_join(., select(data_beliefs, text, community) %>% unique()) %>%
  select(community, text, registration_status, intention_vote, intention_plan, everything()) %>%
  arrange(community, text, registration_status) %>%
  mutate(text = gsub("_", " ", text)) %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)
```


# correlation between centrality and Hornik & Woolf metrics {.tabset}
```{r}
centrality_gain = node_centrality %>%
  left_join(., belief_text) %>%
  mutate(text = gsub(" ", "_", text)) %>%
  left_join(., percent_gain) %>%
  left_join(., mutate(pecent_move, text = gsub(" ", "_", text))) %>%
  left_join(., table_data %>% mutate(text = gsub(" ", "_", text)) %>% select(text, estimate, `r [95% CI]`)) %>%
  mutate(r = abs(as.numeric(gsub(" \\[.*", "", `r [95% CI]`))),
         text_abbreviated = stringr::str_wrap(text_abbreviated, width = 15))

centrality_table = centrality_gain %>%
  select(text, eigenvector_abs, r, percent, percent_gain) %>%
  mutate(text = gsub("_", " ", text),
         eigenvector_abs = round(eigenvector_abs, 2)) %>%
  rename("percent_move" = percent)

write.csv(centrality_table, "output/centrality_table.csv", row.names = FALSE)
```

## comparing percentage to gain and network centrality {.tabset}
```{r, fig.width=7, fig.height=6.5}
cor.test(centrality_gain$percent_gain, centrality_gain$eigenvector_abs)

centrality_gain %>%
  ggplot(aes(eigenvector_abs, percent_gain)) +
  geom_hline(yintercept = 22.03) +
  geom_vline(xintercept = 0.64) +
  geom_rect(aes(xmin=0.64, xmax=Inf, ymin=22.03, ymax=Inf), alpha = .002) +
  geom_point(aes(color = community), size = 3) +
  labs(x = "belief eigenvector centrality (absolute value)", y = "percentage to gain") +
  ggrepel::geom_label_repel(data = centrality_gain, aes(label = text_abbreviated),
                            fill = "white",
                            alpha = .7,
                            box.padding = .5, 
                            point.padding = .25,
                            label.size = .5, size = 2.25,
                            segment.color = 'grey50', show.legend = FALSE) +
  scale_color_manual(values = palette_communities, name = "") +
  plot_aes +
  theme(legend.position = "top")
```

### above average beliefs {.tabset}
```{r}
centrality_gain %>%
  filter(percent_gain > mean(percent_gain) & eigenvector_abs > mean(eigenvector_abs)) %>%
  select(text, community) %>%
  mutate(text = gsub("_", " ", text)) %>%
  arrange(community)
```

## percentage to move {.tabset}
```{r, fig.width=7, fig.height=6.5}
cor.test(centrality_gain$percent, centrality_gain$eigenvector_abs)

centrality_gain %>%
  ggplot(aes(eigenvector_abs, percent)) +
  geom_point(aes(color = community), size = 3) +
  geom_smooth(method = "lm", color = "grey50") +
  labs(x = "belief eigenvector centrality (absolute value)", y = "percentage to gain") +
  ggrepel::geom_label_repel(data = centrality_gain, aes(label = text_abbreviated),
                            fill = "white",
                            alpha = .7,
                            box.padding = .5, 
                            point.padding = .25,
                            label.size = .5, size = 2.5,
                            segment.color = 'grey50', show.legend = FALSE) +
  scale_color_manual(values = palette_communities) +
  plot_aes +
  theme(legend.position = "top")
```

## table
```{r}
centrality_table %>%
  reactable::reactable(filterable = TRUE, sortable = TRUE, striped = TRUE, resizable = TRUE)
```

