---
title: "PLTV 2024 belief survey: cleaning"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    df_print: paged
    highlight: tango
    theme: united
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = FALSE)
options(scipen=999)
```

# load packages
```{r}
if(!require('pacman')) {
	install.packages('pacman')
}

pacman::p_load(tidyverse, knitr, DT, devtools)

if (!require(scorequaltrics)) {
  devtools::install_github('dcosme/qualtrics', ref = "dev/enhance")
}
```

# define variables and paths

To pull data from Qualtrics, you need a credentials file with an API token associated with your account. To create the file, follow these steps.

1. Generate an API token for Qualtrics. Follow the steps outlined [here](https://www.qualtrics.com/support/integrations/api-integration/overview/).

2. Save a Qualtrics credentials text file with the following format. In this example, the file is being saved as `~/credentials.yaml.PENN`. The `baseurl` is the URL for your institution on Qualtrics. Use `upenn.co1.qualtrics.com` for Penn Qualtrics.

```
token: oILNW6...[your qualtrics API token]
baseurl: upenn.co1.qualtrics.com
```

`cred_file_location` = path to your Qualtrics credential file. 

`survey_name_filter` = regular expression to filter the available surveys

```{r}
keep_columns = '(ResponseId|Finished|Progress|Date|DistributionChannel|id$|contact_|ineligible)'
cred_file_location = "~/credentials.yaml.PENN" # This is a file you will need to create using the instructions above
survey_name_filter = "PLTV-Falk Lab Beliefs Survey 2024$|PLTV-Falk Lab Beliefs Survey 2024 SONA"
ignore_items = "ResponseId|IPAddress|RecipientFirstName|RecipientLastName|RecipientEmail|ExternalReference|LocationLatitude|LocationLongitude"
```

# fetch qualtrics data
The Qualtrics API is pretty finicky. If you get the following error, just rerun the `get_survey_data` command until it works:

```
Error in qualtrics_response_codes(f, raw = TRUE) : 
  Qualtrics API complains that the requested resource cannot be found (404 error).
Please check if you are using the correct survey ID.
```
```{r}
# load credential file
credentials = scorequaltrics::creds_from_file(cred_file_location)

# filter
surveysAvail = scorequaltrics::get_surveys()
surveysFiltered = filter(surveysAvail, grepl(survey_name_filter, name))
knitr::kable(arrange(select(surveysFiltered, name), name))

# fetch data
surveys_long = scorequaltrics::get_survey_data(surveysFiltered,
                                               credentials, 
                                               pid_col = keep_columns) %>%
               filter(!grepl(ignore_items, item)) %>% #filter out identifiable data
  select(survey_name, DistributionChannel, ResponseId, id, ineligible, contains("Date"), Finished, Progress, item, value, contains("contact"))

```

# quality checks 
## invariance
Goal is to identify participants who are responding the same way across all items within a survey

```{r, fig.width = 8}
d = data
# Define your multi-item scales (adjust to match your actual scale names/items)                                            
   scales <- list( 
    research_3  = grep("^research_3_\\d+$",   names(d), value = TRUE),
    research_4  = grep("^research_4_\\d+$",   names(d), value = TRUE),                                                       
    research_5a = grep("^research_5.1_\\d+$", names(d), value = TRUE),  # #→. after read.csv
    research_5b = grep("^research_5.2_\\d+$", names(d), value = TRUE),                                                       
    research_6a = grep("^research_6.1_\\d+$", names(d), value = TRUE),
    research_6b = grep("^research_6.2_\\d+$", names(d), value = TRUE),                                                       
    govtfund_4  = grep("^govtfund_4_\\d+$",   names(d), value = TRUE),
    govtfund_5  = grep("^govtfund_5_\\d+$",   names(d), value = TRUE),                                                       
    govtfund_6  = grep("^gotvfund_6_\\d+$",   names(d), value = TRUE),
    govtfund_8  = grep("^govtfund_8_\\d+$",   names(d), value = TRUE),                                                       
    govtfund_9  = grep("^govtfund_9_\\d+$",   names(d), value = TRUE)
  )                                                                                                                          
                 
  # For each scale, flag rows where all non-NA responses are identical (straight-lining)                                     
  straightline_flags <- map_dfc(scales, function(cols) {
    d |>                                                                                                                     
      select(all_of(cols)) |>
      mutate(across(everything(), as.numeric)) |>                                                                            
      rowwise() |>
      mutate(flag = {                                                                                                        
        vals <- c_across(everything())
        vals <- vals[!is.na(vals)]                                                                                           
        if (length(vals) < 2) NA else n_distinct(vals) == 1
      }) |>                                                                                                                  
      ungroup() |>
      pull(flag)                                                                                                             
  }) |>           
    bind_cols(d |> select(ResponseId), y = _) |>
    rename_with(~ paste0("straightline_", names(scales)), -ResponseId)                                                       
                                                                                                                             
  # Summarize: how many participants straight-lined each scale                                                               
  straightline_flags |>                                                                                                      
    summarise(across(starts_with("straightline_"), ~ sum(.x, na.rm = TRUE)))                                                 
                                                                                                                             
  # Flag participants who straight-lined ANY scale                                                                           
  d <- d |>                                                                                                                  
    left_join(straightline_flags, by = "ResponseId") |>
    mutate(any_straightline = if_any(starts_with("straightline_"), ~ .x == TRUE))                                            
   
  d |> count(any_straightline)                     

```

