---
title: "WiN Script to Extract Conditions and Daily Diary Reminders"
author: "Ovidia Stanoi"
date: "2026-02-13"
output: html_document
---

Clear global environment.
```{r, message=F, warning=F}
remove(list=ls())
```

Open packages.
```{r, message=F, warning=F}
library("tidyverse")
library("purrr")
library("glue")
library("lubridate")
```

Define file directory (change path as needed).
```{r}
path <- "/Users/omayat/Box sync/WiN-ARO-Extension_Data_857525"
path <- "~/Library/CloudStorage/Box-Box/WiN-ARO-Extension_Data_857525"
```

Define cohort number.
```{r}
cohort <- 4
```

Define the start date when the study was posted. 
```{r}
start_day <- ymd_hms("2026-07-10 17:00:00")
```

Open raw version of the baseline survey (update the name of the .csv file as needed).
```{r}
b <- read.csv(sprintf("%s/Data/Raw/Cohort %s/WiN_Baseline_Cohort%s.csv", 
                      path, cohort, cohort)) %>%
  tail(-2) %>% # remove subtitles
  filter(StartDate > start_day) # filter out previous cohorts
```

Open the Prolific .csv file including the demographic information of the participants and add the variable representing the bot check to the main baseline file. 
```{r, messages = F, warnings = F}
prolific <- read.csv(sprintf("%s/Data/Raw/Cohort %s/WiN_Baseline_Prolific_Cohort%s.csv", 
                             path, cohort, cohort)) %>%
  select(Participant.id, Authenticity.check..Bots) %>%
  rename(PROLIFIC_PID = Participant.id,
         prolific_check_bot = Authenticity.check..Bots) 

# Merge with the baseline survey
b <- plyr::join(b, prolific)
```

Calculate how much time participants spent off-task.
```{r}
b <- b %>%
  mutate(time_list = strsplit(as.character(worktimeArray), ","),
         time_numeric = lapply(time_list, function(x) as.numeric(gsub("[^0-9.-]", "", x))),
         off_task_sec = sapply(time_numeric, function(x) sum(abs(x[x < 0]), na.rm = TRUE)),
         off_task_min = round(off_task_sec / 60, 2),
         q_duration = round(as.numeric(`Duration..in.seconds.`)/60,2))
```

Merge multiple entries (e.g., if a participant completed the survey twice, save only the first answers).
```{r}
b <- b %>%
  arrange(PROLIFIC_PID, desc(as.numeric(as.character(Progress)))) %>% # order data based on progress
  group_by(PROLIFIC_PID) %>% # group by id
  dplyr::summarise(across(everything(), ~na.omit(.)[1])) # combine data of participants with multiple answers
```

Exclude and do not pay participants who: 

1) did not pass the screener (age < 18 or not veterans), or

2) did not consent to the baseline survey, or

3) did not pass the two attention checks, or

4) have a Q_RecaptchaScore score < 0.5 and were identified as likely bots by Prolific, or

5) spent more than 15 mins off-task. 

```{r}
# First create a list of all participants who should 
# already be filtered out in Prolific
# because they did not pass the screener
exclude_screener <- b %>% 
  filter(age < 18 | veteran_YN == "No")  %>% 
  select(PROLIFIC_PID, age, veteran_YN)
  
# Next, create a list of all participants who did not meet 
# the other exclusion criteria and who will have to be excluded manually
exclude <- b %>%
  filter(!(PROLIFIC_PID %in% exclude_screener$PROLIFIC_PID)) %>%
  mutate(Q_RecaptchaScore = as.numeric(as.character(Q_RecaptchaScore)),
         consent = ifelse(consent_1 == "I agree to participate in this study.", "pass", "fail"),
         attention_1 = ifelse(attention_1 == "Somewhat agree", "pass", "fail"), 
         attention_2 = ifelse(attention_2 == "Disagree", "pass", "fail"), 
         qualtrics_check_bot = ifelse(Q_RecaptchaScore < 0.5, "pass", "fail"), 
         prolific_check_bot = ifelse(!(prolific_check_bot == "low"), "pass", "fail"), 
         off_task_time = ifelse(off_task_min <= 15, "pass", "fail"),
         consent = ifelse(consent == "fail", "fail", "pass"),
         attention = ifelse(attention_1 == "fail" & attention_2 == "fail", "fail", "pass"),
         bot_checks = ifelse(qualtrics_check_bot == "fail" & prolific_check_bot == "fail", "fail", "pass"),) %>%
  filter(consent == "fail" | attention == "fail" |
           bot_checks == "fail" | off_task_time == "fail")  %>% 
  select(PROLIFIC_PID, consent, attention, bot_checks, off_task_time, off_task_min) 
```

For the remaining people, if they agreed to participate in the daily diary portion of the study, extract pIDs, conditions, & active weeks. For the participants in the alcohol perspective condition, also extract the name of their study peer. 
```{r}
df <- b %>%
  filter(!(PROLIFIC_PID %in% exclude_screener$PROLIFIC_PID) & 
           !(PROLIFIC_PID %in% exclude$PROLIFIC_PID) & 
           # exclude participants who did not meet inclusion criteria
           dd_consent == "Yes, I would like to participate in the second portion of the study.") %>%
                   # exclude participants who did not consent to participate in the daily diary portion of the study
  filter(!(PROLIFIC_PID == "6633ee8ca35ae4b909110ee3")) %>%
                     # exclude one participant who messaged on prolific that he would not be able to continue
  select(PROLIFIC_PID, condition, activeweek, study_peer) %>%
  arrange(condition, activeweek)
```

Add the reminders that each participant should receive each day of the daily diary.
```{r}
for (day in 1:12) {
  df <- df %>%
    mutate(
      !!paste0("reminder_day", day) := case_when(

        condition == "gen_perspective" & activeweek == 1 & day <= 6 ~ "gen_perspective",
        condition == "gen_perspective" & activeweek == 1 & day >  6 ~ "gen_react_naturally",

        condition == "gen_perspective" & activeweek == 2 & day <= 6 ~ "gen_react_naturally",
        condition == "gen_perspective" & activeweek == 2 & day >  6 ~ "gen_perspective",

        condition == "gen_mindful" & activeweek == 1 & day <= 6 ~ "gen_mindful",
        condition == "gen_mindful" & activeweek == 1 & day >  6 ~ "gen_react_naturally",

        condition == "gen_mindful" & activeweek == 2 & day <= 6 ~ "gen_react_naturally",
        condition == "gen_mindful" & activeweek == 2 & day >  6 ~ "gen_mindful",

        condition == "alc_perspective" & activeweek == 1 & day <= 6 ~ "alc_perspective",
        condition == "alc_perspective" & activeweek == 1 & day > 6 ~ "alc_react_naturally",

        condition == "alc_perspective" & activeweek == 2 & day <= 6 ~ "alc_react_naturally",
        condition == "alc_perspective" & activeweek == 2 & day > 6 ~ "alc_perspective",

        condition == "alc_mindful" & activeweek == 1 & day <= 6 ~ "alc_mindful",
        condition == "alc_mindful" & activeweek == 1 & day >  6 ~ "alc_react_naturally",

        condition == "alc_mindful" & activeweek == 2 & day <= 6 ~ "alc_react_naturally",
        condition == "alc_mindful" & activeweek == 2 & day >  6 ~ "alc_mindful",

        condition == "control" ~ "",

        TRUE ~ paste0("", day)
      )
    )
}
```

Save different .csv files locally.
```{r}
## .csv file that needs to be uploaded to Qualtrics
## it includes info about participants' conditions, active weeks, and student peers
df_cond <- df %>%
  select(PROLIFIC_PID, condition, activeweek, study_peer) %>%
  mutate(study_peer = ifelse(condition == "alc_perspective", study_peer, NA))
readr::write_excel_csv(df_cond, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Participant_Conditions_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the different types of reminders participants 
## should receive each day
df_reminders <- df %>%
  select(-study_peer) %>%
  arrange(condition)
readr::write_excel_csv(df_reminders, 
                       sprintf("%s/Prolific reminders/WiN_Participant_Reminders_Cohort%s.csv", 
                               path, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the all group
pid_all <- df %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_all, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_All_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the general perspective-taking & active week 1 group 
pid_gen_persp_1 <- df %>%
  filter(condition == "gen_perspective" & activeweek == 1) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_gen_persp_1, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_General_Perspective_Week1_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the general perspective-taking & active week 2 group 
pid_gen_persp_2 <- df %>%
  filter(condition == "gen_perspective" & activeweek == 2) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_gen_persp_2, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_General_Perspective_Week2_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the general mindful & active week 1 group 
pid_gen_mind_1 <- df %>%
  filter(condition == "gen_mindful" & activeweek == 1) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_gen_mind_1, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_General_Mindful_Week1_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the general mindful & active week 2 group 
pid_gen_mind_2 <- df %>%
  filter(condition == "gen_mindful" & activeweek == 2) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_gen_mind_2, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_General_Mindful_Week2_Cohort%s.csv", 
                               path, cohort, cohort), na = "")


## .csv file that includes the Prolific IDs to be included in the alcohol perspective-taking & active week 1 group 
pid_alc_persp_1 <- df %>%
  filter(condition == "alc_perspective" & activeweek == 1) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_alc_persp_1, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_Alcohol_Perspective_Week1_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the alcohol perspective-taking & active week 2 group 
pid_alc_persp_2 <- df %>%
  filter(condition == "alc_perspective" & activeweek == 2) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_alc_persp_2, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_Alcohol_Perspective_Week2_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the alcohol mindful & active week 1 group 
pid_alc_mind_1 <- df %>%
  filter(condition == "alc_mindful" & activeweek == 1) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_alc_mind_1, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_Alcohol_Mindful_Week1_Cohort%s.csv", 
                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the alcohol mindful & active week 2 group 
pid_alc_mind_2 <- df %>%
  filter(condition == "alc_mindful" & activeweek == 2) %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_alc_mind_2, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_Alcohol_Mindful_Week2_Cohort%s.csv", 
                                               path, cohort, cohort), na = "")

## .csv file that includes the Prolific IDs to be included in the control group 
pid_control <- df %>%
  filter(condition == "control") %>%
  select(PROLIFIC_PID) 
readr::write_excel_csv(pid_control, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Prolific_Participant_Group_Control_Cohort%s.csv", 
                                            path, cohort, cohort), na = "")

## .csv file that includes all participants whose submissions should be rejected
readr::write_excel_csv(exclude, 
                       sprintf("%s/Prolific participant groups/Cohort %s/WiN_Participant_Prolific_Reject_Cohort%s.csv", 
                                        path, cohort, cohort), na = "")
```









