---
title: "July Newsletter — Data Cleaning"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(qualtRics)
library(here)
library(knitr)
```

## Load data

```{r load}
QUALTRICS_PATH <- here("Newsletter testing", "Step3_JulyNewsletter", "Data",
                       "UnivNews_JulyNewsletter_July 6, 2026_10.30.csv")
PROLIFIC_PATH  <- here("Newsletter testing", "Step3_JulyNewsletter", "Data",
                       "prolific_demographic_export_6a4566994567f01b9f90d339.csv")
CLEANED_RDS    <- here("Newsletter testing", "Step3_JulyNewsletter", "Data", "july_newsletter_clean.rds")

raw <- read_survey(QUALTRICS_PATH)
```

Raw data: **`r nrow(raw)` rows**, **`r ncol(raw)` columns**.

## Basic exclusions

```{r exclusions}
n_raw <- nrow(raw)

d <- raw |>
  filter(DistributionChannel == "anonymous") |>
  filter(Finished == TRUE) |>
  filter(PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID))

n_after_basic <- nrow(d)
```

| Step | N |
|------|---|
| Raw | `r n_raw` |
| Anonymous channel only | `r nrow(filter(raw, DistributionChannel == "anonymous"))` |
| Finished | `r nrow(filter(raw, DistributionChannel == "anonymous", Finished == TRUE))` |
| Valid Prolific PID | `r n_after_basic` |

## Prolific merge

```{r prolific-merge}
prolific <- read_csv(PROLIFIC_PATH, show_col_types = FALSE) |>
  rename(
    PROLIFIC_PID    = `Participant id`,
    prolific_status = Status,
    prolific_time   = `Time taken`,
    prolific_bot    = `Authenticity check: Bots`
  ) |>
  select(PROLIFIC_PID, prolific_status, prolific_time, prolific_bot,
         Age, Sex, `Ethnicity simplified`, `Country of residence`,
         `Student status`, `Employment status`)

d <- d |> left_join(prolific, by = "PROLIFIC_PID")

cat("Prolific status:\n"); print(table(d$prolific_status, useNA = "ifany"))
cat("\nProlific bot check:\n"); print(table(d$prolific_bot, useNA = "ifany"))
```

## Hard exclusions: Prolific non-completions

```{r hard-exclusions}
n_before_hard <- nrow(d)
d <- d |> filter(!prolific_status %in% c("RETURNED", "TIMED-OUT"))
cat(n_before_hard - nrow(d), "participant(s) removed (RETURNED or TIMED-OUT).\n")
```

## Data quality flags

Three authenticity checks are available for this survey:

- **reCAPTCHA** (`Q_RecaptchaScore` < 0.5): low score indicates likely bot.
- **Prolific bot check** (`prolific_bot` == "mixed"): Prolific's internal signal of mixed authenticity. "N/A" means unassessed (account too new), not failed — not treated as a flag.
- **Attention check** (`attnA_1_1`–`attnA_3_1`, `attnB_1_1`–`attnB_3_1`): six sliders across two blocks that participants are instructed to set to 100. Any value ≠ 100 on any item is a failure. NAs are treated as failures.

`flag_any_auth` marks any single failure (informational). `flag_exclude` marks 2+ failures (exclusion criterion), consistent with Step 2.

```{r flags}
RECAPTCHA_THRESHOLD <- 0.5
ATTN_CORRECT        <- 100

d <- d |>
  mutate(
    flag_recaptcha = !is.na(Q_RecaptchaScore) & Q_RecaptchaScore < RECAPTCHA_THRESHOLD,
    flag_bot       = prolific_bot == "mixed",
    flag_attention = is.na(attnA_1_1) | attnA_1_1 != ATTN_CORRECT |
                     is.na(attnA_2_1) | attnA_2_1 != ATTN_CORRECT |
                     is.na(attnA_3_1) | attnA_3_1 != ATTN_CORRECT |
                     is.na(attnB_1_1) | attnB_1_1 != ATTN_CORRECT |
                     is.na(attnB_2_1) | attnB_2_1 != ATTN_CORRECT |
                     is.na(attnB_3_1) | attnB_3_1 != ATTN_CORRECT,
    n_flags        = rowSums(cbind(flag_recaptcha, flag_bot, flag_attention),
                             na.rm = TRUE),
    flag_any_auth  = n_flags >= 1,
    flag_exclude   = n_flags >= 2
  )
```

```{r flag-summary}
d |>
  summarise(
    `reCAPTCHA < 0.5`          = sum(flag_recaptcha,  na.rm = TRUE),
    `Prolific bot = mixed`      = sum(flag_bot,        na.rm = TRUE),
    `Failed attention check`    = sum(flag_attention,  na.rm = TRUE),
    `Any auth flag`             = sum(flag_any_auth,   na.rm = TRUE),
    `2+ auth flags (excluded)`  = sum(flag_exclude,    na.rm = TRUE)
  ) |>
  kable()
```

```{r flag-detail}
d |>
  filter(flag_any_auth) |>
  select(PROLIFIC_PID, prolific_bot,
         reCAPTCHA = Q_RecaptchaScore,
         attnA_1_1, attnA_2_1, attnA_3_1,
         attnB_1_1, attnB_2_1, attnB_3_1,
         flag_recaptcha, flag_bot, flag_attention, n_flags, flag_exclude) |>
  arrange(desc(n_flags)) |>
  kable()
```

```{r apply-exclusions}
n_before <- nrow(d)
d <- d |> filter(!flag_exclude)
n_excluded <- n_before - nrow(d)
```

`r n_excluded` participant(s) excluded for 2+ flags. **N after exclusions: `r nrow(d)`**.

## Missing data on key outcomes

```{r missing}
outcome_vars <- c(
  "july1_relevant_1", "july2_relevant_1",
  "july3_relevant_1", "july4_relevant_1"
)

d |>
  summarise(across(all_of(outcome_vars), ~sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N missing") |>
  kable()
```

## Condition assignment

Each participant was assigned a condition (relevance or control) for each of the 4 articles independently.

```{r conditions}
d |>
  count(condition_1, condition_2, condition_3, condition_4) |>
  kable(col.names = c("Article 1", "Article 2", "Article 3", "Article 4", "N"))

cat("\nMarginal condition counts per article:\n")
for (i in 1:4) {
  col <- paste0("condition_", i)
  cat("  Article", i, ":\n")
  print(table(d[[col]], useNA = "ifany"))
}
```

## Save

```{r save}
saveRDS(d, CLEANED_RDS)
```

Cleaned data saved to `r CLEANED_RDS`. **Final N = `r nrow(d)`**.
