---
title: "Step 2 — Data Cleaning"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(qualtRics)
library(here)
library(knitr)

source(here("Step2", "analysis", "config.R"))
```

## Load data

```{r load}
if (USE_API) {
  qualtrics_api_credentials(
    api_key  = Sys.getenv("QUALTRICS_API_KEY"),
    base_url = paste0(DATA_CENTER, ".qualtrics.com")
  )
  raw <- fetch_survey(
    surveyID = SURVEY_ID,
    label    = FALSE,
    convert  = FALSE
  )
} else {
  raw <- read_survey(LOCAL_DATA_PATH)
}
```

Raw data: **`r nrow(raw)` rows**, **`r ncol(raw)` columns**.

## Exclusions

```{r exclusions}
n_raw <- nrow(raw)

PILOT_START <- as.POSIXct("2026-06-03 20:00:00", tz = "UTC")  # 4pm ET = 8pm UTC

d <- raw |>
  # Keep only real Prolific responses (anonymous link); removes preview, test, and imported
  filter(DistributionChannel == "anonymous") |>
  filter(Finished == TRUE) |>
  # Remove responses recorded before pilot launch
  filter(RecordedDate >= PILOT_START)

# Remove unfilled Prolific PID template rows (only relevant if PIDs are present)
if (any(!is.na(raw$PROLIFIC_PID))) {
  d <- d |>
    filter(PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID))
}

n_final <- nrow(d)
```

| Step | N |
|------|---|
| Raw | `r n_raw` |
| Anonymous channel only | `r nrow(filter(raw, DistributionChannel == "anonymous"))` |
| Finished | `r nrow(filter(raw, DistributionChannel == "anonymous", Finished == TRUE))` |
| After pilot start cutoff (≥ 4pm ET 2026-06-03) | `r nrow(filter(raw, DistributionChannel == "anonymous", Finished == TRUE, RecordedDate >= PILOT_START))` |
| After Prolific PID filter (if applicable) | `r n_final` |

## Rename variables

Column names in this export use custom export tags. Mapping to analysis-ready names:

```{r rename}
d <- d |>
  rename(
    # ArticleRate block
    share_direct    = rate_1_1,
    share_social    = rate_2_1,
    article_agree_1 = rate_3_1,
    article_agree_2 = rate_3_2,
    # GovtFunding block
    govtfund_general = govtfund_1,
    govtfund_cuts    = govtfund_2,
    # BehaviorIntentions block (3 items shown via loop)
    behavior_intent_1 = `2_behavint_1`,
    behavior_intent_2 = `3_behavint_1`,
    behavior_intent_3 = `4_behavint_1`
    # climate_1, climate_2, climate_3_1/2/3 already named correctly
  )
```

## Coalesce read_more

The "want to read more" slider is split across condition-specific columns (one per loop row per condition). Only one will be non-NA per participant.

```{r coalesce}
d <- d |>
  mutate(
    read_more = coalesce(
      as.numeric(`1_relevance_1_1`),
      as.numeric(`2_relevance_1_1`),
      as.numeric(`3_relevance_1_1`),
      as.numeric(`1_action_1_1`),
      as.numeric(`2_action_1_1`),
      as.numeric(`3_action_1_1`),
      as.numeric(`1_control_1_1`)
    )
  )
```

## Condition factor

```{r condition}
d <- d |>
  filter(condition %in% CONDITION_LEVELS) |>
  mutate(condition = factor(condition, levels = CONDITION_LEVELS))
```

```{r condition-table}
d |>
  count(condition) |>
  kable(col.names = c("Condition", "N"))
```

## Numeric coercion

```{r numeric}
outcome_vars <- c(
  "share_direct", "share_social", "read_more",
  "article_agree_1", "article_agree_2",
  "govtfund_general", "govtfund_cuts",
  "behavior_intent_1", "behavior_intent_2", "behavior_intent_3",
  "climate_1", "climate_2",
  "climate_3_1", "climate_3_2", "climate_3_3"
)

d <- d |>
  mutate(across(all_of(outcome_vars), as.numeric))
```

## Missing data

```{r missing}
d |>
  summarise(across(all_of(outcome_vars), ~sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N missing") |>
  kable()
```

## Save

```{r save}
saveRDS(d, CLEANED_RDS)
```

Cleaned data saved to `r CLEANED_RDS`. **Final N = `r n_final`**.
