---
title: "Step 2 — Data Cleaning"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(qualtRics)
library(here)
library(knitr)

source(here("Step2", "analysis", "config.R"))
```

## Load data

```{r load}
if (USE_API) {
  qualtrics_api_credentials(
    api_key  = Sys.getenv("QUALTRICS_API_KEY"),
    base_url = paste0(DATA_CENTER, ".qualtrics.com")
  )
  raw <- fetch_survey(
    surveyID = SURVEY_ID,
    label    = FALSE,
    convert  = FALSE
  )
} else {
  raw <- read_survey(LOCAL_DATA_PATH)
}
```

Raw data: **`r nrow(raw)` rows**, **`r ncol(raw)` columns**.

## Exclusions

```{r exclusions}
n_raw <- nrow(raw)

d <- raw |>
  # Keep only real Prolific responses (anonymous link); removes preview, test, and imported
  filter(DistributionChannel == "anonymous") |>
  filter(Finished == TRUE) |>
  # Keep only Cohort 1 (launched 2026-06-04); excludes 30 pilot responses from 2026-06-03
  filter(RecordedDate >= COHORT1_START)

# Remove unfilled Prolific PID template rows (only relevant if PIDs are present)
if (any(!is.na(raw$PROLIFIC_PID))) {
  d <- d |>
    filter(PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID))
}

n_final <- nrow(d)
```

| Step | N |
|------|---|
| Raw | `r n_raw` |
| Anonymous channel only | `r nrow(filter(raw, DistributionChannel == "anonymous"))` |
| Finished | `r nrow(filter(raw, DistributionChannel == "anonymous", Finished == TRUE))` |
| Cohort 1 only (≥ 2026-06-04 midnight ET) | `r nrow(filter(raw, DistributionChannel == "anonymous", Finished == TRUE, RecordedDate >= COHORT1_START))` |
| After Prolific PID filter (if applicable) | `r n_final` |

## Rename variables

Column names in this export use custom export tags. Mapping to analysis-ready names:

```{r rename}
d <- d |>
  rename(
    # ArticleRate block
    share_direct    = rate_1_1,
    share_social    = rate_2_1,
    article_self_relev   = rate_3_1,
    article_social_relev = rate_3_2,
    # GovtFunding block
    govtfund_general = govtfund_1,
    govtfund_cuts    = govtfund_2,
    # BehaviorIntentions block (3 items shown via loop)
    behavior_intent_1 = `2_behavint_1`,
    behavior_intent_2 = `3_behavint_1`,
    behavior_intent_3 = `4_behavint_1`
    # climate_1, climate_2, climate_3_1/2/3 already named correctly
  )
```

## Coalesce read_more

Each condition variant is in its own block (`relevance1_1_1` … `control_1_1`). Only the block shown to each participant will be non-NA; coalesce collapses them into a single column.

```{r coalesce}
d <- d |>
  mutate(
    read_more = coalesce(
      relevance1_1_1, relevance2_1_1, relevance3_1_1,
      action1_1_1, action2_1_1, action3_1_1,
      control_1_1
    )
  )
```

## Condition factor

```{r condition}
d <- d |>
  filter(condition %in% CONDITION_LEVELS) |>
  mutate(condition = factor(condition, levels = CONDITION_LEVELS))
```

```{r condition-table}
d |>
  count(condition) |>
  kable(col.names = c("Condition", "N"))
```

## Numeric coercion

```{r numeric}
outcome_vars <- c(
  "share_direct", "share_social", "read_more",
  "article_self_relev", "article_social_relev",
  "govtfund_general", "govtfund_cuts",
  "behavior_intent_1", "behavior_intent_2", "behavior_intent_3",
  "climate_3_1", "climate_3_2", "climate_3_3"
)

covariate_vars <- c(
  "climate_1",   # Do you think global warming is happening? (1–3)
  "climate_2"    # Assuming it is, caused by...? (1–4)
)

d <- d |>
  mutate(across(all_of(c(outcome_vars, covariate_vars)), as.numeric))
```

## Prolific participant data

```{r prolific-merge}
PROLIFIC_EXPORT <- here("Data", "Raw", "UnivNews_Step2_prolific_demographic.csv")

prolific <- read_csv(PROLIFIC_EXPORT, show_col_types = FALSE) |>
  rename(
    PROLIFIC_PID       = `Participant id`,
    prolific_status    = Status,
    prolific_timetaken = `Time taken`,
    prolific_bot       = `Authenticity check: Bots`
  ) |>
  select(PROLIFIC_PID, prolific_status, prolific_timetaken, prolific_bot,
         Age, Sex, `Ethnicity simplified`, `Country of residence`,
         `Student status`, `Employment status`)

d <- d |> left_join(prolific, by = "PROLIFIC_PID")

cat("Status:\n"); print(table(d$prolific_status, useNA = "ifany"))
cat("\nBot check:\n"); print(table(d$prolific_bot, useNA = "ifany"))
```

## Hard exclusions: Prolific non-completions

Remove participants who returned or timed out on Prolific regardless of Qualtrics completion status.

```{r hard-exclusions}
n_before_hard <- nrow(d)
d <- d |> filter(!prolific_status %in% c("RETURNED", "TIMED-OUT"))
cat(n_before_hard - nrow(d), "participant(s) removed (RETURNED or TIMED-OUT on Prolific).\n")
```

## Data quality flags

Exclude participants flagged on 2+ authenticity checks: reCAPTCHA < 0.5, Prolific bot = "mixed", failed attention check.

- Off-task time is recorded as an informational column but not used as an exclusion criterion (per Prolific guidelines).
- Prolific bot `N/A` (unassessed account) is not treated as a flag.
- Attention check NAs are not treated as failures.
- `flag_any_auth`: convenience column marking any single authenticity failure (not an exclusion).

```{r flags}
RECAPTCHA_THRESHOLD <- 0.5
OFF_TASK_THRESHOLD  <- 900

d <- d |>
  mutate(
    flag_offtask   = totalOffTask > OFF_TASK_THRESHOLD,
    flag_recaptcha = Q_RecaptchaScore < RECAPTCHA_THRESHOLD,
    flag_prolific  = prolific_bot == "mixed",
    flag_attention = !is.na(attention_1) & attention_1 != 4,
    n_flags        = rowSums(cbind(flag_recaptcha, flag_prolific, flag_attention),
                             na.rm = TRUE),
    flag_any_auth  = n_flags >= 1,
    flag_exclude   = n_flags >= 2
  )
```

```{r flag-summary}
d |>
  summarise(
    `Off-task > 15 min (info only)` = sum(flag_offtask,   na.rm = TRUE),
    `reCAPTCHA < 0.5`               = sum(flag_recaptcha, na.rm = TRUE),
    `Prolific bot = mixed`          = sum(flag_prolific,  na.rm = TRUE),
    `Failed attention check`        = sum(flag_attention, na.rm = TRUE),
    `Any auth flag (flag_any_auth)` = sum(flag_any_auth,  na.rm = TRUE),
    `2+ auth flags (excluded)`      = sum(flag_exclude,   na.rm = TRUE)
  ) |>
  kable()
```

```{r flag-detail}
d |>
  filter(flag_any_auth | flag_offtask) |>
  select(PROLIFIC_PID, condition, prolific_bot, attention_1,
         `Off-task (min)` = totalOffTask,
         reCAPTCHA = Q_RecaptchaScore,
         flag_offtask, flag_recaptcha, flag_prolific, flag_attention,
         n_flags, flag_exclude) |>
  mutate(`Off-task (min)` = round(`Off-task (min)` / 60, 1)) |>
  arrange(desc(n_flags), desc(flag_offtask)) |>
  kable()
```

```{r apply-exclusions}
n_before <- nrow(d)
d <- d |> filter(!flag_exclude)
n_excluded <- n_before - nrow(d)
```

`r n_excluded` participant(s) excluded for 2+ flags. N after exclusions: **`r nrow(d)`**.

## Missing data

```{r missing}
d |>
  summarise(across(all_of(outcome_vars), ~sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N missing") |>
  kable()
```

## Save

```{r save}
saveRDS(d, CLEANED_RDS)
```

Cleaned data saved to `r CLEANED_RDS`. **Final N = `r n_final`**.
