---
title: "Step 2 — Data Cleaning"
date: today
format:
  html:
    embed-resources: true
    toc: true
    toc-depth: 2
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
---

```{r setup}
library(tidyverse)
library(qualtRics)
library(here)
library(knitr)

source(here("Step2", "analysis", "config.R"))
```

## Load data

```{r load}
if (USE_API) {
  qualtrics_api_credentials(
    api_key  = Sys.getenv("QUALTRICS_API_KEY"),
    base_url = paste0(DATA_CENTER, ".qualtrics.com")
  )
  raw <- fetch_survey(
    surveyID      = SURVEY_ID,
    label         = FALSE,
    convert       = FALSE,
    force_request = TRUE
  )
} else {
  raw <- read_survey(LOCAL_DATA_PATH)
}
```

Raw data: **`r nrow(raw)` rows**, **`r ncol(raw)` columns**.

### Column names

```{r colnames}
names(raw)
```

## Exclusions

```{r exclusions}
d <- raw |>
  filter(Status == 0 | is.na(Status)) |>
  filter(Finished == TRUE | Finished == 1) |>
  filter(PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID))
```

| Step | N |
|------|---|
| Raw | `r nrow(raw)` |
| After removing previews / non-finished | `r nrow(filter(raw, Status == 0 | is.na(Status), Finished == TRUE | Finished == 1))` |
| After removing test Prolific PIDs | `r nrow(d)` |

## Rename variables

```{r rename}
d <- d |>
  rename(
    share_direct      = matches("^Q1319"),
    share_social      = matches("^Q1320"),
    read_more_rel     = matches("^Q1321"),
    read_more_act     = matches("^Q1322"),
    read_more_con     = matches("^Q1325"),
    govtfund_general  = matches("^Q1108"),
    govtfund_cuts     = matches("^Q1301"),
    behavior_intent   = matches("^Q1124"),
    climate_1         = matches("^Q1142"),
    climate_2         = matches("^Q1188"),
    climate_3         = matches("^Q1114"),
    climate_4         = matches("^Q1189"),
    climate_5         = matches("^Q1115"),
    climate_6         = matches("^Q1190"),
    climate_7         = matches("^Q1298"),
    climate_8         = matches("^Q1300")
  )
```

## Coalesce condition-specific items

The "want to read more" slider lives in three separate question IDs depending on condition (QID1321/1322/1325). These are coalesced into a single `read_more` column.

```{r coalesce}
d <- d |>
  mutate(
    read_more = coalesce(
      as.numeric(read_more_rel),
      as.numeric(read_more_act),
      as.numeric(read_more_con)
    )
  ) |>
  select(-read_more_rel, -read_more_act, -read_more_con)
```

## Condition factor

```{r condition}
d <- d |>
  filter(condition %in% CONDITION_LEVELS) |>
  mutate(condition = factor(condition, levels = CONDITION_LEVELS))
```

```{r condition-table}
d |>
  count(condition) |>
  kable(col.names = c("Condition", "N"))
```

## Numeric coercion and climate composite

```{r numeric}
outcome_vars <- c(
  "share_direct", "share_social", "read_more",
  "govtfund_general", "govtfund_cuts", "behavior_intent",
  "climate_1", "climate_2", "climate_3", "climate_4",
  "climate_5", "climate_6", "climate_7", "climate_8"
)

d <- d |>
  mutate(across(all_of(outcome_vars), as.numeric)) |>
  mutate(
    climate_composite = rowMeans(pick(climate_1:climate_8), na.rm = TRUE)
  )
```

::: callout-note
Confirm item directions before using `climate_composite`. Reverse-score any negatively-worded items before this step.
:::

## Missing data

```{r missing}
d |>
  summarise(across(all_of(c(outcome_vars, "climate_composite")), ~sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N missing") |>
  kable()
```

## Save

```{r save}
saveRDS(d, CLEANED_RDS)
```

Cleaned data saved to `r CLEANED_RDS`. **Final N = `r nrow(d)`**.
