---
title: "Step 2 — Exploratory Data Analysis"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, reactable, scales, RColorBrewer, here)
```

```{r aesthetics}
plot_aes <- theme_minimal() +
  theme(
    legend.position    = "bottom",
    legend.text        = element_text(size = 9),
    text               = element_text(size = 12),
    axis.text          = element_text(color = "black"),
    axis.ticks.y       = element_blank(),
    panel.grid.major.y = element_blank()
  )

palette_main     <- "#197278"
condition_colors <- c(
  origcontrol1  = "#444444",
  origcontrol2  = "#888888",
  claudecontrol = "#BBBBBB",
  relevance     = "#011F5B",
  action        = "#990000"
)
```

```{r scale-levels}
lvl_agree7 <- c("Strongly disagree", "Disagree", "Somewhat disagree",
                "Neither agree nor disagree",
                "Somewhat agree", "Agree", "Strongly agree")

# Actual Qualtrics labels: Strongly / Moderately / Slightly (not Somewhat / generic)
lvl_approve7 <- c("Strongly disapprove", "Moderately disapprove", "Slightly disapprove",
                  "Neither approve nor disapprove",
                  "Slightly approve", "Moderately approve", "Strongly approve")

lvl_intent7 <- c("Definitely will not", "Probably will not", "Maybe will not",
                 "Unsure", "Maybe will", "Probably will", "Definitely will")

lvl_ideology <- c("Extremely liberal", "Liberal", "Slightly liberal",
                  "Moderate / middle of the road",
                  "Slightly conservative", "Conservative", "Extremely conservative")

# Code 1 = No formal education (never selected in this sample but needed for correct indexing)
lvl_degree <- c("No formal education",
                "Did not complete high school",
                "High school graduate (diploma)", "High school graduate (GED)",
                "Some college (1–4 years, no degree)",
                "Associate's degree (including occupational or academic degrees)",
                "Bachelor's degree (BA, BS, etc.)",
                "Master's degree (MA, MS, MEng, MSW, etc.)",
                "Professional school degree (MD, DDC, JD, etc.)",
                "Doctoral degree (PhD, EdD, etc.)")

lvl_income <- c("Less than $5,000", "$5,000 through $11,999", "$12,000 through $15,999",
                "$16,000 through $24,999", "$25,000 through $34,999", "$35,000 through $49,999",
                "$50,000 through $74,999", "$75,000 through $99,999",
                "$100,000 through $149,999", "$150,000 or greater",
                "Prefer not to say")

# Actual Qualtrics labels (verified): 1=Man, 2=Woman, 3=Prefer not to say,
# 4=Non-binary, 5=Genderqueer, 6=Agender, 7=Gender fluid, 8=I prefer to self-describe
lvl_gender <- c("Man", "Woman", "Prefer not to say",
                "Non-binary", "Genderqueer", "Agender",
                "Gender fluid", "I prefer to self-describe")

# Codes are 1=Yes, 4=Prefer not to say, 5=No — non-consecutive, use named recode
lgbtq_recode <- c(`1` = "Yes, I identify as LGBTQ+",
                  `4` = "Prefer not to say",
                  `5` = "No, I do not identify as LGBTQ+")

lvl_race <- c("White / Caucasian", "Black / African American",
              "Hispanic / Latino", "Asian / Asian American",
              "Native American / Alaska Native", "Pacific Islander",
              "Middle Eastern / North African", "Multiracial", "Other")

lvl_univ_aff <- c("I am currently enrolled as a student",
                  "I am currently employed (faculty, staff, or administration)",
                  "I was previously enrolled as a student",
                  "I was previously employed",
                  "A family member currently attends or works at a university",
                  "None of the above")
```

```{r helpers}
source(here("Step2", "analysis", "config.R"))
d <- readRDS(CLEANED_RDS)

# Derive MacArthur ladder rung from On/Off indicator columns
ses_cols <- paste0("ses_subjective_", 1:10)
d <- d |> mutate(
  ses_ladder = apply(d[, ses_cols], 1, function(r) {
    on <- which(r == "On"); if (length(on) == 0) NA_integer_ else as.integer(on[1])
  })
)

outcome_vars <- c(
  "share_narrow", "share_broad", "read_more",
  "article_self_relev", "article_social_relev",
  "govtfund_general", "govtfund_cuts",
  "talk_intent", "share_intent", "reps_intent",
  "climate_3_1", "climate_3_2", "climate_3_3"
)

outcome_labels <- c(
  share_narrow         = "Share directly (narrow)",
  share_broad          = "Share on social media (broad)",
  read_more            = "Want to read more",
  article_self_relev   = "Self-relevance",
  article_social_relev = "Social relevance",
  govtfund_general     = "Govt funding (general)",
  govtfund_cuts        = "Approval of funding cuts",
  talk_intent          = "Talk to others about cuts",
  share_intent         = "Share info online about cuts",
  reps_intent          = "Contact reps to support funding",
  climate_3_1          = "Climate attitude (3a)",
  climate_3_2          = "Climate attitude (3b)",
  climate_3_3          = "Climate attitude (3c)"
)

covariate_vars <- c("climate_warming", "climate_cause")
covariate_labels <- c(
  climate_warming = "Global warming happening? (1=Yes, 2=No, 3=Don't know)",
  climate_cause   = "Cause of warming (1=Human, 2=Natural, 3=Equal, 4=Other)"
)

# Pre-compute condition means for all outcomes
means_df <- map_dfr(outcome_vars, function(var) {
  lbl <- outcome_labels[[var]]
  d |>
    group_by(condition) |>
    summarise(M  = mean(.data[[var]], na.rm = TRUE),
              SD = sd(.data[[var]],  na.rm = TRUE),
              n  = sum(!is.na(.data[[var]])),
              .groups = "drop") |>
    mutate(SE = SD / sqrt(n), var = var, label = lbl)
})

# Apply numeric→label mapping for display
recode_num <- function(x, levels) {
  factor(levels[as.integer(x)], levels = levels)
}

# Frequency table (reactable)
freq_tab <- function(data, col, levels = NULL) {
  df <- data |>
    filter(!is.na(.data[[col]]), .data[[col]] != "") |>
    count(Response = .data[[col]], name = "n") |>
    mutate(Pct = round(100 * n / sum(n), 1))
  if (!is.null(levels)) {
    present <- intersect(levels, as.character(df$Response))
    df <- df |> mutate(Response = factor(Response, levels = present)) |> arrange(Response)
  } else {
    df <- df |> arrange(desc(n))
  }
  df |> reactable(striped = TRUE, compact = TRUE, defaultPageSize = 15)
}

# Bar chart: single variable, overall
bar_single <- function(data, col, title = "", levels = NULL, fill = palette_main) {
  df <- data |>
    filter(!is.na(.data[[col]]), .data[[col]] != "") |>
    count(response = .data[[col]])
  if (!is.null(levels)) {
    present <- intersect(levels, as.character(df$response))
    df <- df |> mutate(response = factor(response, levels = present))
  } else {
    df <- df |> mutate(response = fct_reorder(response, n))
  }
  ggplot(df, aes(x = response, y = n)) +
    geom_col(fill = fill) +
    geom_text(aes(label = n), hjust = -0.2, size = 3.5) +
    coord_flip() +
    expand_limits(y = max(df$n) * 1.15) +
    labs(x = "", y = "Count", title = title) +
    plot_aes
}

# Bar chart: Likert variable, faceted by condition
bar_by_condition <- function(data, col, title = "", levels = NULL) {
  df <- data |>
    filter(!is.na(.data[[col]]), !is.na(condition)) |>
    count(condition, response = .data[[col]])
  if (!is.null(levels)) {
    present <- intersect(levels, as.character(df$response))
    df <- df |> mutate(response = factor(response, levels = present))
  }
  ggplot(df, aes(x = response, y = n, fill = condition)) +
    geom_col(show.legend = FALSE) +
    facet_wrap(~condition, ncol = 5) +
    scale_fill_manual(values = condition_colors) +
    coord_flip() +
    labs(x = "", y = "Count", title = title) +
    plot_aes
}

# Histogram: 0–100 slider, faceted by condition
hist_slider <- function(data, col, title = "") {
  df <- data |> filter(!is.na(.data[[col]]), !is.na(condition))
  ggplot(df, aes(x = .data[[col]], fill = condition)) +
    geom_histogram(bins = 20, alpha = 0.9) +
    facet_wrap(~condition, ncol = 5) +
    scale_fill_manual(values = condition_colors, drop = FALSE) +
    labs(title = title, x = NULL, y = "Count") +
    theme_minimal(base_size = 11) +
    theme(legend.position = "none")
}

# Means ± SE plot for a subset of outcomes
means_plot <- function(vars, height = 4) {
  df <- means_df |>
    filter(var %in% vars) |>
    filter(!is.na(M), is.finite(M)) |>
    mutate(label = factor(label, levels = outcome_labels[vars]))
  ggplot(df, aes(x = condition, y = M, fill = condition)) +
    geom_col(width = 0.6, alpha = 0.9) +
    geom_errorbar(aes(ymin = M - SE, ymax = M + SE), width = 0.2) +
    facet_wrap(~label, scales = "free_y", ncol = min(3, length(vars))) +
    scale_fill_manual(values = condition_colors) +
    labs(x = NULL, y = "Mean (±1 SE)") +
    theme_minimal(base_size = 10) +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 20, hjust = 1))
}

# Means table for a subset of outcomes
means_table <- function(vars) {
  means_df |>
    filter(var %in% vars) |>
    mutate(M = round(M, 2), SD = round(SD, 2)) |>
    select(Outcome = label, Condition = condition, M, SD, n) |>
    arrange(Outcome, Condition) |>
    reactable(striped = TRUE, compact = TRUE, groupBy = "Outcome",
              defaultPageSize = length(vars) * 3)
}

# Stacked proportional bar: matrix question
bar_matrix <- function(data, cols, item_labels, title = "", scale_levels = NULL,
                       pal = "RdYlGn", pal_dir = 1, legend_rows = 2) {
  df <- data |>
    select(all_of(cols)) |>
    rename_with(~ item_labels) |>
    pivot_longer(everything(), names_to = "item", values_to = "response") |>
    filter(!is.na(response), response != "")
  if (!is.null(scale_levels)) {
    present <- intersect(scale_levels, as.character(unique(df$response)))
    df <- df |> mutate(response = factor(response, levels = present))
  }
  df |>
    count(item, response) |>
    group_by(item) |>
    mutate(pct  = n / sum(n),
           item = factor(item, levels = rev(item_labels))) |>
    ggplot(aes(x = item, y = pct, fill = response)) +
    geom_col(position = "fill", width = 0.7) +
    coord_flip() +
    scale_y_continuous(labels = percent_format(accuracy = 1)) +
    scale_fill_brewer(palette = pal, direction = pal_dir) +
    labs(x = "", y = "Proportion", fill = "", title = title) +
    plot_aes +
    guides(fill = guide_legend(reverse = TRUE, nrow = legend_rows))
}

# Frequency table: matrix question
freq_matrix <- function(data, cols, item_labels, scale_levels = NULL) {
  df <- data |>
    select(all_of(cols)) |>
    rename_with(~ item_labels) |>
    pivot_longer(everything(), names_to = "Item", values_to = "Response") |>
    filter(!is.na(Response), Response != "") |>
    count(Item, Response) |>
    group_by(Item) |>
    mutate(Pct = round(100 * n / sum(n), 1))
  if (!is.null(scale_levels)) {
    present <- intersect(scale_levels, as.character(unique(df$Response)))
    df <- df |> mutate(Response = factor(Response, levels = present)) |>
      arrange(Item, Response)
  }
  df |>
    reactable(groupBy = "Item", striped = TRUE, compact = TRUE, filterable = TRUE,
              defaultPageSize = 20,
              columns = list(Item = colDef(minWidth = 250)))
}

# Multi-select: count per indicator column
bar_multiselect <- function(data, cols, item_labels, title = "", fill = palette_main) {
  df <- tibble(
    item = item_labels,
    n    = sapply(cols, function(c) sum(data[[c]] == 1, na.rm = TRUE))
  ) |> mutate(item = fct_reorder(item, n))
  ggplot(df, aes(x = item, y = n)) +
    geom_col(fill = fill) +
    geom_text(aes(label = n), hjust = -0.2, size = 3.5) +
    coord_flip() +
    expand_limits(y = max(df$n) * 1.15) +
    labs(x = "", y = "Count", title = title) +
    plot_aes
}
```

**N = `r nrow(d)`** (Cohort 1, 2026-06-04; exclusions applied — see `00_clean.html`).

Condition counts: `r paste(paste0(levels(d$condition), " (", table(d$condition), ")"), collapse = " | ")`.

---

# 1. Article Ratings {.tabset}

## Sharing {.unnumbered}

**share_direct**: Would you share this article directly with someone you know?

```{r share-direct}
hist_slider(d, "share_narrow", "Share directly / narrow (0–100)")
```

**share_social**: Would you share this article by posting on social media?

```{r share-social}
hist_slider(d, "share_broad", "Share on social media / broad (0–100)")
```

**read_more**: How much would you want to read more articles like this one?

```{r read-more}
hist_slider(d, "read_more", "Want to read more (0–100)")
```

## Relevance {.unnumbered}

**article_self_relev** / **article_social_relev**: "Rate your agreement with the following statements."

```{r relevance}
d_rel <- d |> mutate(
  article_self_relev   = recode_num(article_self_relev,   lvl_agree7),
  article_social_relev = recode_num(article_social_relev, lvl_agree7)
)
bar_by_condition(d_rel, "article_self_relev",
                 "This article is relevant to me", levels = lvl_agree7)
freq_tab(d_rel, "article_self_relev", levels = lvl_agree7)

bar_by_condition(d_rel, "article_social_relev",
                 "This article is relevant to people I know", levels = lvl_agree7)
freq_tab(d_rel, "article_social_relev", levels = lvl_agree7)
```

## Means by condition {.unnumbered}

```{r article-means, fig.height = 5}
means_plot(c("share_narrow", "share_broad", "read_more",
             "article_self_relev", "article_social_relev"))
means_table(c("share_narrow", "share_broad", "read_more",
              "article_self_relev", "article_social_relev"))
```

---

# 2. Government Funding {.tabset}

## General Attitude {.unnumbered}

**govtfund_general**: Do you approve or disapprove of the federal government using taxpayer funds to invest in research at colleges and universities?

```{r gf-general}
d_gf <- d |> mutate(govtfund_general = recode_num(govtfund_general, lvl_approve7))
bar_by_condition(d_gf, "govtfund_general",
                 "Approval of federal research funding", levels = lvl_approve7)
freq_tab(d_gf, "govtfund_general", levels = lvl_approve7)
```

## Attitude Toward Cuts {.unnumbered}

**govtfund_cuts**: Do you disapprove or approve of cuts to funding for scientific research? (1 = Strongly disapprove, 7 = Strongly approve)

```{r gf-cuts}
d_gf2 <- d |> mutate(govtfund_cuts = recode_num(govtfund_cuts, lvl_approve7))
bar_by_condition(d_gf2, "govtfund_cuts",
                 "Approval of funding cuts", levels = lvl_approve7)
freq_tab(d_gf2, "govtfund_cuts", levels = lvl_approve7)
```

## Means by condition {.unnumbered}

```{r gf-means, fig.height = 4}
means_plot(c("govtfund_general", "govtfund_cuts"))
means_table(c("govtfund_general", "govtfund_cuts"))
```

---

# 3. Behavioral Intentions {.tabset}

## Intent to Act {.unnumbered}

How likely are you to do each of the following in the next 3 months?

```{r behavioral-intent, fig.height = 4}
d_bi <- d |> mutate(
  talk_intent  = recode_num(talk_intent,  lvl_intent7),
  share_intent = recode_num(share_intent, lvl_intent7),
  reps_intent  = recode_num(reps_intent,  lvl_intent7)
)
bi_cols   <- c("talk_intent", "share_intent", "reps_intent")
bi_labels <- c("Talk to others about cuts",
               "Share info online about cuts",
               "Contact reps to support funding")

bar_matrix(d_bi, bi_cols, bi_labels,
           title        = "Behavioral intentions",
           scale_levels = lvl_intent7,
           pal = "Blues", pal_dir = 1, legend_rows = 2)
freq_matrix(d_bi, bi_cols, bi_labels, scale_levels = lvl_intent7)
```

## Means by condition {.unnumbered}

```{r bi-means, fig.height = 4}
means_plot(c("talk_intent", "share_intent", "reps_intent"))
means_table(c("talk_intent", "share_intent", "reps_intent"))
```

---

# 4. Climate Attitudes {.tabset}

## Climate Attitudes (climate_3) {.unnumbered}

```{r climate3, fig.height = 4}
d_cl <- d |> mutate(
  climate_3_1 = recode_num(climate_3_1, lvl_agree7),
  climate_3_2 = recode_num(climate_3_2, lvl_agree7),
  climate_3_3 = recode_num(climate_3_3, lvl_agree7)
)
cl_cols   <- c("climate_3_1", "climate_3_2", "climate_3_3")
cl_labels <- c("Climate attitude (3a)", "Climate attitude (3b)", "Climate attitude (3c)")

bar_matrix(d_cl, cl_cols, cl_labels,
           title        = "Climate attitudes",
           scale_levels = lvl_agree7,
           pal = "RdYlBu", pal_dir = 1, legend_rows = 2)
freq_matrix(d_cl, cl_cols, cl_labels, scale_levels = lvl_agree7)
```

## Means by condition {.unnumbered}

```{r cl-means, fig.height = 4}
means_plot(c("climate_3_1", "climate_3_2", "climate_3_3"))
means_table(c("climate_3_1", "climate_3_2", "climate_3_3"))
```

---

# 5. Climate Belief Covariates {.tabset}

`climate_warming` and `climate_cause` are categorical pre-attitude items, not comparable to the 7-point outcome scales.

## Global Warming Happening {.unnumbered}

**climate_warming**: Do you think global warming is happening?

```{r clim1}
# Verified: code 1=No, 2=Yes, 3=Don't know
lvl_gw <- c("No", "Yes", "Don't know")
d_cov  <- d |> mutate(climate_warming = recode_num(climate_warming, lvl_gw))
bar_single(d_cov, "climate_warming",
           title = "Do you think global warming is happening?", levels = rev(lvl_gw))
freq_tab(d_cov, "climate_warming", levels = rev(lvl_gw))
```

## Cause of Warming {.unnumbered}

**climate_cause**: Assuming global warming is happening, do you think it is...

```{r clim2}
# Verified: 1=Caused mostly by humans, 2=Mostly natural, 3=None of the above (GW not happening), 4=Other
lvl_cause <- c("Caused mostly by humans",
               "Caused mostly by natural changes in the environment",
               "None of the above, because global warming isn't happening",
               "Other")
d_cov2 <- d |> mutate(climate_cause = recode_num(climate_cause, lvl_cause))
bar_single(d_cov2, "climate_cause", title = "Cause of global warming", levels = lvl_cause)
freq_tab(d_cov2, "climate_cause", levels = lvl_cause)
```

---

# 6. Outcome Correlations

```{r correlations, fig.height = 8, fig.width = 9}
cor_mat <- d |>
  select(all_of(outcome_vars)) |>
  cor(use = "pairwise.complete.obs") |>
  round(2)

cor_df <- as.data.frame(cor_mat) |>
  rownames_to_column("var1") |>
  pivot_longer(-var1, names_to = "var2", values_to = "r") |>
  mutate(
    var1 = factor(var1, levels = outcome_vars, labels = outcome_labels[outcome_vars]),
    var2 = factor(var2, levels = outcome_vars, labels = outcome_labels[outcome_vars])
  )

ggplot(cor_df, aes(x = var1, y = var2, fill = r)) +
  geom_tile() +
  geom_text(aes(label = r), size = 2.5) +
  scale_fill_gradient2(low = "#990000", mid = "white", high = "#011F5B",
                       midpoint = 0, limits = c(-1, 1)) +
  labs(x = NULL, y = NULL, fill = "r") +
  theme_minimal(base_size = 9) +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

---

# 7. Demographics {.tabset}

## Age {.unnumbered}

```{r demo-age}
d |>
  mutate(Age = as.numeric(Age)) |>
  summarise(M   = round(mean(Age, na.rm = TRUE), 1),
            SD  = round(sd(Age,   na.rm = TRUE), 1),
            Min = min(Age, na.rm = TRUE),
            Max = max(Age, na.rm = TRUE)) |>
  reactable(compact = TRUE)

d |>
  mutate(Age = as.numeric(Age)) |>
  filter(!is.na(Age)) |>
  ggplot(aes(x = Age)) +
  geom_histogram(binwidth = 5, fill = palette_main, color = "white") +
  labs(x = "Age", y = "Count", title = "Age distribution") +
  plot_aes
```

## Gender {.unnumbered}

```{r demo-gender}
d_gend <- d |> mutate(gender_label = recode_num(gender, lvl_gender))
bar_single(d_gend, "gender_label", title = "Gender identity", levels = lvl_gender)
freq_tab(d_gend, "gender_label", levels = lvl_gender)
```

## Sex (Prolific) {.unnumbered}

```{r demo-sex}
bar_single(d, "Sex", title = "Sex (Prolific-provided)")
freq_tab(d, "Sex")
```

## Race / Ethnicity {.unnumbered}

```{r demo-race, fig.height = 5}
race_cols <- paste0("race_", 1:9)
bar_multiselect(d, race_cols, lvl_race,
                title = "Race / ethnicity (select all that apply)")

d |>
  mutate(race_self_resp = na_if(race_self, "")) |>
  filter(!is.na(race_self_resp)) |>
  count(race_self_resp, sort = TRUE) |>
  reactable(striped = TRUE, compact = TRUE,
            columns = list(race_self_resp = colDef(name = "Self-description")))
```

## Ethnicity (Prolific) {.unnumbered}

```{r demo-ethnicity}
bar_single(d, "Ethnicity simplified", title = "Ethnicity (Prolific-provided)")
freq_tab(d, "Ethnicity simplified")
```

## LGBTQ+ {.unnumbered}

```{r demo-lgbtq}
lvl_lgbtq <- c("Yes, I identify as LGBTQ+", "Prefer not to say",
               "No, I do not identify as LGBTQ+")
d_lgbtq <- d |> mutate(lgbtq_label = recode(as.character(LGBTQ), !!!lgbtq_recode))
bar_single(d_lgbtq, "lgbtq_label", title = "LGBTQ+ identity", levels = lvl_lgbtq)
freq_tab(d_lgbtq, "lgbtq_label", levels = lvl_lgbtq)
```

## Education {.unnumbered}

```{r demo-edu}
d_edu <- d |> mutate(ses_degree_label = recode_num(ses_degree, lvl_degree))
bar_single(d_edu, "ses_degree_label",
           title = "Highest education level", levels = lvl_degree)
freq_tab(d_edu, "ses_degree_label", levels = lvl_degree)
```

## Income {.unnumbered}

```{r demo-income}
d_inc <- d |> mutate(income_label = recode_num(ses_income_household, lvl_income))
bar_single(d_inc, "income_label", title = "Household income", levels = lvl_income)
freq_tab(d_inc, "income_label", levels = lvl_income)
```

## Subjective SES {.unnumbered}

MacArthur ladder (1 = bottom, 10 = top): relative standing in the US by money, education, and job prestige.

```{r demo-ses}
d |>
  filter(!is.na(ses_ladder)) |>
  summarise(M = round(mean(ses_ladder), 1), SD = round(sd(ses_ladder), 1),
            Min = min(ses_ladder), Max = max(ses_ladder)) |>
  reactable(compact = TRUE)

d |>
  filter(!is.na(ses_ladder)) |>
  ggplot(aes(x = factor(ses_ladder))) +
  geom_bar(fill = palette_main) +
  labs(x = "Ladder rung", y = "Count",
       title = "Subjective SES (MacArthur ladder)") +
  plot_aes
```

## Political Ideology {.unnumbered}

```{r demo-ideology}
d_pol <- d |> mutate(ideology_label = recode_num(politics_ideology, lvl_ideology))
bar_single(d_pol, "ideology_label",
           title = "Political ideology", levels = lvl_ideology)
freq_tab(d_pol, "ideology_label", levels = lvl_ideology)
```

## University Affiliation {.unnumbered}

```{r demo-affil, fig.height = 5}
aff_cols <- paste0("univ_affiliate_", 1:6)
bar_multiselect(d, aff_cols, lvl_univ_aff,
                title = "University affiliation (select all that apply)")
```

## Student & Employment Status {.unnumbered}

```{r demo-student}
bar_single(d, "Student status", title = "Student status (Prolific-provided)")
freq_tab(d, "Student status")
```

```{r demo-employment, fig.height = 4}
bar_single(d, "Employment status", title = "Employment status (Prolific-provided)")
freq_tab(d, "Employment status")
```
