---
title: "Step 2 — Analysis"
subtitle: "Action and Relevance conditions vs Control"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(broom)
library(effectsize)
library(here)
library(knitr)

source(here("Step2", "analysis", "config.R"))

d <- readRDS(CLEANED_RDS)

outcomes <- c(
  share_direct      = "Share directly",
  share_social      = "Share on social media",
  read_more         = "Want to read more",
  article_agree_1   = "Article agreement (1)",
  article_agree_2   = "Article agreement (2)",
  govtfund_general  = "Govt funding (general)",
  govtfund_cuts     = "Disapprove of funding cuts",
  behavior_intent_1 = "Behavioral intention (1)",
  behavior_intent_2 = "Behavioral intention (2)",
  behavior_intent_3 = "Behavioral intention (3)",
  climate_1         = "Climate belief (1)",
  climate_2         = "Climate belief (2)",
  climate_3_1       = "Climate belief (3a)",
  climate_3_2       = "Climate belief (3b)",
  climate_3_3       = "Climate belief (3c)"
)

condition_colors <- c(control = "#888888", relevance = "#011F5B", action = "#990000")
```

## Design

Between-subjects, 3 conditions. Reference level: **control**. For each outcome, a separate linear model estimates:

- **Relevance vs Control** (`conditionrelevance`)
- **Action vs Control** (`conditionaction`)

**N = `r nrow(d)`** (`r paste(paste0(levels(d$condition), ": ", table(d$condition)), collapse = " | ")`)

## Models

```{r models}
models <- map(names(outcomes), function(var) {
  tryCatch(
    lm(as.formula(paste(var, "~ condition")), data = d |> filter(!is.na(.data[[var]]))),
    error = function(e) NULL
  )
}) |>
  set_names(names(outcomes))

skipped <- names(Filter(is.null, models))
if (length(skipped) > 0) {
  cat("Skipped (insufficient data):", paste(skipped, collapse = ", "), "\n")
}
models <- Filter(Negate(is.null), models)
```

## Contrasts vs Control

```{r contrasts}
results <- map_dfr(names(models), function(var) {
  tidy(models[[var]], conf.int = TRUE) |>
    filter(term %in% c("conditionrelevance", "conditionaction")) |>
    mutate(
      outcome  = outcomes[[var]],
      contrast = str_remove(term, "^condition")
    )
}) |>
  select(outcome, contrast, estimate, std.error, statistic, p.value, conf.low, conf.high) |>
  mutate(
    across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
    statistic = round(statistic, 2),
    p.value   = round(p.value, 3),
    sig       = case_when(
      p.value < .001 ~ "***",
      p.value < .01  ~ "**",
      p.value < .05  ~ "*",
      p.value < .10  ~ "†",
      TRUE           ~ ""
    )
  )

results |>
  select(Outcome = outcome, Contrast = contrast,
         B = estimate, SE = std.error,
         t = statistic, p = p.value, sig,
         `95% CI low` = conf.low, `95% CI high` = conf.high) |>
  kable()
```

## Effect sizes (Cohen's *d*)

```{r cohens-d}
cohens_d_results <- map_dfr(names(models), function(var) {
  bind_rows(
    cohens_d(as.formula(paste(var, "~ condition")),
             data = d |> filter(condition %in% c("control", "relevance"))) |>
      as.data.frame() |> mutate(outcome = outcomes[[var]], contrast = "relevance"),
    cohens_d(as.formula(paste(var, "~ condition")),
             data = d |> filter(condition %in% c("control", "action"))) |>
      as.data.frame() |> mutate(outcome = outcomes[[var]], contrast = "action")
  )
}) |>
  select(outcome, contrast, d = Cohens_d, ci_low = CI_low, ci_high = CI_high) |>
  mutate(across(where(is.numeric), ~round(., 3)))

cohens_d_results |>
  kable(col.names = c("Outcome", "Contrast", "Cohen's d", "95% CI low", "95% CI high"))
```

## Omnibus F-tests

```{r omnibus}
map_dfr(names(models), function(var) {
  glance(models[[var]]) |>
    mutate(outcome = outcomes[[var]])
}) |>
  select(Outcome = outcome,
         `R²` = r.squared, `adj. R²` = adj.r.squared,
         F = statistic, p = p.value,
         df, `df resid.` = df.residual) |>
  mutate(across(where(is.numeric), ~round(., 3))) |>
  kable()
```

## Summary table

```{r summary-table}
results |>
  left_join(
    cohens_d_results |>
      rename(`Cohen's d` = d, `d CI low` = ci_low, `d CI high` = ci_high),
    by = c("outcome", "contrast")
  ) |>
  select(Outcome = outcome, Contrast = contrast,
         B = estimate, p = p.value, sig,
         `Cohen's d`, `d CI low`, `d CI high`) |>
  kable()
```

## Coefficient plot

```{r coef-plot, fig.height=8, fig.width=9}
results |>
  mutate(
    outcome  = factor(outcome, levels = rev(unname(outcomes))),
    contrast = factor(contrast, levels = c("relevance", "action"))
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.5), size = 0.5) +
  scale_color_manual(values = c(relevance = "#011F5B", action = "#990000"),
                     labels = c(relevance = "Relevance vs Control",
                                action    = "Action vs Control")) +
  labs(x = "Coefficient (B)", y = NULL, color = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

## Save results

```{r save}
results_out <- list(
  models    = models,
  contrasts = results,
  cohens_d  = cohens_d_results,
  omnibus   = map_dfr(names(models), ~glance(models[[.x]]) |> mutate(outcome = .x))
)

saveRDS(results_out, RESULTS_RDS)
```

Results saved to `r RESULTS_RDS`.

---

# Secondary analyses: variant-level

Within the relevance and action conditions, participants were randomly assigned to one of three headline/lede variants. These analyses ask:

1. Does each of the 6 variants differ from control?
2. Do the 3 relevance variants differ from each other?
3. Do the 3 action variants differ from each other?

```{r variant-setup}
library(emmeans)

variant_levels <- c("control",
                    "relevance1", "relevance2", "relevance3",
                    "action1",    "action2",    "action3")

d <- d |>
  mutate(variant_condition = factor(variant_seen, levels = variant_levels))

cat("Variant counts:\n")
print(table(d$variant_condition, useNA = "ifany"))
```

## Variant-level models

One model per outcome, 7-level factor with control as reference. Coefficients are each variant vs control.

```{r variant-models}
variant_models <- map(names(outcomes), function(var) {
  tryCatch(
    lm(as.formula(paste(var, "~ variant_condition")),
       data = d |> filter(!is.na(.data[[var]]), !is.na(variant_condition))),
    error = function(e) NULL
  )
}) |>
  set_names(names(outcomes)) |>
  Filter(Negate(is.null), x = _)
```

## Each variant vs Control

```{r variant-vs-control}
variant_vs_control <- map_dfr(names(variant_models), function(var) {
  tidy(variant_models[[var]], conf.int = TRUE) |>
    filter(str_detect(term, "^variant_condition")) |>
    mutate(
      outcome  = outcomes[[var]],
      variant  = str_remove(term, "^variant_condition"),
      condition = str_extract(variant, "^[a-z]+")
    )
}) |>
  mutate(
    across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
    statistic = round(statistic, 2),
    p.value   = round(p.value, 3),
    sig = case_when(
      p.value < .001 ~ "***", p.value < .01 ~ "**",
      p.value < .05  ~ "*",   p.value < .10 ~ "†",
      TRUE ~ ""
    )
  )

variant_vs_control |>
  select(Outcome = outcome, Variant = variant,
         B = estimate, SE = std.error,
         t = statistic, p = p.value, sig,
         `95% CI low` = conf.low, `95% CI high` = conf.high) |>
  arrange(Outcome, Variant) |>
  kable()
```

## Variant vs Control coefficient plot

```{r variant-coef-plot, fig.height=9, fig.width=10}
variant_colors <- c(
  relevance1 = "#011F5B", relevance2 = "#3A5FA0", relevance3 = "#7B9FD4",
  action1    = "#990000", action2    = "#CC3333", action3    = "#FF7777"
)

variant_vs_control |>
  filter(is.finite(estimate)) |>
  mutate(
    outcome = factor(outcome, levels = rev(unname(outcomes))),
    variant = factor(variant, levels = rev(variant_levels[-1]))
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = variant,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.7), size = 0.4) +
  scale_color_manual(values = variant_colors) +
  labs(x = "Coefficient vs Control (B)", y = NULL, color = "Variant") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "right")
```

## Within-condition pairwise comparisons

```{r within-pairs}
pairwise_within <- function(model, group_variants) {
  tryCatch({
    em  <- emmeans(model, ~variant_condition)
    obs <- as.character(summary(em)$variant_condition)
    inc <- intersect(group_variants, obs)
    if (length(inc) < 2) return(NULL)
    contrast(em, method = "pairwise", include = inc) |>
      summary() |>
      as.data.frame()
  }, error = function(e) NULL)
}

within_pairs <- map_dfr(names(variant_models), function(var) {
  bind_rows(
    pairwise_within(variant_models[[var]], c("relevance1","relevance2","relevance3")) |>
      (\(x) if (!is.null(x)) mutate(x, outcome = outcomes[[var]], group = "relevance") else NULL)(),
    pairwise_within(variant_models[[var]], c("action1","action2","action3")) |>
      (\(x) if (!is.null(x)) mutate(x, outcome = outcomes[[var]], group = "action") else NULL)()
  )
})

if (nrow(within_pairs) > 0) {
  # emmeans uses 't.ratio' in older versions and 'statistic' or 't.ratio' in newer ones
  t_col <- intersect(c("t.ratio", "statistic"), names(within_pairs))[1]

  within_pairs |>
    mutate(
      across(where(is.numeric), ~round(., 3)),
      sig = case_when(
        p.value < .001 ~ "***", p.value < .01  ~ "**",
        p.value < .05  ~ "*",   p.value < .10  ~ "†",
        TRUE ~ ""
      )
    ) |>
    select(Outcome = outcome, Group = group, Contrast = contrast,
           Estimate = estimate, SE = SE,
           t = all_of(t_col), p = p.value, sig) |>
    arrange(Outcome, Group, Contrast) |>
    kable()
} else {
  cat("Insufficient data for within-condition pairwise comparisons (expected with test data).\n")
}
```

## Save updated results

```{r save-secondary}
results_out$variant_models       <- variant_models
results_out$variant_vs_control   <- variant_vs_control
results_out$within_pairs         <- within_pairs

saveRDS(results_out, RESULTS_RDS)
```
