---
title: "Step 2 — Analysis"
subtitle: "Action and Relevance conditions vs Control"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(broom)
library(effectsize)
library(here)
library(knitr)

source(here("Step2", "analysis", "config.R"))

d <- readRDS(CLEANED_RDS)

outcomes <- c(
  share_direct      = "Share directly",
  share_social      = "Share on social media",
  read_more         = "Want to read more",
  govtfund_general  = "Govt funding attitude (general)",
  govtfund_cuts     = "Disapprove of funding cuts",
  behavior_intent   = "Behavioral intention",
  climate_composite = "Climate beliefs (composite)"
)

condition_colors <- c(control = "#888888", relevance = "#011F5B", action = "#990000")
```

## Design

Between-subjects, 3 conditions. Reference level: **control**. For each outcome, a separate linear model estimates the contrasts:

- **Relevance vs Control** (`conditionrelevance`)
- **Action vs Control** (`conditionaction`)

**N = `r nrow(d)`** (`r paste(paste0(levels(d$condition), ": ", table(d$condition)), collapse = " | ")`)

## Models

```{r models}
models <- map(names(outcomes), function(var) {
  lm(as.formula(paste(var, "~ condition")), data = d)
}) |>
  set_names(names(outcomes))
```

## Contrasts vs Control

```{r contrasts}
results <- map_dfr(names(outcomes), function(var) {
  tidy(models[[var]], conf.int = TRUE) |>
    filter(term %in% c("conditionrelevance", "conditionaction")) |>
    mutate(
      outcome  = outcomes[[var]],
      contrast = str_remove(term, "^condition")
    )
}) |>
  select(outcome, contrast, estimate, std.error, statistic, p.value, conf.low, conf.high) |>
  mutate(
    across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
    statistic = round(statistic, 2),
    p.value   = round(p.value, 3),
    sig       = case_when(
      p.value < .001 ~ "***",
      p.value < .01  ~ "**",
      p.value < .05  ~ "*",
      p.value < .10  ~ "†",
      TRUE           ~ ""
    )
  )

results |>
  select(Outcome = outcome, Contrast = contrast,
         B = estimate, SE = std.error,
         t = statistic, p = p.value, sig,
         `95% CI low` = conf.low, `95% CI high` = conf.high) |>
  kable()
```

## Effect sizes (Cohen's *d*)

```{r cohens-d}
cohens_d_results <- map_dfr(names(outcomes), function(var) {
  bind_rows(
    cohens_d(as.formula(paste(var, "~ condition")),
             data = d |> filter(condition %in% c("control", "relevance"))) |>
      as.data.frame() |> mutate(outcome = outcomes[[var]], contrast = "relevance"),
    cohens_d(as.formula(paste(var, "~ condition")),
             data = d |> filter(condition %in% c("control", "action"))) |>
      as.data.frame() |> mutate(outcome = outcomes[[var]], contrast = "action")
  )
}) |>
  select(outcome, contrast, d = Cohens_d, ci_low = CI_low, ci_high = CI_high) |>
  mutate(across(where(is.numeric), ~round(., 3)))

cohens_d_results |>
  kable(col.names = c("Outcome", "Contrast", "Cohen's d", "95% CI low", "95% CI high"))
```

## Omnibus F-tests

```{r omnibus}
map_dfr(names(outcomes), function(var) {
  glance(models[[var]]) |>
    mutate(outcome = outcomes[[var]])
}) |>
  select(Outcome = outcome,
         `R²` = r.squared, `adj. R²` = adj.r.squared,
         F = statistic, p = p.value,
         df, `df resid.` = df.residual) |>
  mutate(across(where(is.numeric), ~round(., 3))) |>
  kable()
```

## Summary table

```{r summary-table}
results |>
  left_join(
    cohens_d_results |>
      rename(`Cohen's d` = d, `d CI low` = ci_low, `d CI high` = ci_high),
    by = c("outcome", "contrast")
  ) |>
  select(Outcome = outcome, Contrast = contrast,
         B = estimate, p = p.value, sig,
         `Cohen's d`, `d CI low`, `d CI high`) |>
  kable()
```

## Coefficient plot

```{r coef-plot, fig.height=6, fig.width=8}
results |>
  mutate(
    outcome  = factor(outcome, levels = rev(unname(outcomes))),
    contrast = factor(contrast, levels = c("relevance", "action"))
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.5), size = 0.6) +
  scale_color_manual(values = c(relevance = "#011F5B", action = "#990000"),
                     labels = c(relevance = "Relevance vs Control",
                                action    = "Action vs Control")) +
  labs(x = "Coefficient (B)", y = NULL, color = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

## Save results

```{r save}
results_out <- list(
  models   = models,
  contrasts = results,
  cohens_d  = cohens_d_results,
  omnibus   = map_dfr(names(outcomes), ~glance(models[[.x]]) |> mutate(outcome = .x))
)

saveRDS(results_out, RESULTS_RDS)
```

Results saved to `r RESULTS_RDS`.
