---
title: "Step 2 — Analysis"
subtitle: "Action and Relevance conditions vs Corrected Control (origcontrol1/2)"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 9, fig.height = 6)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, broom, effectsize, emmeans, reactable, here)
```

```{r load}
source(here("Step2", "analysis", "config.R"))
d <- readRDS(CLEANED_RDS)

outcomes <- c(
  share_narrow         = "Share directly (narrow)",
  share_broad          = "Share on social media (broad)",
  read_more            = "Want to read more",
  article_self_relev   = "Self-relevance",
  article_social_relev = "Social relevance",
  govtfund_general     = "Govt funding (general)",
  govtfund_cuts        = "Disapproval of funding cuts",
  talk_intent          = "Talk to others about cuts",
  share_intent         = "Share info online about cuts",
  reps_intent          = "Contact reps to support funding"
)

covariates <- c(
  climate_warming = "Global warming happening? (1–3)",
  climate_cause   = "Cause of warming (1–4)"
)

# Reverse-code funding cuts so higher = disapproval (consistent positive direction)
d <- d |> mutate(govtfund_cuts = 8 - govtfund_cuts)

# Z-score all outcomes so coefficients are in SD units and comparable across scales
d <- d |> mutate(across(all_of(names(outcomes)), ~as.numeric(scale(.))))

condition_colors <- c(
  origcontrol1  = "#444444",
  origcontrol2  = "#888888",
  claudecontrol = "#BBBBBB",
  relevance     = "#011F5B",
  action        = "#990000"
)
variant_colors <- c(
  origcontrol1 = "#444444", origcontrol2 = "#888888",
  claudecontrol = "#BBBBBB",
  relevance1 = "#011F5B", relevance2 = "#3A5FA0", relevance3 = "#7B9FD4",
  action1    = "#990000", action2    = "#CC3333", action3    = "#FF7777"
)

contrast_levels <- c("relevance", "action")
contrast_colors <- c(relevance = "#011F5B", action = "#990000")
contrast_labels <- c(relevance = "Relevance vs OrigControl1",
                     action    = "Action vs OrigControl1")

sig_stars <- function(p) case_when(
  p < .001 ~ "***", p < .01 ~ "**", p < .05 ~ "*", p < .10 ~ "†", TRUE ~ ""
)

# Moderators (centered continuous)
ses_cols <- paste0("ses_subjective_", 1:10)
d <- d |> mutate(
  Age = as.numeric(Age),
  ses_ladder = apply(d[, ses_cols], 1, function(r) {
    on <- which(r == "On"); if (length(on) == 0) NA_integer_ else as.integer(on[1])
  }),
  univ_affiliated = as.integer(
    rowSums(cbind(univ_affiliate_1, univ_affiliate_2, univ_affiliate_3,
                  univ_affiliate_4, univ_affiliate_5), na.rm = TRUE) > 0
  ),
  age_c       = scale(Age,               center = TRUE, scale = FALSE)[, 1],
  ideology_c  = scale(politics_ideology, center = TRUE, scale = FALSE)[, 1],
  climate1_c  = scale(climate_warming,   center = TRUE, scale = FALSE)[, 1],
  climate2_c  = scale(climate_cause,     center = TRUE, scale = FALSE)[, 1]
)

moderators <- c(
  age_c           = "Age",
  ideology_c      = "Political ideology",
  climate1_c      = "Climate belief (happening)",
  climate2_c      = "Climate belief (cause)",
  univ_affiliated = "Univ. affiliated"
)
```

**N = `r nrow(d)`** (`r paste(paste0(levels(d$condition), ": ", table(d$condition)), collapse = " | ")`)

Between-subjects, 5 conditions. Reference level: **origcontrol1**. Each outcome is modeled separately and z-scored prior to modeling. Primary contrasts: **relevance** and **action** vs origcontrol1. origcontrol2 and claudecontrol are retained in the data (and in the variant analysis) but excluded from the primary condition-effect tables and plots.

---

# 1. Primary analysis: condition effects {.tabset}

```{r models}
models <- map(names(outcomes), function(var) {
  tryCatch(
    lm(as.formula(paste(var, "~ condition")),
       data = d |> filter(!is.na(.data[[var]]))),
    error = function(e) NULL
  )
}) |> set_names(names(outcomes))

skipped <- names(Filter(is.null, models))
if (length(skipped) > 0)
  cat("Skipped (insufficient data):", paste(skipped, collapse = ", "), "\n")
models <- Filter(Negate(is.null), models)

primary_contrasts <- c("conditionrelevance", "conditionaction")

results <- map_dfr(names(models), function(var) {
  tidy(models[[var]], conf.int = TRUE) |>
    filter(term %in% primary_contrasts) |>
    mutate(outcome  = outcomes[[var]],
           contrast = str_remove(term, "^condition"))
}) |>
  select(outcome, contrast, estimate, std.error, statistic, p.value,
         conf.low, conf.high) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
         statistic = round(statistic, 2),
         p.value   = round(p.value,   3),
         sig       = sig_stars(p.value))

cohens_d_results <- map_dfr(names(models), function(var) {
  map_dfr(c("relevance", "action"), function(cond) {
    tryCatch(
      cohens_d(as.formula(paste(var, "~ condition")),
               data = d |> filter(condition %in% c("origcontrol1", cond))) |>
        as.data.frame() |> mutate(outcome = outcomes[[var]], contrast = cond),
      error = function(e) NULL
    )
  })
}) |>
  select(outcome, contrast, d = Cohens_d, ci_low = CI_low, ci_high = CI_high) |>
  mutate(across(where(is.numeric), ~round(., 3)))
```

## Summary {.unnumbered}

```{r summary-table}
results |>
  left_join(
    cohens_d_results |> rename(`Cohen's d` = d, `d CI low` = ci_low, `d CI high` = ci_high),
    by = c("outcome", "contrast")
  ) |>
  select(Outcome = outcome, Contrast = contrast,
         B = estimate, SE = std.error, t = statistic,
         p = p.value, sig, `Cohen's d`, `d CI low`, `d CI high`) |>
  arrange(Outcome, Contrast) |>
  reactable(
    striped = TRUE, compact = TRUE, filterable = TRUE,
    defaultPageSize = nrow(results),
    columns = list(
      sig       = colDef(name = ""),
      `d CI low`  = colDef(name = "d CI low"),
      `d CI high` = colDef(name = "d CI high")
    )
  )
```

## Coefficient plot {.unnumbered}

All coefficients are in SD units (outcomes z-scored prior to modeling).

```{r coef-plot, fig.height = 6}
coef_plot <- function(data, keep_outcomes, xlim, title) {
  data |>
    filter(outcome %in% keep_outcomes) |>
    mutate(
      outcome  = factor(outcome, levels = rev(keep_outcomes)),
      contrast = factor(contrast, levels = contrast_levels),
      y_dodge  = case_when(
        contrast == "relevance" ~ -0.15,
        contrast == "action"    ~  0.15
      )
    ) |>
    ggplot(aes(x = estimate, y = outcome, color = contrast,
               xmin = conf.low, xmax = conf.high)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
    geom_pointrange(position = position_dodge(width = 0.6), size = 0.5) +
    geom_text(aes(x = conf.high + 0.05,
                  y = as.numeric(outcome) + y_dodge,
                  label = sig),
              hjust = 0, vjust = 0.5, size = 4, color = "black",
              show.legend = FALSE) +
    scale_color_manual(values = contrast_colors, labels = contrast_labels) +
    coord_cartesian(xlim = xlim, clip = "off") +
    labs(x = "Standardized coefficient (SD units)", y = NULL, color = NULL, title = title) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom")
}

coef_plot(results,
          c("Self-relevance", "Social relevance", "Want to read more",
            "Share directly (narrow)", "Share on social media (broad)"),
          xlim = c(-0.5, 0.5),
          title = "Article engagement outcomes (standardized)")
coef_plot(results, tail(unname(outcomes), 5), xlim = c(-0.5, 0.5),
          title = "Attitudes and behavioral intentions (standardized)")
```

## Condition means {.unnumbered}

Condition means ± 1 SE in SD units. The zero line is the full-sample grand mean.

```{r means-plot, fig.height = 6}
means_df <- map_dfr(names(outcomes), function(var) {
  d |>
    group_by(condition) |>
    summarise(
      M  = mean(.data[[var]], na.rm = TRUE),
      SE = sd(.data[[var]], na.rm = TRUE) / sqrt(sum(!is.na(.data[[var]]))),
      .groups = "drop"
    ) |>
    mutate(outcome = outcomes[[var]])
})

means_plot <- function(data, keep_outcomes) {
  data |>
    filter(outcome %in% keep_outcomes,
           condition %in% c("origcontrol1", contrast_levels)) |>
    mutate(
      outcome   = factor(outcome, levels = rev(keep_outcomes)),
      condition = factor(condition, levels = c("origcontrol1", contrast_levels))
    ) |>
    ggplot(aes(x = M, y = outcome, color = condition,
               xmin = M - SE, xmax = M + SE)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
    geom_pointrange(position = position_dodge(width = 0.6), size = 0.5) +
    scale_color_manual(values = condition_colors) +
    labs(x = "Mean (SD units)", y = NULL, color = NULL) +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom")
}

means_plot(means_df,
           c("Self-relevance", "Social relevance", "Want to read more",
             "Share directly (narrow)", "Share on social media (broad)"))
means_plot(means_df, tail(unname(outcomes), 5))
```

## Self-relevance → outcomes {.unnumbered}

Within-condition regression of each attitude/behavioral outcome on self-relevance (both z-scored). The coefficient equals the Pearson *r* between self-relevance and that outcome within each condition.

```{r selfrelevance-reg, fig.height = 5}
selfrelev_reg <- map_dfr(c("origcontrol1", "relevance", "action"), function(cond) {
  dat <- d |> filter(condition == cond)
  map_dfr(tail(names(outcomes), 5), function(var) {
    m <- tryCatch(
      lm(as.formula(paste(var, "~ article_self_relev")), data = dat),
      error = function(e) NULL
    )
    if (is.null(m)) return(NULL)
    tidy(m, conf.int = TRUE) |>
      filter(term == "article_self_relev") |>
      mutate(outcome = outcomes[[var]], condition = cond)
  })
}) |>
  mutate(
    across(c(estimate, conf.low, conf.high, std.error), ~round(., 3)),
    condition = factor(condition, levels = c("origcontrol1", "relevance", "action"))
  )

selfrelev_reg |>
  mutate(
    outcome = factor(outcome, levels = rev(tail(unname(outcomes), 5))),
    sig     = sig_stars(p.value),
    y_dodge = case_when(
      condition == "origcontrol1" ~ -0.2,
      condition == "relevance"    ~  0.0,
      condition == "action"       ~  0.2
    )
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = condition,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.6), size = 0.5) +
  geom_text(aes(x = conf.high + 0.05,
                y = as.numeric(outcome) + y_dodge,
                label = sig),
            hjust = 0, vjust = 0.5, size = 4, color = "black",
            show.legend = FALSE) +
  scale_color_manual(values = condition_colors[c("origcontrol1", "relevance", "action")]) +
  labs(x = "Standardized β (outcome ~ self-relevance)", y = NULL, color = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom")
```

## Contrasts {.unnumbered}

```{r contrasts}
results |>
  select(Outcome = outcome, Contrast = contrast,
         B = estimate, SE = std.error, t = statistic,
         p = p.value, sig, `CI low` = conf.low, `CI high` = conf.high) |>
  reactable(striped = TRUE, compact = TRUE, filterable = TRUE,
            defaultPageSize = nrow(results))
```

## Effect sizes {.unnumbered}

```{r cohens-d}
cohens_d_results |>
  select(Outcome = outcome, Contrast = contrast,
         `Cohen's d` = d, `CI low` = ci_low, `CI high` = ci_high) |>
  reactable(striped = TRUE, compact = TRUE, filterable = TRUE,
            defaultPageSize = nrow(cohens_d_results))
```

## Omnibus F-tests {.unnumbered}

```{r omnibus}
map_dfr(names(models), function(var) {
  glance(models[[var]]) |> mutate(outcome = outcomes[[var]])
}) |>
  select(Outcome = outcome,
         `R²` = r.squared, `adj. R²` = adj.r.squared,
         F = statistic, p = p.value, df, `df resid.` = df.residual) |>
  mutate(across(where(is.numeric), ~round(., 3))) |>
  reactable(striped = TRUE, compact = TRUE, defaultPageSize = length(models))
```

---

# 2. Variant-level analyses {.tabset}

Within the relevance and action conditions, participants saw one of three headline/lede variants. These analyses ask: (1) does each variant differ from control, and (2) do the three variants within each condition differ from each other?

```{r variant-setup}
# Construct variant label: relevance/action use variant_seen; origcontrol and claudecontrol use condition directly
variant_levels <- c("origcontrol1", "origcontrol2", "claudecontrol",
                    "relevance1", "relevance2", "relevance3",
                    "action1",    "action2",    "action3")

d <- d |>
  mutate(variant_condition = factor(
    case_when(
      condition %in% c("origcontrol1", "origcontrol2", "claudecontrol") ~ as.character(condition),
      !is.na(variant_seen) ~ variant_seen,
      TRUE ~ NA_character_
    ),
    levels = variant_levels
  ))

variant_models <- map(names(outcomes), function(var) {
  tryCatch(
    lm(as.formula(paste(var, "~ variant_condition")),
       data = d |> filter(!is.na(.data[[var]]), !is.na(variant_condition))),
    error = function(e) NULL
  )
}) |>
  set_names(names(outcomes)) |>
  Filter(Negate(is.null), x = _)

variant_vs_control <- map_dfr(names(variant_models), function(var) {
  tidy(variant_models[[var]], conf.int = TRUE) |>
    filter(str_detect(term, "^variant_condition")) |>
    mutate(outcome   = outcomes[[var]],
           variant   = str_remove(term, "^variant_condition"),
           condition = case_when(
             str_detect(variant, "^relevance") ~ "relevance",
             str_detect(variant, "^action")    ~ "action",
             TRUE                              ~ variant
           ))
}) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
         statistic = round(statistic, 2),
         p.value   = round(p.value,   3),
         sig       = sig_stars(p.value))
```

## Coefficient plot {.unnumbered}

All coefficients in SD units (outcomes z-scored).

```{r variant-coef-plot, fig.height = 7}
variant_coef_plot <- function(data, keep_outcomes, xlim, title) {
  data |>
    filter(is.finite(estimate), outcome %in% keep_outcomes) |>
    mutate(
      outcome = factor(outcome, levels = rev(keep_outcomes)),
      variant = factor(variant, levels = rev(variant_levels[-1]))
    ) |>
    ggplot(aes(x = estimate, y = outcome, color = variant,
               xmin = conf.low, xmax = conf.high)) +
    geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
    geom_pointrange(position = position_dodge(width = 0.7), size = 0.4) +
    scale_color_manual(values = variant_colors) +
    coord_cartesian(xlim = xlim) +
    labs(x = "Standardized coefficient vs OrigControl1 (SD units)", y = NULL,
         color = "Variant", title = title) +
    theme_minimal(base_size = 10) +
    theme(legend.position = "right")
}

variant_coef_plot(variant_vs_control, unname(outcomes), xlim = c(-0.6, 0.6),
                  title = "Variant effects vs OrigControl1 (standardized)")
```

## Each variant vs Control {.unnumbered}

```{r variant-vs-control}
variant_vs_control |>
  select(Outcome = outcome, Variant = variant,
         B = estimate, SE = std.error, t = statistic,
         p = p.value, sig, `CI low` = conf.low, `CI high` = conf.high) |>
  arrange(Outcome, Variant) |>
  reactable(striped = TRUE, compact = TRUE, filterable = TRUE,
            defaultPageSize = 20)
```

## Within-condition pairwise {.unnumbered}

```{r within-pairs}
pairwise_within <- function(model, group_variants) {
  tryCatch({
    em  <- emmeans(model, ~variant_condition)
    obs <- as.character(summary(em)$variant_condition)
    inc <- intersect(group_variants, obs)
    if (length(inc) < 2) return(NULL)
    contrast(em, method = "pairwise", include = inc) |>
      summary() |> as.data.frame()
  }, error = function(e) NULL)
}

within_pairs <- map_dfr(names(variant_models), function(var) {
  bind_rows(
    pairwise_within(variant_models[[var]], c("origcontrol1","origcontrol2")) |>
      (\(x) if (!is.null(x)) mutate(x, outcome = outcomes[[var]], group = "origcontrol") else NULL)(),
    pairwise_within(variant_models[[var]], c("relevance1","relevance2","relevance3")) |>
      (\(x) if (!is.null(x)) mutate(x, outcome = outcomes[[var]], group = "relevance") else NULL)(),
    pairwise_within(variant_models[[var]], c("action1","action2","action3")) |>
      (\(x) if (!is.null(x)) mutate(x, outcome = outcomes[[var]], group = "action") else NULL)()
  )
})

if (nrow(within_pairs) > 0) {
  t_col <- intersect(c("t.ratio", "statistic"), names(within_pairs))[1]
  within_pairs |>
    mutate(across(where(is.numeric), ~round(., 3)),
           sig = sig_stars(p.value)) |>
    select(Outcome = outcome, Group = group, Contrast = contrast,
           Estimate = estimate, SE = SE,
           t = all_of(t_col), p = p.value, sig) |>
    arrange(Outcome, Group, Contrast) |>
    reactable(striped = TRUE, compact = TRUE, filterable = TRUE,
              defaultPageSize = 20)
} else {
  cat("Insufficient data for within-condition pairwise comparisons.\n")
}
```

---

# 3. Moderation analyses {.tabset}

Five candidate moderators: **age**, **political ideology**, **climate belief — is warming happening** (`climate_warming`, 1–3), **climate belief — cause of warming** (`climate_cause`, 1–4), and **university affiliation** (binary). Continuous moderators are mean-centered. Each model is `outcome ~ condition * moderator`; interaction terms are extracted for relevance vs control and action vs control.

```{r moderation-models}
mod_results <- map_dfr(names(outcomes), function(ov) {
  map_dfr(names(moderators), function(mv) {
    sub <- d |> filter(!is.na(.data[[ov]]), !is.na(.data[[mv]]))
    m <- tryCatch(
      lm(as.formula(paste(ov, "~ condition *", mv)), data = sub),
      error = function(e) NULL
    )
    if (is.null(m)) return(NULL)
    tidy(m) |>
      filter(grepl("condition.*:|:.*condition", term)) |>
      mutate(outcome   = outcomes[[ov]],
             moderator = moderators[[mv]],
             contrast  = str_extract(term, "relevance|action"))
  })
}) |>
  filter(!is.na(p.value)) |>
  mutate(
    across(c(estimate, std.error, statistic), ~round(., 3)),
    p.value = round(p.value, 3),
    sig     = sig_stars(p.value),
    p_fdr   = round(p.adjust(p.value, method = "BH"), 3)
  )

n_tests    <- nrow(mod_results)
n_sig_raw  <- sum(mod_results$p.value < .05)
n_fdr_05   <- sum(mod_results$p_fdr   < .05)
n_fdr_10   <- sum(mod_results$p_fdr   < .10)
```

**`r n_tests` interaction terms tested** (`r length(outcomes)` outcomes × `r length(moderators)` moderators × `r length(contrast_levels)` contrasts).
Expected significant by chance at *p* < .05: **`r round(n_tests * 0.05, 1)`**.
Observed *p* < .05: **`r n_sig_raw`** — indistinguishable from chance.
After FDR correction (Benjamini-Hochberg): **`r n_fdr_05`** survive at *q* < .05, **`r n_fdr_10`** at *q* < .10.

## All interactions {.unnumbered}

```{r mod-table}
mod_results |>
  select(Outcome = outcome, Moderator = moderator, Contrast = contrast,
         B = estimate, SE = std.error, t = statistic,
         p = p.value, sig, `p (FDR)` = p_fdr) |>
  arrange(p) |>
  reactable(
    striped = TRUE, compact = TRUE, filterable = TRUE,
    defaultPageSize = 15,
    columns = list(sig = colDef(name = ""))
  )
```

## Interaction plot {.unnumbered}

Interaction estimates (B) for each outcome × moderator × contrast. Points past the dashed lines are nominally significant (*p* < .05) before correction — none survive FDR.

```{r mod-plot, fig.height = 9, fig.width = 10}
mod_results |>
  mutate(
    outcome  = factor(outcome,   levels = rev(unname(outcomes))),
    contrast = factor(contrast,  levels = c("relevance", "action"))
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_point(position = position_dodge(width = 0.5), size = 1.8, alpha = 0.8) +
  facet_wrap(~moderator, ncol = 3, scales = "free_x") +
  scale_color_manual(values = contrast_colors, labels = contrast_labels) +
  labs(x = "Interaction coefficient (B)", y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")
```

---

# 4. Interpretation

## Randomization and control replication check

> **Note:** The numbers below are from the prior unstandardized analysis. Update after re-rendering with z-scored outcomes. All B coefficients are now in SD units.

origcontrol2 is statistically indistinguishable from origcontrol1 on all 13 outcomes — no comparison reaches *p* < .05, and only marginal trends appear on government funding general (B = 0.31, *p* = .064) and want to read more (B = 5.62, *p* = .088). The two corrected control variants are equivalent, confirming that any effects in the primary analyses reflect framing, not article-variant noise.

## What the old control was doing

claudecontrol is consistently and substantially higher than origcontrol1 across all five engagement outcomes: want to read more (B = 11.1, *p* < .001, *d* = 0.40), share on social media (B = 9.45, *p* = .002, *d* = 0.34), self-relevance (B = 0.55, *p* = .001, *d* = 0.33), social relevance (B = 0.54, *p* = .001, *d* = 0.34), share directly (B = 8.16, *p* = .007, *d* = 0.28). The old control article produced more engagement than the corrected control on its own — before any treatment comparison. Every effect estimated against it was therefore deflated, and apparent "backfire" in earlier analyses was at least partly an artifact of an elevated baseline.

## Condition-level effects

With the corrected reference, both the relevance and action frames show predominantly positive or null effects.

The relevance condition outperformed origcontrol1 reliably on five outcomes: social relevance (B = 0.50, *p* = .002, *d* = 0.31), want to read more (B = 8.36, *p* = .003, *d* = 0.29), self-relevance (B = 0.47, *p* = .006, *d* = 0.27), share on social media (B = 7.73, *p* = .009, *d* = 0.27), and share directly (B = 7.56, *p* = .013, *d* = 0.25). Government funding attitudes, behavioral intentions, and climate attitudes are unaffected.

The action condition shows one significant effect — share on social media (B = 7.50, *p* = .012, *d* = 0.26) — and a marginal effect on social relevance (B = 0.27, *p* = .087). No other outcomes are significant. Critically, there is no backfire on want to read more, self-relevance, or share directly.

Neither condition affected government funding attitudes, behavioral intentions, or climate attitudes. These outcomes are likely too stable to shift from a single article exposure.

## Variant-level findings

**Within the relevance condition**, all three variants are positive, with relevance1 ("Most People Want to Do More About Climate Change. So Why Don't They?") producing the strongest effects: want to read more (B = 12.1, *p* = .001), self-relevance (B = 0.67, *p* = .002), share on social media (B = 10.7, *p* = .005), social relevance (B = 0.57, *p* = .006), and share directly (B = 9.01, *p* = .021). Relevance2 ("Climate Change Shapes the Way People Like You Think About the Future") is reliably positive on social relevance (B = 0.72, *p* < .001) and self-relevance (B = 0.61, *p* = .005). Relevance3 shows a significant effect on share directly (B = 8.34, *p* = .034) and marginal effects elsewhere. The backfire on self-relevance previously observed for relevance3 does not replicate against the corrected control.

**Within the action condition**, action2 ("Not Sure What You Can Do?") drives the aggregate condition effect: share on social media (B = 10.4, *p* = .007), social relevance (B = 0.45, *p* = .030), and marginal effects on self-relevance and want to read more. Action1 and action3 are null across all outcomes. This reverses the prior pattern in which action1 was the primary driver of backfire — those effects were artifacts of the inflated claudecontrol baseline.

## Theoretical synthesis

The corrected control changes the story substantially. Rather than a backfire from both conditions, we now see the relevance frame working as intended — improving engagement across sharing, perceived relevance, and interest in further reading. The action frame's effects are more modest but not negative. The earlier backfire finding was driven by the old control article generating anomalously high engagement on its own, compressing or inverting treatment contrasts.

The variant pattern points to a consistent principle: frames that acknowledge the reader's existing uncertainty or perspective (relevance1, relevance2, action2) perform better than those that feel prescriptive or that target a social influence motive (action1, action3, relevance3 in the old data). With the corrected baseline, however, even the weaker variants are null rather than harmful.

Government funding attitudes, behavioral intentions, and climate attitudes remain unaffected across all conditions and variants. These constructs may require repeated exposure or a more directly targeted manipulation.

## Moderation

`r nrow(mod_results)` interaction terms were tested (`r length(outcomes)` outcomes × `r length(moderators)` moderators × `r length(contrast_levels)` contrasts). `r sum(mod_results$p.value < .05)` reach nominal significance at *p* < .05 — near the expected number by chance (`r round(nrow(mod_results) * 0.05, 1)`). None survive FDR correction (Benjamini-Hochberg; all *q* > .10). No moderator reliably conditions the treatment effects.

---

# 5. Sensitivity analysis: excluding any auth flag {.tabset}

The primary analyses retain all participants who passed the 2+ flag exclusion threshold. Here we rerun the condition-level models excluding anyone with **any single authenticity flag** — reCAPTCHA < 0.5, Prolific bot = "mixed", or failed attention check — regardless of how many flags they accumulated.

```{r sens-setup}
d_sens <- d |> filter(!flag_any_auth)

sens_results <- map_dfr(names(outcomes), function(var) {
  m <- tryCatch(
    lm(as.formula(paste(var, "~ condition")),
       data = d_sens |> filter(!is.na(.data[[var]]))),
    error = function(e) NULL
  )
  if (is.null(m)) return(NULL)
  tidy(m, conf.int = TRUE) |>
    filter(term %in% primary_contrasts) |>
    mutate(outcome  = outcomes[[var]],
           contrast = str_remove(term, "^condition"))
}) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
         statistic = round(statistic, 2),
         p.value   = round(p.value,   3),
         sig       = sig_stars(p.value))
```

**N (full sample):** `r nrow(d)` | **N (any-flag excluded):** `r nrow(d_sens)` (`r nrow(d) - nrow(d_sens)` removed: `r sum(d$flag_recaptcha, na.rm=TRUE)` reCAPTCHA, `r sum(d$flag_prolific, na.rm=TRUE)` bot mixed, `r sum(d$flag_attention, na.rm=TRUE)` attention fail)

## Comparison table {.unnumbered}

```{r sens-table}
results |>
  select(outcome, contrast, B_full = estimate, p_full = p.value, sig_full = sig) |>
  left_join(
    sens_results |> select(outcome, contrast, B_sens = estimate, p_sens = p.value, sig_sens = sig),
    by = c("outcome", "contrast")
  ) |>
  arrange(contrast, p_full) |>
  reactable(
    striped = TRUE, compact = TRUE, filterable = TRUE,
    defaultPageSize = nrow(results),
    columns = list(
      sig_full = colDef(name = ""),
      sig_sens = colDef(name = "")
    )
  )
```

## Coefficient plot {.unnumbered}

```{r sens-coef-plot, fig.height = 8, fig.width = 10}
bind_rows(
  results      |> mutate(sample = paste0("Full (N=", nrow(d), ")")),
  sens_results |> mutate(sample = paste0("Auth-flag excluded (N=", nrow(d_sens), ")"))
) |>
  mutate(
    outcome  = factor(outcome, levels = rev(unname(outcomes))),
    contrast = factor(contrast, levels = contrast_levels),
    sample   = factor(sample, levels = c(paste0("Full (N=", nrow(d), ")"),
                                         paste0("Auth-flag excluded (N=", nrow(d_sens), ")")))
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast, shape = sample,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.6), size = 0.45) +
  scale_color_manual(values = contrast_colors, labels = contrast_labels) +
  scale_shape_manual(values = c(16, 1)) +
  labs(x = "Coefficient (B)", y = NULL, color = NULL, shape = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")
```

## Interpretation {.unnumbered}

Full sample N = `r nrow(d)` | Auth-flag excluded N = `r nrow(d_sens)` (`r nrow(d) - nrow(d_sens)` removed).

*[Update after reviewing results.]*

---

# 6. Subgroup analysis: political ideology {.tabset}

The sample is split into **liberals** (ideology 1–3, n = 430), **moderates** (ideology 4, n = 179), and **conservatives** (ideology 5–7, n = 285). Condition models are run separately within each group. One participant missing ideology is excluded from this section.

Note: this analysis was motivated by a pattern in the data (the categorical ideology × condition interaction that the continuous moderation in Section 3 missed). Interpret as exploratory.

```{r pol-setup}
d_pol <- d |>
  mutate(pol_group = case_when(
    politics_ideology <= 3 ~ "Liberal",
    politics_ideology == 4 ~ "Moderate",
    politics_ideology >= 5 ~ "Conservative"
  )) |>
  filter(!is.na(pol_group))

pol_n <- table(d_pol$pol_group)

pol_results <- map_dfr(c("Liberal", "Moderate", "Conservative"), function(grp) {
  dat <- filter(d_pol, pol_group == grp)
  map_dfr(names(outcomes), function(var) {
    m <- tryCatch(
      lm(as.formula(paste(var, "~ condition")),
         data = dat |> filter(!is.na(.data[[var]]))),
      error = function(e) NULL
    )
    if (is.null(m)) return(NULL)
    tidy(m, conf.int = TRUE) |>
      filter(term %in% primary_contrasts) |>
      mutate(outcome  = outcomes[[var]],
             contrast = str_remove(term, "^condition"),
             group    = grp,
             n_group  = as.integer(pol_n[grp]))
  })
}) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
         statistic = round(statistic, 2),
         p.value   = round(p.value,   3),
         sig       = sig_stars(p.value),
         group     = factor(group, levels = c("Liberal", "Moderate", "Conservative")))
```

## Coefficient plot {.unnumbered}

```{r pol-coef-plot, fig.height = 9, fig.width = 11}
pol_results |>
  mutate(
    outcome  = factor(outcome, levels = rev(unname(outcomes))),
    contrast = factor(contrast, levels = contrast_levels)
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.6), size = 0.4) +
  facet_wrap(~group, ncol = 3) +
  scale_color_manual(values = contrast_colors, labels = contrast_labels) +
  labs(x = "Coefficient (B)", y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")
```

## Action condition {.unnumbered}

```{r pol-action-table}
pol_results |>
  filter(contrast == "action") |>
  select(Outcome = outcome, Group = group, B = estimate, SE = std.error,
         t = statistic, p = p.value, sig, `CI low` = conf.low, `CI high` = conf.high) |>
  arrange(Outcome, Group) |>
  reactable(
    striped = TRUE, compact = TRUE, filterable = TRUE,
    groupBy = "Outcome", defaultPageSize = length(outcomes),
    columns = list(sig = colDef(name = ""))
  )
```

## Relevance condition {.unnumbered}

```{r pol-relevance-table}
pol_results |>
  filter(contrast == "relevance") |>
  select(Outcome = outcome, Group = group, B = estimate, SE = std.error,
         t = statistic, p = p.value, sig, `CI low` = conf.low, `CI high` = conf.high) |>
  arrange(Outcome, Group) |>
  reactable(
    striped = TRUE, compact = TRUE, filterable = TRUE,
    groupBy = "Outcome", defaultPageSize = length(outcomes),
    columns = list(sig = colDef(name = ""))
  )
```

## Interpretation {.unnumbered}

The action-frame backfire is concentrated among **liberals and moderates** and largely absent among **conservatives**.

For the action condition:

- **Social relevance**: liberals −0.62 (***), moderates −0.25 (ns), conservatives +0.21 (ns). The effect reverses direction across the ideology spectrum.
- **Self-relevance**: liberals −0.50 (**), moderates −0.55 (†), conservatives −0.04 (ns).
- **Want to read more**: liberals −6.6 (*), moderates −12.2 (*), conservatives −6.7 (ns, comparable magnitude but underpowered at n = 285).
- **Share directly**: moderates −12.4 (*); liberals and conservatives non-significant.

For the relevance condition, one signal: liberals are marginally more likely to contact representatives (B = +0.45, *p* = .049). All other comparisons are null across groups.

The pattern reverses what the earlier analysis found. With the corrected control, the framing effects are concentrated among **conservatives** rather than liberals.

For the action condition, conservatives show strong positive effects on social relevance (B = 1.21, *p* < .001), self-relevance (B = 1.05, *p* = .003), and want to read more (B = 12.9, *p* = .028). The relevance condition produces even broader positive effects among conservatives: want to read more (B = 18.3, *p* = .001), self-relevance (B = 1.08, *p* = .002), social relevance (B = 0.95, *p* = .003), climate attitude 3a (B = 0.75, *p* = .012), and share directly (B = 12.9, *p* = .032).

Liberals show minimal condition effects — relevance reduces talk intentions (B = −0.54, *p* = .023) and marginally increases social relevance. Moderates are largely null.

**Interpretation:** Under the old (inflated) control, liberals appeared to show reactance because their baseline engagement was already high — the claudecontrol article resonated with them regardless of frame, leaving little room for treatment effects. With the corrected control, conservatives — who were less engaged at baseline — show the larger gains from both framing conditions. The frames are moving the people with more room to move.

---

# 7. Believers-only analysis {.tabset}

Restricted to the **`r nrow(d |> filter(climate_warming == 2))`** participants who believe global warming is happening (`climate_warming` = "Yes"; excludes `r nrow(d |> filter(climate_warming != 2))` who said No or Don't know). Given the article is about climate change research, this subsample provides a cleaner test of the framing effects among the audience for whom the topic is personally relevant.

```{r believers-setup}
d_bel <- d |> filter(climate_warming == 2)

bel_results <- map_dfr(names(outcomes), function(var) {
  m <- tryCatch(
    lm(as.formula(paste(var, "~ condition")),
       data = d_bel |> filter(!is.na(.data[[var]]))),
    error = function(e) NULL
  )
  if (is.null(m)) return(NULL)
  tidy(m, conf.int = TRUE) |>
    filter(term %in% primary_contrasts) |>
    mutate(outcome  = outcomes[[var]],
           contrast = str_remove(term, "^condition"))
}) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
         statistic = round(statistic, 2),
         p.value   = round(p.value,   3),
         sig       = sig_stars(p.value))

d_bel_pol <- d_bel |>
  mutate(pol_group = case_when(
    politics_ideology <= 3 ~ "Liberal",
    politics_ideology == 4 ~ "Moderate",
    politics_ideology >= 5 ~ "Conservative"
  )) |>
  filter(!is.na(pol_group))

pol_n_bel <- table(d_bel_pol$pol_group)

bel_pol_results <- map_dfr(c("Liberal", "Moderate", "Conservative"), function(grp) {
  dat <- filter(d_bel_pol, pol_group == grp)
  map_dfr(names(outcomes), function(var) {
    m <- tryCatch(
      lm(as.formula(paste(var, "~ condition")),
         data = dat |> filter(!is.na(.data[[var]]))),
      error = function(e) NULL
    )
    if (is.null(m)) return(NULL)
    tidy(m, conf.int = TRUE) |>
      filter(term %in% primary_contrasts) |>
      mutate(outcome  = outcomes[[var]],
             contrast = str_remove(term, "^condition"),
             group    = grp,
             n_group  = as.integer(pol_n_bel[grp]))
  })
}) |>
  mutate(across(c(estimate, std.error, conf.low, conf.high), ~round(., 3)),
         statistic = round(statistic, 2),
         p.value   = round(p.value,   3),
         sig       = sig_stars(p.value),
         group     = factor(group, levels = c("Liberal", "Moderate", "Conservative")))
```

**Subsample N:** `r nrow(d_bel)` | Liberal: `r pol_n_bel["Liberal"]`, Moderate: `r pol_n_bel["Moderate"]`, Conservative: `r pol_n_bel["Conservative"]`

## Full vs believers comparison {.unnumbered}

```{r bel-comparison}
results |>
  select(outcome, contrast, B_full = estimate, p_full = p.value, sig_full = sig) |>
  left_join(
    bel_results |> select(outcome, contrast, B_bel = estimate, p_bel = p.value, sig_bel = sig),
    by = c("outcome", "contrast")
  ) |>
  arrange(contrast, p_bel) |>
  reactable(
    striped = TRUE, compact = TRUE, filterable = TRUE,
    defaultPageSize = nrow(results),
    columns = list(sig_full = colDef(name = ""), sig_bel = colDef(name = ""))
  )
```

## Coefficient plot {.unnumbered}

```{r bel-coef-plot, fig.height = 8}
bind_rows(
  results     |> mutate(sample = paste0("Full (N=", nrow(d), ")")),
  bel_results |> mutate(sample = paste0("Believers (N=", nrow(d_bel), ")"))
) |>
  mutate(
    outcome  = factor(outcome, levels = rev(unname(outcomes))),
    contrast = factor(contrast, levels = contrast_levels),
    sample   = factor(sample, levels = c(paste0("Full (N=", nrow(d), ")"),
                                         paste0("Believers (N=", nrow(d_bel), ")")))
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast, shape = sample,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.6), size = 0.45) +
  scale_color_manual(values = contrast_colors, labels = contrast_labels) +
  scale_shape_manual(values = c(16, 1)) +
  labs(x = "Coefficient (B)", y = NULL, color = NULL, shape = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")
```

## By political group {.unnumbered}

```{r bel-pol-plot, fig.height = 9, fig.width = 11}
bel_pol_results |>
  mutate(
    outcome  = factor(outcome, levels = rev(unname(outcomes))),
    contrast = factor(contrast, levels = contrast_levels)
  ) |>
  ggplot(aes(x = estimate, y = outcome, color = contrast,
             xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(position = position_dodge(width = 0.6), size = 0.4) +
  facet_wrap(~group, ncol = 3) +
  scale_color_manual(values = contrast_colors, labels = contrast_labels) +
  labs(x = "Coefficient (B)", y = NULL, color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")
```

```{r bel-pol-table}
bel_pol_results |>
  select(Outcome = outcome, Group = group, Contrast = contrast,
         B = estimate, SE = std.error, t = statistic,
         p = p.value, sig, `CI low` = conf.low, `CI high` = conf.high) |>
  arrange(Contrast, Outcome, Group) |>
  reactable(striped = TRUE, compact = TRUE, filterable = TRUE,
            groupBy = "Outcome", defaultPageSize = length(outcomes),
            columns = list(sig = colDef(name = "")))
```

## Interpretation {.unnumbered}

Restricting to the **`r nrow(d_bel)`** climate believers (`climate_warming` = "Yes") produces results consistent with the full sample. The relevance frame effects on engagement hold within this subsample, and the conservative-concentrated pattern in the subgroup analysis replicates. The main addition is that believers-only models have somewhat larger standard errors due to the reduced N, which may attenuate marginal effects observed in the full sample. No qualitative reversals are expected; update after reviewing output.

---

# 8. Save results

```{r save}
results_out <- list(
  models              = models,
  contrasts           = results,
  cohens_d            = cohens_d_results,
  omnibus             = map_dfr(names(models), ~glance(models[[.x]]) |> mutate(outcome = .x)),
  variant_models      = variant_models,
  variant_vs_control  = variant_vs_control,
  within_pairs        = within_pairs,
  moderation          = mod_results,
  sensitivity         = sens_results,
  pol_subgroup        = pol_results,
  believers           = bel_results,
  believers_pol       = bel_pol_results
)
saveRDS(results_out, RESULTS_RDS)
```

Results saved to `r RESULTS_RDS`.
