---
title: "Step 2 — Plain-Language Plots"
subtitle: "Raw-scale means for non-technical audiences"
author: "Nicole Cooper"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: yes
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 7, fig.height = 5)
options(scipen = 999)
```

```{r packages}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, here, patchwork)
```

```{r load}
source(here("Step2", "analysis", "config.R"))
d <- readRDS(CLEANED_RDS)

# Raw govtfund_cuts is "approval of cuts" (1=strongly disapprove, 7=strongly approve of cuts).
# Reverse so higher = disapproval of cuts, matching the pro-funding direction of every other
# outcome (consistent with the recoding in 02_analysis.Rmd).
d <- d |> mutate(govtfund_cuts = 8 - govtfund_cuts)
```

These plots use **raw, unstandardized scales** (not SD units) and show the **mean ± 1 SE** (the precision of each group's estimated average — the same uncertainty basis as the technical analysis, just plotted on the item's original scale). Asterisks mark conditions that differ significantly from Control, based on the condition regression. They're meant for sharing with audiences who don't need full model output — just "here's what people said, and here's what's a real difference vs. not."

```{r condition-setup}
PRIMARY_CONDITIONS <- c("origcontrol1", "relevance", "action")

condition_labels_plain <- c(
  origcontrol1 = "Control",
  relevance    = "Relevance frame",
  action       = "Action frame"
)

condition_colors_plain <- c(
  origcontrol1 = "#444444",
  relevance    = "#011F5B",
  action       = "#990000"
)

sig_stars <- function(p) case_when(
  p < .001 ~ "***", p < .01 ~ "**", p < .05 ~ "*", p < .10 ~ "†", TRUE ~ ""
)
```

## Function

```{r plot-fn}
# Bar chart of raw-scale means +/- 1 SE for the three primary conditions, with
# significance stars (vs Control) from a condition regression on the raw outcome.
# outcome_var   - column name in `data` (string)
# outcome_label - y-axis label, e.g. "Self-relevance (1-7)"
# y_limits      - optional c(min, max) to fix the scale to the item's real range
# out_file      - filename (no path) to save under this folder; NULL skips saving
# show_caption  - set FALSE when combining panels, so the caption isn't repeated per panel
# base_size     - overall font scale; shrink this (not individual text sizes) for multi-panel slides
# title_wrap    - character width to wrap the panel title at, so long titles don't overflow
plot_mean_se <- function(data, outcome_var, outcome_label, y_limits = NULL, out_file = NULL,
                          show_caption = TRUE, base_size = 20, title_wrap = 40) {
  dat <- data |> filter(condition %in% PRIMARY_CONDITIONS, !is.na(.data[[outcome_var]]))

  df <- dat |>
    group_by(condition) |>
    summarise(
      M  = mean(.data[[outcome_var]]),
      SE = sd(.data[[outcome_var]]) / sqrt(n()),
      n  = n(),
      .groups = "drop"
    ) |>
    mutate(condition = factor(condition, levels = PRIMARY_CONDITIONS))

  # Condition regression (origcontrol1 is the reference level) for significance stars
  m <- lm(reformulate("condition", response = outcome_var), data = droplevels(dat))
  sig_df <- broom::tidy(m) |>
    filter(term %in% c("conditionrelevance", "conditionaction")) |>
    mutate(condition = str_remove(term, "^condition"), sig = sig_stars(p.value)) |>
    select(condition, sig, p.value)

  df <- df |> left_join(sig_df, by = "condition") |>
    mutate(sig = replace_na(sig, ""),
           condition = factor(condition, levels = PRIMARY_CONDITIONS))

  p <- ggplot(df, aes(x = condition, y = M, fill = condition)) +
    geom_col(width = 0.6) +
    geom_errorbar(aes(ymin = M - SE, ymax = M + SE), width = 0.15, linewidth = 0.6) +
    geom_text(aes(label = sprintf("%.1f", M), y = M), vjust = 1.5, size = base_size * 0.325,
              fontface = "bold", color = "white") +
    geom_text(aes(label = sig, y = M + SE), vjust = -0.4, size = base_size * 0.4,
              fontface = "bold", color = "black") +
    scale_x_discrete(labels = condition_labels_plain) +
    scale_fill_manual(values = condition_colors_plain, guide = "none") +
    labs(x = NULL, y = outcome_label, title = str_wrap(outcome_label, title_wrap)) +
    theme_minimal(base_size = base_size) +
    theme(plot.title = element_text(face = "bold"),
          axis.text = element_text(size = base_size * 0.8),
          plot.margin = margin(5.5, 12, 5.5, 5.5),
          plot.caption = element_text(hjust = 0, size = base_size * 0.6))

  if (show_caption) {
    p <- p + labs(caption = "Bars = group mean. Error bars = ±1 SE. Asterisks: significant\ndifference vs Control (* p<.05, ** p<.01, *** p<.001, † p<.10).")
  }

  if (!is.null(y_limits)) p <- p + coord_cartesian(ylim = y_limits)

  if (!is.null(out_file)) {
    ggsave(here("Step2", "analysis", out_file), p, width = 8.5, height = 6.5, dpi = 200)
  }
  p
}
```

## Self-relevance

```{r self-relevance}
plot_mean_se(d, "article_self_relev", "Self-relevance (1-7)",
             y_limits = c(1, 7), out_file = "plot_self_relevance.png")
```

## Want to read more, share directly, share on social media

```{r read-share-slide, fig.width = 15, fig.height = 6.5}
p1 <- plot_mean_se(d, "read_more",     "Want to read more (0-100)",
                    y_limits = c(0, 100), show_caption = FALSE, base_size = 15, title_wrap = 20)
p2 <- plot_mean_se(d, "share_narrow",  "Share directly (0-100)",
                    y_limits = c(0, 100), show_caption = FALSE, base_size = 15, title_wrap = 20)
p3 <- plot_mean_se(d, "share_broad",   "Share on social media (0-100)",
                    y_limits = c(0, 100), show_caption = FALSE, base_size = 15, title_wrap = 20)

slide_panel <- (p1 | p2 | p3) +
  patchwork::plot_annotation(
    caption = "Bars = group mean. Error bars = ±1 SE. Asterisks: significant difference vs Control (* p<.05, ** p<.01, *** p<.001, † p<.10).",
    theme = theme(plot.caption = element_text(hjust = 0, size = 13))
  )

ggsave(here("Step2", "analysis", "plot_read_share_slide.png"), slide_panel,
       width = 16, height = 7, dpi = 200)
slide_panel
```

## Govt funding attitudes

```{r govtfund-slide, fig.width = 11, fig.height = 6.5}
p1 <- plot_mean_se(d, "govtfund_general", "Govt funding (general) (1-7)",
                    y_limits = c(1, 7), show_caption = FALSE, base_size = 16, title_wrap = 24)
p2 <- plot_mean_se(d, "govtfund_cuts",    "Disapproval of funding cuts (1-7)",
                    y_limits = c(1, 7), show_caption = FALSE, base_size = 16, title_wrap = 24)

govtfund_slide <- (p1 | p2) +
  patchwork::plot_annotation(
    caption = "Bars = group mean. Error bars = ±1 SE. Asterisks: significant difference vs Control (* p<.05, ** p<.01, *** p<.001, † p<.10).",
    theme = theme(plot.caption = element_text(hjust = 0, size = 13))
  )

ggsave(here("Step2", "analysis", "plot_govtfund_slide.png"), govtfund_slide,
       width = 12, height = 7, dpi = 200)
govtfund_slide
```

## Behavioral intentions

```{r intent-slide, fig.width = 15, fig.height = 6.5}
p1 <- plot_mean_se(d, "talk_intent",  "Talk to others about cuts (1-7)",
                    y_limits = c(1, 7), show_caption = FALSE, base_size = 15, title_wrap = 20)
p2 <- plot_mean_se(d, "share_intent", "Share info online about cuts (1-7)",
                    y_limits = c(1, 7), show_caption = FALSE, base_size = 15, title_wrap = 20)
p3 <- plot_mean_se(d, "reps_intent",  "Contact reps to support funding (1-7)",
                    y_limits = c(1, 7), show_caption = FALSE, base_size = 15, title_wrap = 20)

intent_slide <- (p1 | p2 | p3) +
  patchwork::plot_annotation(
    caption = "Bars = group mean. Error bars = ±1 SE. Asterisks: significant difference vs Control (* p<.05, ** p<.01, *** p<.001, † p<.10).",
    theme = theme(plot.caption = element_text(hjust = 0, size = 13))
  )

ggsave(here("Step2", "analysis", "plot_intent_slide.png"), intent_slide,
       width = 16, height = 7, dpi = 200)
intent_slide
```

## Self-relevance → other outcomes

Pooled across all three conditions: does rating an article as more self-relevant go along with higher scores on these outcomes? Points show the simple Pearson correlation (not a per-condition breakdown); all five are significant, so no asterisks are shown.

```{r selfrelev-outcomes-corr, fig.width = 9, fig.height = 5}
corr_outcomes <- c(
  govtfund_general = "Govt funding (general)",
  govtfund_cuts    = "Disapproval of funding cuts",
  talk_intent      = "Talk to others about cuts",
  share_intent     = "Share info online about cuts",
  reps_intent      = "Contact reps to support funding"
)

corr_dat <- d |> filter(condition %in% PRIMARY_CONDITIONS)

corr_results <- map_dfr(names(corr_outcomes), function(var) {
  dat <- corr_dat |> filter(!is.na(.data[[var]]), !is.na(article_self_relev))
  ct  <- cor.test(dat$article_self_relev, dat[[var]])
  tibble(outcome = corr_outcomes[[var]], r = ct$estimate,
         conf.low = ct$conf.int[1], conf.high = ct$conf.int[2], p.value = ct$p.value)
})

corr_results |>
  mutate(outcome = factor(outcome, levels = rev(unname(corr_outcomes)))) |>
  ggplot(aes(x = r, y = outcome, xmin = conf.low, xmax = conf.high)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "grey60") +
  geom_pointrange(size = 0.8, linewidth = 1, color = "#011F5B") +
  geom_text(aes(label = sprintf("r = %.2f", r), y = as.numeric(outcome) + 0.25),
            size = 5, fontface = "bold", color = "#011F5B") +
  labs(x = "Correlation with self-relevance rating (r)", y = NULL,
       title = "Self-relevance is linked to attitudes and behavioral intentions") +
  coord_cartesian(xlim = c(-0.1, 0.6)) +
  theme_minimal(base_size = 16) +
  theme(plot.title = element_text(face = "bold", size = 15))

ggsave(here("Step2", "analysis", "plot_selfrelev_outcomes_corr.png"),
       width = 9, height = 5, dpi = 200)
```

## Adding another outcome

Copy the chunk above and swap in the new `outcome_var` (raw column name from `step2_clean.rds`), its label, and its real scale range for `y_limits` (e.g. `c(0, 100)` for the 0–100 sliders like `share_narrow`/`share_broad`/`read_more`, `c(1, 7)` for the 1–7 Likert items).
