---
title: "August Newsletter Study — Data Cleaning"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(here)
source(here("Newsletter testing", "August headlines", "config.R"))
```

This template reads the Qualtrics + Prolific exports named in `config.R`, applies
exclusions, and saves a cleaned wide data frame. **To run a new round, edit only
`config.R`.** All quality-flag logic lives in `helpers.R::compute_flags()` and is
shared with `01_prolific_rejections.Rmd`, so exclusions and payment rejections
always use identical rules.

## Load data

The pipeline starts from the raw Qualtrics export named in `config.R`.
`read_qualtrics()` parses the three-row Qualtrics header so every column comes in
with the correct type (sliders as numbers, timestamps as dates).

```{r load}
raw <- read_qualtrics(CFG$qualtrics_path)
```

Raw Qualtrics: **`r nrow(raw)` rows**, **`r ncol(raw)` columns**.

## Basic exclusions

Three filters remove non-genuine responses before any quality checks run.
`DistributionChannel == "anonymous"` drops survey previews and internal test runs,
`Finished == TRUE` drops incomplete submissions, and the `PROLIFIC_PID` filter
drops the placeholder string Qualtrics stores when a participant's ID fails to pipe
in. The table below tracks how many rows survive each step.

```{r basic}
n_raw <- nrow(raw)
d <- raw |>
  filter(DistributionChannel == "anonymous") |>
  filter(Finished == TRUE) |>
  filter(PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID))
n_basic <- nrow(d)
```

| Step | N |
|------|---|
| Raw | `r n_raw` |
| Anonymous channel | `r nrow(filter(raw, DistributionChannel == "anonymous"))` |
| Finished | `r nrow(filter(raw, DistributionChannel == "anonymous", Finished == TRUE))` |
| Valid Prolific PID | `r n_basic` |

## Merge Prolific + drop non-completions

Prolific supplies recruitment metadata that Qualtrics does not: submission status,
time taken, the bot-authenticity rating, and demographics. After merging these onto
each response by `PROLIFIC_PID`, we drop submissions Prolific already marks
`RETURNED` or `TIMED-OUT`, since those are never paid and never analyzed.

```{r prolific}
prolific <- read_prolific(CFG$prolific_path)
d <- d |> left_join(prolific, by = "PROLIFIC_PID")

cat("Prolific status:\n"); print(table(d$prolific_status, useNA = "ifany"))

n_before_hard <- nrow(d)
d <- d |> filter(!prolific_status %in% c("RETURNED", "TIMED-OUT"))
cat("\n", n_before_hard - nrow(d),
    "removed (RETURNED / TIMED-OUT). N =", nrow(d), "\n")
```

## Quality flags

`compute_flags()` (in `helpers.R`) computes every quality flag and the final
reject decision in one place, so this cleaning script and the rejection report can
never disagree on who is excluded. A participant is **excluded/rejected** if any
*standalone-reject* flag fires (`r paste(CFG$standalone_reject_flags, collapse=", ")`)
**or** they accumulate `r CFG$reject_nflags`+ flags of any kind. Thresholds are set
in `config.R`.

- `flag_bot_combined` — reCAPTCHA < `r CFG$recaptcha_threshold` **and** Prolific bot ∈ {`r paste(CFG$prolific_bot_fail, collapse=", ")`}
- `flag_duplicate` — Qualtrics `Q_DuplicateRespondent == TRUE`
- `flag_auth_q` — any Prolific per-question authenticity check == "Fail"
- `flag_attention` — `r CFG$attn_nfail`+ *seen* attention sliders ≠ `r CFG$attn_correct`
- `flag_straightline` — identical value across all substantive sliders answered
- `flag_offtask` — off-task minutes > `r CFG$offtask_threshold_min`

The summary table counts how often each flag fires across the sample; the detail
table then lists every flagged participant with the specific reason, so borderline
cases can be inspected by hand.

```{r flags}
d <- compute_flags(d, CFG)

d |>
  summarise(
    `Bot (combined)`       = sum(flag_bot_combined),
    `Duplicate`            = sum(flag_duplicate),
    `Auth-question fail`   = sum(flag_auth_q),
    `Attention (2+ seen)`  = sum(flag_attention),
    `Straightlined`        = sum(flag_straightline),
    `Off-task > threshold` = sum(flag_offtask),
    `Rejected / excluded`  = sum(reject)
  ) |>
  pivot_longer(everything(), names_to = "Flag", values_to = "N") |>
  kable()
```

```{r flag-detail}
d |>
  filter(n_flags >= 1 | reject) |>
  select(PROLIFIC_PID, n_flags, reject, reject_reason,
         flag_bot_combined, flag_duplicate, flag_auth_q, flag_attention,
         n_attn_wrong, n_attn_shown, flag_straightline, n_sliders_same,
         flag_offtask, off_task_min) |>
  arrange(desc(reject), desc(n_flags)) |>
  kable(caption = "All participants with at least one flag.")
```

## Apply exclusions

The cleaned analytic dataset keeps only participants who were not rejected.
Rejection and analysis-exclusion use the same rule, so anyone withheld from payment
is also dropped from the analysis, and vice versa.

```{r apply}
n_before <- nrow(d)
d_clean <- d |> filter(!reject)
cat(n_before - nrow(d_clean), "excluded.  Final analytic N =", nrow(d_clean), "\n")
```

## Condition (arm) assignment check

This confirms the survey's randomizer behaved as designed: within the retained
sample, each article's control vs self-relevant split should be roughly even. A
lopsided split points to a randomization or data-handling problem worth
investigating before analysis.

```{r arms}
cond_cols <- paste0(CFG$condition_prefix, seq_len(CFG$n_headlines))
cond_cols <- cond_cols[cond_cols %in% names(d_clean)]
for (cc in cond_cols) {
  cat(cc, ":\n"); print(table(d_clean[[cc]], useNA = "ifany")); cat("\n")
}
```

## Missing data on primary outcome

Item nonresponse on the primary outcome (self-relevance) is tabulated per article,
so any article with unusual missingness is visible before it reaches the models.

```{r missing}
prim_cols <- sprintf("%s%d_%s_1", CFG$headline_prefix,
                     seq_len(CFG$n_headlines), CFG$primary_measure)
prim_cols <- prim_cols[prim_cols %in% names(d_clean)]
d_clean |>
  summarise(across(all_of(prim_cols), ~sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "Variable", values_to = "N missing") |>
  kable()
```

## Save

```{r save}
dir.create(dirname(CFG$cleaned_rds), showWarnings = FALSE, recursive = TRUE)
saveRDS(d_clean, CFG$cleaned_rds)
```

Cleaned data saved to `` `r CFG$cleaned_rds` ``. **Final N = `r nrow(d_clean)`**.
