---
title: "Prolific Rejections — Participants to Reject / Not Pay"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(knitr)
library(here)
source(here("Newsletter testing", "August headlines", "config.R"))
```

> **Purpose.** This report is deliberately separate from the analysis. It lists
> every Prolific submission that meets the pre-registered rejection criteria,
> with a reason for each, so a human can review before actioning rejections on
> Prolific. **Rejection is hard to reverse and Prolific scrutinises it — review
> this table manually; do not auto-submit.**

Rejection rule (from `config.R`): reject a submission if any *standalone-reject*
flag fires (`r paste(CFG$standalone_reject_flags, collapse=", ")`) **or** it
accumulates `r CFG$reject_nflags`+ quality flags of any kind. This is the exact
rule `00_clean.Rmd` uses to exclude data, computed by the same `compute_flags()`,
so the people not paid are the same people dropped from analysis.

## Load + merge

We rebuild the same evaluated sample the cleaning script uses: genuine, finished
submissions with a valid Prolific ID that Prolific has not already marked
`RETURNED`/`TIMED-OUT`. Recomputing flags here (rather than reading the cleaned
file) keeps this report self-contained and lets it run the moment data lands.

```{r load}
q <- read_qualtrics(CFG$qualtrics_path)
p <- read_prolific(CFG$prolific_path)

# Rejection applies to genuine submissions only: finished, valid PID, and not
# already unpaid on Prolific (RETURNED / TIMED-OUT are never "rejected").
d <- q |>
  filter(DistributionChannel == "anonymous", Finished == TRUE,
         PROLIFIC_PID != "{{%PROLIFIC_PID%}}", !is.na(PROLIFIC_PID)) |>
  left_join(p, by = "PROLIFIC_PID") |>
  filter(!prolific_status %in% c("RETURNED", "TIMED-OUT"))

d <- compute_flags(d, CFG)
```

Submissions evaluated: **`r nrow(d)`**.

## Summary

Counts of the whole evaluated pool, the flagged subset, and the rejections. The
two indented rows split every rejection into the two mutually exclusive paths that
can trigger it, so they always sum to **TO REJECT**: rejected by a single
standalone flag (bot, duplicate, or off-task), versus rejected only by reaching the
2+ flag threshold.

```{r summary}
standalone   <- intersect(CFG$standalone_reject_flags, names(d))
standalone_hit <- if (length(standalone)) rowSums(d[standalone]) > 0 else rep(FALSE, nrow(d))

tibble(
  Metric = c("Submissions evaluated", "Flagged (>=1)", "TO REJECT",
             "  via a standalone flag", "  via 2+ flags (no standalone)"),
  N = c(nrow(d), sum(d$n_flags >= 1), sum(d$reject),
        sum(standalone_hit), sum(d$reject & !standalone_hit))
) |> kable()
```

## ▶ Participants to reject / not pay

The table below is the actionable output: **Prolific ID, submission ID, and the
reason for each rejection.** Empty means no submission met the criteria.

```{r reject-table}
rejects <- d |>
  filter(reject) |>
  transmute(
    PROLIFIC_PID,
    submission_id,
    reason        = reject_reason,
    n_flags,
    attn          = sprintf("%d/%d wrong", n_attn_wrong, n_attn_shown),
    off_task_min,
    completion_code
  ) |>
  arrange(desc(n_flags), desc(off_task_min))

if (nrow(rejects) == 0) {
  cat("No submissions met the rejection criteria.\n")
} else {
  kable(rejects, caption = sprintf("%d submission(s) to reject.", nrow(rejects)))
}
```

## Write rejection CSV

The rejection table is saved to disk as a durable record and to make actioning it
easy: paste the IDs into Prolific's bulk-reject flow and use the `reason` column
for the manual reason Prolific requires on each rejection.

```{r write}
dir.create(dirname(CFG$reject_csv), showWarnings = FALSE, recursive = TRUE)
write_excel_csv(rejects, CFG$reject_csv, na = "")
cat("Wrote", nrow(rejects), "row(s) to", CFG$reject_csv, "\n")
```

## For contrast: flagged but NOT rejected

Submissions with exactly one flag (below the 2+ threshold and no standalone
trigger). These are **kept and paid** under the current rule — review in case you
want to tighten `config.R` (e.g., add `flag_attention` to standalone rejects).

```{r not-rejected}
d |>
  filter(!reject, n_flags >= 1) |>
  transmute(PROLIFIC_PID, n_flags,
            which_flag = case_when(
              flag_attention ~ sprintf("attention (%d/%d wrong)", n_attn_wrong, n_attn_shown),
              flag_straightline ~ sprintf("straightlined (%d sliders)", n_sliders_same),
              flag_bot_combined ~ "bot",
              flag_duplicate ~ "duplicate",
              flag_auth_q ~ "auth-question",
              flag_offtask ~ "off-task",
              TRUE ~ "other")) |>
  arrange(desc(n_flags)) |>
  kable(caption = "Flagged once — paid under current rule.")
```
