---
title: "August Newsletter — Analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    self_contained: true
    toc: true
    toc_depth: 2
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(broom)
library(broom.mixed)
library(knitr)
library(here)
source(here("Newsletter testing", "August headlines", "config.R"))
```

Modeled on the July Newsletter analysis, adapted for the August design (6
articles, each **control** vs one **self-relevant** variant; control is the
reference for every contrast). Reads the cleaned data from `00_clean.Rmd`.

## Load + reshape

The cleaned data is one row per participant. `reshape_long()` pivots it to one row
per participant-by-article, carrying each article's assigned arm (control vs
self-relevant) and its three slider outcomes. This long format is what the
article-level and mixed models below consume. The count table is a sanity check
that every article has both arms populated.

```{r load}
d  <- readRDS(CFG$cleaned_rds)
dl <- reshape_long(d, CFG)
cat("Analytic N:", n_distinct(dl$PROLIFIC_PID),
    "| articles:", nlevels(dl$headline),
    "| arms:", paste(levels(dl$arm), collapse = ", "), "\n")
dl |> count(headline, arm) |> pivot_wider(names_from = arm, values_from = n) |> kable()
```

The hidden chunk below defines the three workhorse functions reused across every
outcome: `fit_overall()` pools all articles into one mixed model to estimate the
average self-relevant effect (with a random slope so the effect may vary by
article, backing off to random intercepts if that model fails to converge);
`fit_by_article()` runs a separate OLS per article for the article-specific
effects; and `manip_plot()` draws the arm means with standard-error bars.

```{r helpers, include=FALSE}
sig_stars <- function(p) case_when(p < .001 ~ "***", p < .01 ~ "**",
                                   p < .05 ~ "*", TRUE ~ "")

# Overall mixed model: outcome ~ arm + (1|person) + (1+arm|article),
# falling back to random intercepts if the maximal model fails to converge.
fit_overall <- function(outcome) {
  f_max <- reformulate(c("arm", "(1|PROLIFIC_PID)", "(1 + arm|headline)"), response = outcome)
  f_ri  <- reformulate(c("arm", "(1|PROLIFIC_PID)", "(1|headline)"),        response = outcome)
  m <- tryCatch(lmer(f_max, data = dl, REML = TRUE), error = function(e) NULL)
  if (!is.null(m) && length(m@optinfo$conv$lme4) == 0) { attr(m, "spec") <- "maximal"; return(m) }
  m2 <- lmer(f_ri, data = dl, REML = TRUE); attr(m2, "spec") <- "random intercepts (fallback)"; m2
}

show_overall <- function(m) {
  cat("*Model:*", attr(m, "spec"), "\n\n")
  print(kable(tidy(m, effects = "fixed", conf.int = TRUE) |>
                mutate(across(where(is.numeric), ~round(., 2))),
              caption = "Fixed effects (reference = control)"))
}

# Per-article OLS: self-relevant vs control
fit_by_article <- function(outcome) {
  map_dfr(levels(dl$headline), function(a) {
    sub <- filter(dl, headline == a, !is.na(.data[[outcome]])) |> mutate(arm = droplevels(arm))
    if (nlevels(sub$arm) < 2) return(NULL)
    m <- lm(reformulate("arm", outcome), data = sub)
    tidy(m, conf.int = TRUE) |>
      filter(term != "(Intercept)") |>
      transmute(article = a, B = estimate, SE = std.error, t = statistic,
                p = p.value, conf.low, conf.high,
                n_control = sum(sub$arm == CFG$control_label),
                n_selfrel = sum(sub$arm != CFG$control_label))
  }) |>
    mutate(sig = sig_stars(p), across(where(is.numeric), ~round(., 2)))
}

manip_plot <- function(outcome, ylab, title) {
  dl |>
    filter(!is.na(.data[[outcome]])) |>
    group_by(headline, arm) |>
    summarise(M = mean(.data[[outcome]]), SE = sd(.data[[outcome]])/sqrt(n()), .groups = "drop") |>
    ggplot(aes(arm, M, ymin = M - SE, ymax = M + SE, color = arm)) +
    geom_pointrange(size = 0.5) +
    facet_wrap(~headline, nrow = 1,
               labeller = as_labeller(function(x) gsub("_", " ", x))) +
    scale_color_manual(values = setNames(c("grey50", "#011F5B"),
                                         c(CFG$control_label,
                                           setdiff(levels(dl$arm), CFG$control_label)[1]))) +
    labs(x = NULL, y = ylab, color = NULL, title = title,
         caption = "Points = mean, bars = +/-1 SE") +
    theme_minimal(base_size = 11) +
    theme(legend.position = "bottom")
}
```

# Manipulation checks

Does the self-relevant framing move each outcome, relative to control? Each outcome
gets two complementary views: an **overall** mixed model that pools all six
articles for the average effect and its precision, and a **by-article** table that
shows where the effect is strong, weak, or reversed. The primary outcome is
self-relevance; reading interest and sharing follow as secondary outcomes.

## Self-relevance

```{r sr-overall, results='asis'}
show_overall(fit_overall("relevant"))
```

```{r sr-article}
kable(fit_by_article("relevant"), caption = "Self-relevant vs control, by article")
```

```{r sr-plot, fig.width=10, fig.height=3.2}
manip_plot("relevant", "Self-relevance (0-100)", "Self-relevance by article and condition")
```

## Want to read more

```{r read-overall, results='asis'}
show_overall(fit_overall("read"))
```

```{r read-article}
kable(fit_by_article("read"), caption = "Self-relevant vs control, by article")
```

```{r read-plot, fig.width=10, fig.height=3.2}
manip_plot("read", "Want to read more (0-100)", "Reading interest by article and condition")
```

## Sharing

```{r share-overall, results='asis'}
show_overall(fit_overall("share"))
```

```{r share-article}
kable(fit_by_article("share"), caption = "Self-relevant vs control, by article")
```

```{r share-plot, fig.width=10, fig.height=3.2}
manip_plot("share", "Willingness to share (0-100)", "Sharing by article and condition")
```

# Impact of self-relevance

The manipulation checks ask whether the framing *raised* self-relevance. This
section asks the downstream question: regardless of condition, does a reader who
*perceives* an article as more self-relevant engage with it more and hold warmer
attitudes toward research? Here self-relevance is a measured predictor, not the
manipulated arm.

## Reading + sharing (article-level, MLM)

`outcome ~ relevant + (1 + relevant | person) + (1 + relevant | article)`,
falling back to random intercepts if needed.

```{r sr-impact-fns, include=FALSE}
fit_sr_impact <- function(outcome) {
  f_rs <- reformulate(c("relevant", "(1 + relevant|PROLIFIC_PID)", "(1 + relevant|headline)"),
                      response = outcome)
  f_ri <- reformulate(c("relevant", "(1|PROLIFIC_PID)", "(1|headline)"), response = outcome)
  m <- tryCatch(lmer(f_rs, data = dl, REML = TRUE), error = function(e) NULL)
  if (!is.null(m) && length(m@optinfo$conv$lme4) == 0) { attr(m, "spec") <- "random slopes"; return(m) }
  m2 <- lmer(f_ri, data = dl, REML = TRUE); attr(m2, "spec") <- "random intercepts (fallback)"; m2
}
```

```{r sr-impact-read, results='asis'}
for (oc in c("read", "share")) {
  cat("\n\n**", oc, "**\n\n", sep = "")
  m <- fit_sr_impact(oc)
  cat("*Model:*", attr(m, "spec"), "\n\n")
  print(kable(tidy(m, effects = "fixed", conf.int = TRUE) |>
                mutate(across(where(is.numeric), ~round(., 3))),
              caption = paste0(oc, " ~ self-relevance")))
}
```

## Research attitudes (person-level, OLS)

The two research-attitude items are asked once per person, not per article, so they
cannot go in an article-level model. Instead each participant's self-relevance is
averaged across their six articles and used to predict each attitude with a simple
person-level OLS. The recode below maps the 7-point Likert responses to 1–7
whether they export as text labels or as Qualtrics choice IDs (13–19).

```{r research-recode, include=FALSE}
likert <- c("Strongly disagree","Disagree","Somewhat disagree",
            "Neither agree nor disagree","Somewhat agree","Agree","Strongly agree")
# Robust recode: numeric 13-19 (Qualtrics choice IDs) -> 1-7; text -> 1-7; else as-is.
recode_likert <- function(x) {
  if (is.numeric(x)) return(ifelse(x >= 13 & x <= 19, x - 12, x))
  num <- suppressWarnings(as.numeric(x))
  if (all(is.na(x) | !is.na(num))) return(ifelse(num >= 13 & num <= 19, num - 12, num))
  as.numeric(factor(x, levels = likert))
}
```

```{r research-impact, results='asis'}
person <- dl |>
  group_by(PROLIFIC_PID) |>
  summarise(mean_relevant = mean(relevant, na.rm = TRUE), .groups = "drop") |>
  left_join(d |> select(PROLIFIC_PID, all_of(CFG$research_cols)), by = "PROLIFIC_PID")

for (j in seq_along(CFG$research_cols)) {
  col <- CFG$research_cols[j]
  person$y <- recode_likert(person[[col]])
  m <- lm(y ~ mean_relevant, data = filter(person, !is.na(y)))
  cat("\n\n**", CFG$research_labels[j], "** (", col, ")\n\n", sep = "")
  print(kable(tidy(m, conf.int = TRUE) |> mutate(across(where(is.numeric), ~round(., 3)))))
}
```
